### 2019-04-21 Draft_Inv.tex
Initial Overleaf Import

%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% sample root file for your "contribution" to a contributed volume
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\RequirePackage{amsmath}
\documentclass[graybox]{svmult}

% choose options for [] as required from the list
% in the Reference Guide

\usepackage{amssymb}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom

\usepackage{psfrag,bbm,epsf}
\usepackage{amssymb, color,enumerate,float,mathtools,algorithmicx}
\usepackage{algorithm}
\usepackage[numbers]{natbib}
\usepackage{enumerate,multirow,booktabs}
\usepackage{url}
\usepackage{natbib}

\newcommand{\blind}{1}
\newtheorem{lem}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem{pro}{Proposition}
\newtheorem{defn}{Definition}
\newtheorem{rmk}{Remark}
\newtheorem{cor}{Corollary}
\newcommand{\reals}{\mathbb{R}}
\newcommand{\naturals}{\mathbb{R}}
\newcommand{\vc}{\boldsymbol{c}}
\newcommand{\vx}{\boldsymbol{x}}
\newcommand{\vt}{\boldsymbol{t}}
\newcommand{\vz}{\boldsymbol{z}}
\newcommand{\vu}{\boldsymbol{u}}
\newcommand{\vy}{\boldsymbol{y}}
\newcommand{\vinfty}{\boldsymbol{\infty}}
\newcommand{\vzero}{\boldsymbol{0}}
\newcommand{\vPsi}{\boldsymbol{\Psi}}
\newcommand{\dif}{{\rm d}}
\DeclareMathOperator{\sign}{sign}
\newcommand{\Udes}{\mathcal{U}}
\newcommand{\Xdes}{\mathcal{X}}
\newcommand{\FXdes}{F_{\Xdes}}
\newcommand{\cm}{\mathcal{M}}
\newcommand{\Ftar}{F}
\newcommand{\ftar}{\varrho}
\newcommand{\cube}{\ensuremath{(0,1)^d}}
\newcommand{\bbone}{\mathbbm{1}}
\newcommand{\ip}[3][{}]{\ensuremath{\left \langle #2, #3 \right \rangle_{#1}}}
\newcommand{\norm}[2][{}]{\ensuremath{\left \lVert #2 \right \rVert}_{#1}}

\def\abs#1{\ensuremath{\left \lvert #1 \right \rvert}}

\usepackage{bm} %to get bold math fonts

\newcommand{\FJH}[1]{{\color{blue}Fred: #1}}
\newcommand{\LK}[1]{{\color{green}Lulu: #1}} %choose your color
\newcommand{\YL}[1]{{\color{red}Yiou: #1}} %choose your color

% see the list of further useful packages
% in the Reference Guide

\makeindex             % used for the subject index
                       % please use the style svind.ist with
                       % your makeindex program

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title*{Are Transformed Low Discrepancy Points Also Low Discrepancy?}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Yiou Li, Lulu Kang, and Fred Hickernell}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{Yiou Li \at DePaul University, 1 E. Jackson
Chicago, IL 60604, \email{yli139@depaul.edu}
\and Lulu Kang \at Illinois Institute of Technology, 10 W 32nd Street, Chicago, IL 60616 \email{lkang2@iit.edu} 
\and 
Fred Hickernell \at Illinois Institute of Technology, 10 W 32nd Street, Chicago, IL 60616 \email{hickernell@iit.edu}}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

\abstract{Write me later}

\section{Introduction}

Professor Kai-Tai Fang and his collaborators have demonstrated the effectiveness of low discrepancy points as space filling designs \cite{FanWan94, FanLiSud06, FangHic07a}.  
They promoted discrepancy as a quality measure for statistical experimental designs to the statistics, science, and engineering communities \cite{FanMaWin02, FanMuk00, FanMa01a, FanMa01b}.

Low discrepancy designs, $\Udes = \{\vu_i\}_{i=1}^N$, are typically constructed so that their empirical distribution, $F_\Udes$, approximates $F_u$, the uniform distribution on the unit cube, \cube.  
The discrepancy measures how large $F_u-F_\Udes$ is.

When the target distribution for the design, $\Ftar$, defined over the experimental domain $\Omega$, is \emph{not} the uniform distribution on the unit cube, then one typically constructs the desired design, $\Xdes$, by transforming a low discrepancy uniform design, i.e., 
\begin{equation} \label{eq:transPts}
\Xdes = \{\vx_i\}_{i=1}^N = \{\vPsi(\vu_i)\}_{i=1}^N = \vPsi(\Udes), \qquad \vPsi: \cube \to \Omega.
\end{equation}
Note that $\Ftar$ may differ from $F_u$ because $\Omega \ne \cube$ and/or $\Ftar$ is non-uniform.  
A natural transformation, $\vPsi$, when $\Ftar$ has independent marginals is the inverse distribution transformation:
\begin{equation}\label{eq:inverse}
\Psi_j(u_j) = F_j^{-1}(u_j), \quad \text{where } \Ftar(\vx) = F_1(u_1) \cdots F_d(u_d).
\end{equation}
A number of transformation methods for different distributions can be found in \cite{devroye2006nonuniform}.

The question addressed in this chapter is whether the design $\Xdes$ resulting from transformation \eqref{eq:transPts} of a low discrepancy design, $\Udes$, is itself low discrepancy with respect to the target distribution $\Ftar$. 
In other words, 
\begin{equation} \label{BigQ} \tag{Q}
\text{\emph{does small $F_u - F_\Udes$ imply small $\Ftar - F_\Xdes$?}}
\end{equation}
We demonstrate that the answer may be yes or no, depending on how the question is posed.  
We discuss both cases.  
For illustrative purposes, we consider the case where $\Ftar$ is the multivariate normal distribution.

In the rest of this chapter, we first explain the discrepancy that measures how large $\Ftar - F_\Xdes$ is and motivate it from three different perspectives.  Next, we the inverse transformation can lead to inconsistency in terms the discrepancies of the designs before and after transformation. 
We also proposed a remedy method to improve the design in terms of the discrepancy between $\Ftar$ and $F_\Xdes$. 
Numerical examples are used to show the performance of the method.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Discrepancy}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Experimental design theory based on  discrepancy assumes an experimental region, $\Omega$, and a target probability distribution, $\Ftar:\Omega \to [0,1]$, which is known a priori. In many of our examples, we assume that $\Ftar$ has a probability density, $\ftar$.  It is convenient to also work with measures, $\nu$, defined on $\Omega$.  If $\nu$ is a probability measure, the associated probability distribution is given by $F(\vx) = \nu((-\vinfty,\vx])$.  The Dirac measure, $\delta_{\vx}$ is the probability measure assigning unit measure to the point $\vx$.  A design, $\Xdes = \{\vx_i\}_{i=1}^N$, is a finite set of points that has an associated empirical distribution, $F_{\Xdes}  = N^{-1} \sum_{i=1}^N \bbone_{(-\vinfty,\vx_i]}$ as well as an associated empirical measure, $\nu_{\Xdes}  = N^{-1} \sum_{i=1}^N \delta_{\vx_i}$.

In the remainder of this section we provide three interpretations of the discrepancy---the magnitude of $\Ftar - \FXdes$.  One interpretation is the norm of $\Ftar - \FXdes$.  The second interpretation is worst-case cubature error for integrands in a Hilbert space.  The third interpretation is average case cubature error for stochastic processes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Definition in Terms of a Norm on a Hilbert Space of Measures}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Let $(\cm, \ip[\cm]{\cdot}{\cdot})$ be a Hilbert space of measures defined on the experimental region, $\Omega$.  Assume that $\cm$ includes all Dirac measures.  Define the function $K:\Omega \times \Omega \to \reals$ in terms of inner products of Dirac measures:
\begin{equation} \label{kerDeltaDef}
    K(\vt,\vx) := \ip[\cm]{\delta_{\vt}}{\delta_{\vx}}, \qquad \forall \vt, \vx \in \Omega.
\end{equation}
It is straightforward to show that $ K$ is symmetric in its arguments and positive-definite, namely:
\begin{gather*}
K(\vx, \vt) = K(\vt, \vx) \qquad \forall \vt, \vx\in \Omega,\\
\sum\limits_{i, k=1}^N c_i c_k  K(\vx_i,\vx_k) > 0, \qquad \forall N\in\mathbb{N}, \  \vc \in\mathbb{R}^N, \ \vc \ne \vzero,  \ \Xdes \in\Omega.
\end{gather*}
For arbitrary measures $\lambda, \nu \in \cm$, their inner product can be expressed in terms of a double integral of the kernel, $K$:
\begin{equation} \label{ipMdef}
    \ip[\cm]{\lambda}{\nu} = \int_{\Omega \times \Omega} K(\vt,\vx) \, \lambda(\dif \vt) \nu(\dif \vx).
\end{equation}
This can be established directly from \eqref{kerDeltaDef} for $\cm_0$, the vector space spanned by all Dirac measures.  Letting $\cm$ be the closure of the pre-Hilbert space $\cm_0$ then yields \eqref{ipMdef}.

The discrepancy of the design $\Xdes$ with respect to the target probability measure $\nu$ using the kernel $K$, can be defined as the norm of the difference between the target probability measure, $\nu$, and the empirical probability measure for $\Xdes$:
\begin{subequations} \label{discDef}
\begin{align} 
    D^2(\Xdes,\nu,K) & := \norm[\cm]{\nu - \nu_{\Xdes}}^2 = \int_{\Omega \times \Omega} K(\vt,\vx) \, (\nu - \nu_{\Xdes})(\dif \vt) (\nu - \nu_{\Xdes})(\dif \vx) \\
    \nonumber
    & = \int_{\Omega \times \Omega} K(\vt,\vx) \, \nu(\dif \vt) \nu (\dif \vx)\\
    & \qquad \qquad - \frac 2N \sum_{i=1}^N \int_{\Omega} K(\vt,\vx_i) \, \nu(\dif \vt) + \sum_{i,k=1}^N K(\vx_i,\vx_k).
\end{align}
The first argument refers to the design, the second to the target measure, and the third refers to the kernel used to define the kernel used to define the Hilbert space norm for $\cm$.
The formula for the discrepancy may be written equivalently in terms of the probability density, $\rho$, corresponding to the probability measure, $\varrho$:
\begin{align}
\nonumber
    D^2(\Xdes,\varrho,K)  & = \int_{\Omega \times \Omega} K(\vt,\vx) \, \varrho(\vt) \varrho (\vx) \, \dif \vt\dif \vx\\
    & \qquad \qquad - \frac 2N \sum_{i=1}^N \int_{\Omega} K(\vt,\vx_i)  \, \varrho(\vt) \, \dif \vt + \sum_{i,k=1}^N K(\vx_i,\vx_k).
\end{align}
\end{subequations}
Here, and below we abuse the notation for discrepancy, but we always preserve the meaning of the first second and third arguments.  Thus,
\[
D(\Xdes,\nu,K), \ D(\Xdes,F,K), \ D(\Xdes,\varrho,K), \ D(\nu_{\Xdes},\nu,K), \text{ etc.} 
\]
are all equivalent.

The equivalent formulas for the discrepancy in \eqref{discDef} depend inherently on the choice of $K$.  That is key to the answering our question \eqref{BigQ}.  A kernel often used is 
\begin{align}
    K(\vt,\vx)  = \prod\limits_{j=1}^d\left[1+ |t_j|+ |x_j|- |x_j-t_j|\right].
\end{align}

\section{A Discrepancy Defined for Normal Distribution}

Consider any symmetric and positive semi-definite kernel function $K(\vx,\vt)$ on the experiment region $\Omega$. 
In other words, the kernel function satisfies 
\begin{align*}
K(\vx, \vt) &= K(\vt, \vx), \,\,\,\forall \vt, \vx\in \Omega,\\
\sum\limits_{i, k=1}^n c_ic_k & K(\vx_i,\vx_k)\geq 0, \,\,\,\forall n\in\mathbb{N^+}, c_i\in\mathbb{R}, \vx_i\in\Omega.
\end{align*}
The discrepancy of a design $P = \{\vx_i\}_{i=1}^N$ on $\Omega$ with respect to a distribution $\Ftar$ is then defined as
\begin{equation}\label{eq:Disc}
D(P) = \left\{\int_{\Omega\times\Omega} K(\vx,\vt)\dif [\Ftar(\vx)-F_{P}(\vx)]\dif [\Ftar(\vt)-F_{P}(\vt)]\right\}^{1/2},
\end{equation}
and thus, 
\begin{align}\label{eq:Disc2}\nonumber
[D(P)]^2  =& \int_{\Omega\times\Omega}  K(\vx,\vt)\dif F_{*}(\vx)\dif F_{*}(\vt) \\
- &\frac{2}{N}\sum\limits_{\vx\in P}\int_{\Omega}K(\vx,\vt)\dif F_{*}(\vt) +\frac{1}{N^2}\sum\limits_{\vx,\vx'\in P}K(\vx,\vx')
\end{align}
In \cite{Hic99a}, it is showed that, any discrepancy determined by a reproducing kernel function $K$ and a distribution $\Ftar$ is a goodness-of-fit statistic that measures how well the empirical distribution $F_P$ of design $P$ approximates the distribution $\Ftar$. 
What's more, the order of computation for evaluating the discrepancy is at worst $\mathcal{O}(N^2)$.

 Let $P = \{\vx_i\}_{i=1}^N$ be a design on $\Omega = \mathbb{R}^d$. 
 According to \eqref{eq:Disc2}, the squared discrepancy of the design $P$ with respect to the $d$-dimensional standard multivariate normal probability distribution $N({\bf 0}, {\bf I}_d)$ with cdf $\Phi$ is
\begin{eqnarray}\label{eqn:discrepancy}\nonumber
[D(P)]^2 &=& \int_{\Omega\times\Omega} K(\vx,\vt)\dif \Phi(\vx)\dif \Phi(\vt)\\
&-&\frac{2}{N}\sum_{i=1}^N \int_{\Omega}K(\vx,\vx_i)\dif \Phi(\vx)+\frac{1}{N^2}\sum_{i,k=1}^N K(\vx_i,\vx_k).
\end{eqnarray}

We need to choose a kernel function that can facilitate the analytical derivation of the discrepancy for both standard normal and uniform distribution. 
A commonly used discrepancy to measure for the uniform distribution on $[0,1]^d$ is the centered $L_2$ discrepancy \cite{Hic97a} defined as:
\begin{align*}
[D_2(P)]^2 =& \left(\frac{13}{12}\right)^d - \frac{2}{N}\sum\limits_{\vz\in P}\prod_{j=1}^d \left(1+\frac{1}{2}|z_j-1/2|-1/2|z_j-1/2|^2\right)\\
\hspace{5ex}&+ \frac{1}{N^2}\sum\limits_{\vz,\vz'\in P}\prod_{j=1}^d\left[1+\frac{1}{2}|z_j-1/2|+\frac{1}{2}|z_j'-1/2|-\frac{1}{2}|z_j-z_j'|\right],    
\end{align*}
with the reproducing kernel:
\begin{equation}\label{eqn:oril2kernel}
K_2(\vx,\vt) = \prod\limits_{j=1}^s\left[1+\frac{1}{2}|x_j-1/2|+\frac{1}{2}|t_j-1/2|-\frac{1}{2}|x_j-t_j|\right].
\end{equation}
Shifting experimental region to $[-1/2,1/2]^d$, the reproducing kernel in \eqref{eqn:oril2kernel} becomes
\begin{align}\label{eqn:l2kernel}
K(\vx,\vt) & = \prod\limits_{j=1}^d\left[1+\frac{1}{2}|x_j|+\frac{1}{2}|t_j|-\frac{1}{2}|x_j-t_j|\right].  
\end{align}
Next we extend the domain of this kernel function to $\mathbb{R}^d$, and show that this kernel function is a reproducing kernel with a proper defined inner product.

We define an inner product as follows. 
\begin{equation}\label{eq:inner}
\langle f,g \rangle = \sum_{u\subseteq \{1,...,d\}}\int_{\mathbb{R}^{|u|}}\frac{\partial^{|u|}}{\partial \vx_u}f(\vx_u,{\bf 0})\frac{\partial^{|u|}}{\partial \vx_u}g(\vx_u,{\bf 0})\dif \vx_u,
\end{equation}
where $u$ is an index set and $u\subseteq \{1, \ldots, d\}$ and $|u|$ is the cardinality of $u$. 
Using the following operators, 
$$\partial \vx_u = \prod\limits_{k\in u}\partial x_k \text{ and } \dif \vx_u = \prod\limits_{k\in u}\dif x_k , $$
the $|u|$-th order partial derivative in \eqref{eq:inner} is with respective to $\vx_{u}$, the subset of variables indexed by $u$, and the integration is also with respect to the same subset of variables. 
The vector $(\vx_u,{\bf 0})$ is a $d$-dimensional vector with the dimension indexed by $u$ denoted as $\vx_u$ and the rest are set to be ${\bf 0}$. 
In particular, for $u = \{1,...,d\}$, we have $(\vx_u,{\bf 0}) = \vx$; for $u=\emptyset$, we have $(\vx_u,{\bf 0}) = {\bf 0}$.

With the inner product \eqref{eq:inner}, it is easy to see that above kernel function in \eqref{eqn:l2kernel} is symmetric and positive semi-definite on $\Omega = \mathbb{R}^d$, i.e., the domain of the $d$-dim multivariate normal distribution. 
Note that $K({\bf 0},\vt) = 1$ and
\begin{align*}
\frac{\partial^{|u|} K((\vx_u,{\bf 0}),\vt)}{\partial \vx_u}& =\prod_{i\in u}\frac 12 \left[\sign(x_i) - \sign(x_i - t_i) \right] \\
= &\begin{cases}
\prod\limits_{i\in u}\sign(t_i), & \min(0,t_i) < x_i \leq \max(0,t_i), i\in u\\
0, & \textrm{otherwise}.
\end{cases}.
\end{align*}
Thus, $\langle K(\cdot,\vt), K(\cdot,\vt) \rangle < \infty $, and
\begin{align*}
\langle f, K(\cdot,\vt) \rangle &= \sum_{u\subseteq \{1,...,d\}}\int_{\mathbb{R}^{|u|}}\frac{\partial^{|u|}}{\partial \vx_u}f(\vx_u,{\bf 0})\frac{\partial^{|u|} K((\vx_u,{\bf 0}),\vt)}{\partial \vx_u}\dif \vx_u \\
& =     \sum_{u\subseteq \{1,...,d\}}\sum_{v\subseteq u}(-1)^{|u|-|v|}f(\vt_v,{\bf 0})\\
& = f(\vt)
\end{align*}
With the reproducing kernel \eqref{eqn:l2kernel}, we can analytically derive the  squared discrepancy for the standard normal distribution. 
For univariate standard normal distribution $N(0,1)$ 
\begin{align}\label{eq:DisNormald=1}\nonumber
[D(P)]^2=& -\frac{2}{N}\sum_{n=1}^N \left[\max(x_n,0)-x_n\Phi(x_n)-\phi(x_n)\right]\\
+&\frac{1}{N}\sum_{n=1}^N|x_n|-\frac{1}{2N^2}\sum_{n,m=1}^N|x_n-x_m|. 
\end{align}
For multivariate standard normal distribution $N({\bf 0}, {\bf I}_d)$, 
\begin{align}\label{eq:DisNormald>1}\nonumber
&[D(P)]^2\\\nonumber
  &= \left(1+\sqrt{\frac{2}{\pi}}\right)^d - \frac{2}{N}\sum\limits_{\vx\in P} \prod\limits_{j=1}^d\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_j|-x_j[\Phi(x_j)-1/2]-\phi(x_j)\right]\\
  &+\frac{1}{N^2}\sum_{\vx,\vt\in P}\prod_{j=1}^d \left[1+\frac{1}{2}|x_j|+\frac{1}{2}|t_j|-\frac{1}{2}|x_j-t_j|\right]. 
\end{align}
In both \eqref{eq:DisNormald=1} and \eqref{eq:DisNormald>1}, $\phi(\cdot)$ and $\Phi(\cdot)$ are the pdf and cdf for the univeriate standard normal distribution $N(0,1)$, respectively. 
The derivations are in Appendix.

\section{Inconsistency in Discrepancy}\label{sec:inconsistency}

Let $\mathcal{H}$ be a reproducing kernel Hilbert space associated with the reproducing kernel function $K$: $\mathbb{R}\times \mathbb{R}\rightarrow\mathbb{R}$. 
One fundamental problem in mathematics and statistics is to compute the mean value $\mu$ of any given function $g\in \mathcal{H}$. 
\[
\mu=\mathbb{E}(g(X))=\int_{\mathbb{R}}g(x)\phi(x)dx=\int_{\mathbb{R}} g(x)d\Phi(x), 
\]
where $\phi(\cdot)$ and $\Phi(\cdot)$ are the pdf and cdf functions of the standard normal distribution $N(0,1)$. 
When

To illustrate the inconsistency in discrepancy before and after inverse distribution transformation, we consider a toy example with $s=5$ and $n=50$. 20 randomly generated uniform random samples are adapted to generate samples from standard multivariate normal distribution using inverse distribution transformation. The following figure \ref{fig:UniVsNormDisc} shows that a sample with low uniform discrepancy may not guarantee a sample with low normal discrepancy after inverse distribution transformation.

\begin{figure}[H]
\label{fig:UniVsNormDisc}
\centering
{\includegraphics[width=8cm]{d5n50UniVsNormDisc2.pdf}}
\caption{Uniform Discrepancy Vs. Normal Discrepancy after Inverse Transformation}
\end{figure}

We further investigate the correlation between uniform discrepancy and the normal discrepancy after the inverse distribution transformation. For different variable dimension from $s=1$ to $s=10$, the sample correlation coefficients between the uniform discrepancies of 1000 uniform random samples of size 50 and the normal discrepancies of the corresponding normal random samples generated using inverse distribution transformation are calculated. From figure \ref{fig:UniVsNormDisc}, it can be seen that the phenomenon of inconsistency in discrepancy becomes more pronounced as the sample becomes more sparse.

\begin{figure}[htbp]
\label{fig:DimVsDisc}
\centering
{\includegraphics[width=8cm]{dimVsdisc.pdf}}
\caption{Correlation between Uniform Discrepancy and Normal Discrepancy with Different Variable Dimensions}
\end{figure}

\section{Improvement by the Coordinate-Exchange Algorithm}
The common practice to generate $d-$dim standard normal random numbers is inverse distribution transformation. However, as discussed in section \ref{sec:inconsistency}, a random sequence with low uniform discrepancy doesn't guarantee a low normal discrepancy sequence after inverse distribution transformation. We propose an efficient algorithm that assures low normal discrepancy of the generated $d$-dim standard normal random numbers.
\begin{algorithm}[ht]
\begin{algorithmic}[1]
\caption{Algorithm to generate a $d$-dim low normal discrepancy sequence}
\State Start with a $d$-dim low uniform discrepancy sequence, e.g., Sobol sequence 
\State 
\end{algorithmic}
\end{algorithm}
\section{Simulation}

\section{Conclusion}

\section*{Appendix}
Derivation of \eqref{eq:DisNormald=1} and \eqref{eq:DisNormald>1}. 
\begin{proof}
We first derive $[D(p)]^2$ for $d=1$ case. 
To compute the discrepancy, we first integrate the kernel once:
\begin{align*}
\MoveEqLeft{\int_{-\infty}^\infty K(x,t) \, \dif \Phi(x)}\\
=&\int_{-\infty}^{\infty} \left(1+\frac{1}{2}|x|+\frac{1}{2}|t|-\frac{1}{2}|x-t|\right)\phi(x) \, \dif x\\
=& 1+ \frac{1}{\sqrt{2\pi}} + \frac{1}{2}|t|-\frac{1}{2}\left[\int_{-\infty}^{t}(t-x)\phi(x) \, \dif x+\int_{t}^{\infty} (x-t)\phi(x) \, \dif x\right]\\
=& 1+ \frac{1}{\sqrt{2\pi}} + \frac{1}{2}|t| - t [\Phi(t)-1/2] - \phi(t) .
\end{align*}
Then we integrate again:
\begin{align*}
\MoveEqLeft{\int_{-\infty}^\infty \int_{-\infty}^\infty K(x,t) \, \dif \Phi(x) \dif \Phi(t)}\\
& =  \int_{-\infty}^{\infty} \left( 1+\frac{1}{\sqrt{2\pi}} + \frac{1}{2}|t| - t [\Phi(t)-1/2] + \phi(t)\right)\phi(t) \, \dif t\\
&= 1+ \sqrt{\frac{2}{\pi}} + \int_{-\infty}^{\infty} \{ - t \Phi(t)\phi(t)  +  [\phi(t)]^2 \} \, \dif t\\
&= 1+\sqrt{\frac{2}{\pi}}-\frac{1}{\sqrt{4\pi}}+\int_{-\infty}^{\infty}\frac{1}{2\pi}e^{-t^2}\dif t\\
&= 1+\sqrt{\frac{2}{\pi}}-\frac{1}{\sqrt{4\pi}}+\frac{\frac{1}{\sqrt{2}}}{\sqrt{2\pi}}\int_{-\infty}^{\infty}\frac{1}{\sqrt{2\pi}\left(\frac{1}{\sqrt{2}}\right)}e^{-\frac{t^2}{2\left(\frac{1}{\sqrt{2}}\right)^2}}\dif t\\
&=1+\sqrt{\frac{2}{\pi}}. 
\end{align*}
Notice that $\int_{-\infty}^{\infty} t\Phi(t)\phi(t)\dif t = \frac{1}{\sqrt{4\pi}}$ and 
\begin{eqnarray*}
&&\int_{\Omega}K(x,x_n)\dif \Phi(x)\\
&=& \int_{-\infty}^{\infty} \left(1+\frac{1}{2}|x|+\frac{1}{2}|x_n|-\frac{1}{2}|x-x_n|\right)\phi(x)\dif x\\
&=& 1+\frac{1}{2}\sqrt{\frac{2}{\pi}}+\frac{1}{2}|x_n|-\frac{1}{2}\left[\int_{-\infty}^{x_n}(x_n-x)\phi(x)\dif x+\int_{x_n}^{\infty} (x-x_n)\phi(x)\dif x\right]\\
&=& 1+\sqrt{\frac{1}{2\pi}}+\frac{1}{2}|x_n|-\frac{1}{2}\left[\int_{-\infty}^{x_n}(x_n-x)\phi(x)\dif x+\int_{x_n}^{\infty} (x-x_n)\phi(x)\dif x\right]\\
&=& 1+\sqrt{\frac{1}{2\pi}}+\frac{1}{2}|x_n|-\frac{1}{2}\left[2x_n\Phi(x_n)-x_n-2\int_{-\infty}^{x_n}x\phi(x)\dif x\right]\\
&=& 1+\sqrt{\frac{1}{2\pi}}+\max(x_n,0)-x_n\Phi(x_n)-\frac{ e^{-x_n^2/2}}{\sqrt{2\pi}}. 
\end{eqnarray*}
Thus, the discrepancy can be obtained as follows. 
\begin{eqnarray*}
&& [D(P)]^2\\
&= &1+\sqrt{\frac{2}{\pi}}-\frac{2}{N}\sum_{n=1}^N \left[1+\sqrt{\frac{1}{2\pi}}+\max(x_n,0)-x_n\Phi(x_n)-\frac{ e^{-x_n^2/2}}{\sqrt{2\pi}}\right]\\
&&+\frac{1}{N^2}\sum_{n,m=1}^N \left[1+\frac{1}{2}|x_n|+\frac{1}{2}|x_m|-\frac{1}{2}|x_n-x_m|\right]\\
&= &-\frac{2}{N}\sum_{n=1}^N \left[\max(x_n,0)-x_n\Phi(x_n)-\frac{ e^{-x_n^2/2}}{\sqrt{2\pi}}\right]+\frac{1}{N^2}\sum_{n,m=1}^N \left[\frac{1}{2}|x_n|+\frac{1}{2}|x_m|-\frac{1}{2}|x_n-x_m|\right]\\
&=& -\frac{2}{N}\sum_{n=1}^N \left[\max(x_n,0)-x_n\Phi(x_n)-\phi(x_n)\right]+\frac{1}{N}\sum_{n=1}^N|x_n|-\frac{1}{2N^2}\sum_{n,m=1}^N|x_n-x_m|.\\
\end{eqnarray*}
For the distribution $N({\bf 0}, {\bf I}_d)$, the joint pdf is $$\prod\limits_{j=1}^d\phi(x_j) = \prod\limits_{j=1}^d \frac{1}{\sqrt{2\pi}}e^{-x_j^2/2}.$$
Here the cdf function $\Phi$ used interchangeably for $N({\bf 0}, {\bf I}_d)$ and $N(0, 1)$, depending if the variable is a vector or scalar. Thus, 
\begin{align*}
\int_{\reals^d\times \reals^d} K(\vx,\vt)&\dif\Phi(\vx)\dif\Phi(\vt) = \left(1+\sqrt{\frac{2}{\pi}}\right)^d, \\
\int_{\reals^d}K(\vx,\vx_n)\dif\Phi(\vx) = \prod\limits_{j=1}^s&\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_j|-x_j[\Phi(x_j)-1/2]-\phi(x_j)\right].
\end{align*}
The discrepancy can be obtained
\begin{eqnarray*}
&&[D(P)]^2\\
&=& \left(1+\sqrt{\frac{2}{\pi}}\right)^d - \frac{2}{N}\sum\limits_{\vx\in P} \prod\limits_{j=1}^d\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_j|-x_j[\Phi(x_j)-1/2]-\phi(x_j)\right]\\
&&+\frac{1}{N^2}\sum_{\vx,\vt\in P}\prod_{j=1}^d \left[1+\frac{1}{2}|x_j|+\frac{1}{2}|t_j|-\frac{1}{2}|x_j-t_j|\right]. 
\end{eqnarray*}       
\end{proof}

\bibliographystyle{amsplain}
%\bibliography{FJH23,FJHown23}
\bibliography{Ref.bib}

\end{document}

### 2019-04-21 Notes.tex
Initial Overleaf Import

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,bbm,epsf}
\usepackage{amssymb, amsmath, amsthm, color,enumerate,float,mathtools,graphicx,hyperref}
\usepackage{algorithm}
\usepackage[numbers]{natbib}
\usepackage{enumerate,multirow,booktabs}
\usepackage{url}
\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL

%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{1}
\newtheorem{lem}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem*{thm*}{Theorem}
\newtheorem{pro}{Proposition}
\newtheorem{defn}{Definition}
\newtheorem{rmk}{Remark}
\newtheorem{cor}{Corollary}
\newcommand{\reals}{\mathbb{R}}
\newcommand{\naturals}{\mathbb{R}}
\newcommand{\vx}{\boldsymbol{x}}
\newcommand{\vt}{\boldsymbol{t}}
\newcommand{\vz}{\boldsymbol{z}}
\newcommand{\vy}{\boldsymbol{y}}
\newcommand{\dif}{{\rm d}}
\DeclareMathOperator{\sign}{sign}

\def\abs#1{\ensuremath{\left \lvert #1 \right \rvert}}

\newcommand{\FJH}[1]{{\color{blue}Fred: #1}}
\newcommand{\LK}[1]{{\color{green}Lulu: #1}} %choose your color
\newcommand{\YL}[1]{{\color{red}Yiou: #1}} %choose your color

\allowdisplaybreaks
\title{Inverse transformed points}
\author{ }
\date{November 2018}

\begin{document}

\maketitle

\section{A wrap up of meeting 11/20/2018:}
Structure and workflow of the paper:
\begin{enumerate}
    \item 
    Start with an example of performing inverse transformation method on low discrepancy sequence that produces large discrepancy with respect to normal measure.
    \begin{itemize}
        \item 
        Which discrepancy to use? $L_2$ discrepancy, centered $L_2$ or ....? \FJH{Use the centered $L_2$, but we may want to re-define it on a domain centered at the origin.}
        \item
        We decide to keep the kernel function fixed, but the discrepancy changes from
        $$[D(P;K)]^2 = \int_{\Omega\times\Omega} K(x,t)d[F_{\text{unif}}(x)-F_P(x)]d[F_{\text{unif}}(t)-F_P(t)]$$
        to
        $$[D(P;K)_{\text{normal}}]^2 = \int_{\Omega\times\Omega} K(x,t)d[\Phi(x)-F_P(x)]d[\Phi(t)-F_P(t)]$$
        \FJH{Here $F_P$ denotes the empirical distribution function of the design $P= \{x_i\}_{i=1}^N$.}
        \item
        The low discrepancy sequence that has small $[D(P;K)]^2$ may not retain small $[D(\Phi^{-1}(P));K)]^2_{\text{normal}}$ after applying inverse transformation.
    \end{itemize}
    \item
    Derive an analytical expression for $[D(P;K)_{\text{normal}}]^2$ so that we can evaluate it given a set of inverse transformed points. 
    \item
    Figure out a remedy for the issue. For instance take several low discrepancy sequences and evaluate $[D(P;K)_{\text{normal}}]^2$ of the inverse transformed sequences, then choose the one with the smallest $[D(P;K)_{\text{normal}}]^2$. Or, some optimization tools could be used to refine the inverse transformed points.
\end{enumerate}

\section{Intermediate Notes}
The reproducing kernel for centered $L_2$ discrepancy on $[0,1]^s$ is:
$$K(\vx,\vt) = \prod\limits_{j=1}^s\left[1+\frac{1}{2}|x_j-1/2|+\frac{1}{2}|t_j-1/2|-\frac{1}{2}|x_j-t_j|\right].$$
Transformed the kernel onto the region $[-1/2,1/2]^s$, we have:
\begin{align*}
    K(\vx,\vt) & = \prod\limits_{j=1}^s\left[1+\frac{1}{2}|x_j|+\frac{1}{2}|t_j|-\frac{1}{2}|x_j-t_j|\right] \\
\end{align*}
\FJH{Let $P = \{x_i\}_{i=1}^N$ be a possible design.}  Then, the discrepancy of the design $P$ w.r.t.\ the standard multivariate normal probability distribution $\Phi$, which has domain $\Omega = (-\infty,\infty)^s$ is
\begin{eqnarray*}
&&[D(P)]^2\\
&=& \int_{\Omega\times \Omega} K(\vx,\vt)\dif \Phi(\vx)\dif \Phi(\vt)-\frac{2}{N}\sum_{n=1}^N \int_{\Omega}K(\vx,\vx_n)\dif \Phi(\vx)+\frac{1}{N^2}\sum_{n,m=1}^N K(\vx_n,\vx_m)\\
\end{eqnarray*}
\textcolor{red}{From Lulu: by a design $P$, do you mean a sample of $\{x_i\}_{i=1}^N$ that is sampled from $P$? This part is not very clear to me.}

\begin{enumerate}
    \item ($s=1$)
    \FJH{Note that this reproducing kernel corresponds to the inner product
    \begin{equation}
        \langle f,g \rangle = f(0) g(0)  + \int_{-\infty}^\infty f'(x) g'(x) \, \dif x
    \end{equation}
    To demonstrate this, note that
    \begin{align*}
        K(0,t) &= 1, \\
        \frac{\partial K(x,t)}{\partial x} &= \frac 12 \left[\sign(x) - \sign(x - t) \right] \\
        & = \begin{cases} 0, & -\infty < x < \min(0,t), \\
        \sign(t), & \min(0,t) < x < \max(0,t), \\
        0, & \max(0,t) < x < \infty,
        \end{cases}
        \\
        \intertext{so $\langle K(\cdot,t), K(\cdot,t) \rangle < \infty $, and}
        \langle f, K(\cdot,t) \rangle &= f(0) K(0,t) + \int_{-\infty}^\infty f'(x) \frac{\partial K(x,t)}{\partial x} \, \dif x \\
        & = f(0) + \sign(t) \int_{\min(0,t)}^{\max(0,t)} f'(x)  \, \dif x \\    
        & = f(0) + \sign(t) [f(\max(0,t)) - f(\min(0,t))] \\    
        & = f(t)
        \end{align*}

        To compute the discrepancy, we first integrate the kernel once:
       \begin{align*}
  \MoveEqLeft{\int_{-\infty}^\infty K(x,t) \, \dif \Phi(x)}\\
    & =  \int_{-\infty}^{\infty} \left(1+\frac{1}{2}|x|+\frac{1}{2}|t|-\frac{1}{2}|x-t|\right)\phi(x) \, \dif x\\
    &= 1+ \frac{1}{\sqrt{2\pi}} + \frac{1}{2}|t|-\frac{1}{2}\left[\int_{-\infty}^{t}(t-x)\phi(x) \, \dif x+\int_{t}^{\infty} (x-t)\phi(x) \, \dif x\right]\\
    &= 1+ \frac{1}{\sqrt{2\pi}} + \frac{1}{2}|t| - t [\Phi(t)-1/2] - \phi(t) .
    \end{align*}
    Then we integrate again:
       \begin{align*}
  \MoveEqLeft{\int_{-\infty}^\infty \int_{-\infty}^\infty K(x,t) \, \dif \Phi(x) \dif \Phi(t)}\\
    & =  \int_{-\infty}^{\infty} \left( 1+ \frac{1}{\sqrt{2\pi}} + \frac{1}{2}|t| - t [\Phi(t)-1/2] +  \phi(t) \right)\phi(t) \, \dif t\\
    &= 1+ \sqrt{\frac{2}{\pi}} + \int_{-\infty}^{\infty} \{ - t \Phi(t)\phi(t)  +  [\phi(t)]^2 \} \, \dif t\\
    &= 1+\sqrt{\frac{2}{\pi}}-\frac{1}{\sqrt{4\pi}}+\int_{-\infty}^{\infty}\frac{1}{2\pi}e^{-t^2}\dif t\\
    &= 1+\sqrt{\frac{2}{\pi}}-\frac{1}{\sqrt{4\pi}}+\frac{\frac{1}{\sqrt{2}}}{\sqrt{2\pi}}\int_{-\infty}^{\infty}\frac{1}{\sqrt{2\pi}\left(\frac{1}{\sqrt{2}}\right)}e^{-\frac{t^2}{2\left(\frac{1}{\sqrt{2}}\right)^2}}\dif t\\
    &=1+\sqrt{\frac{2}{\pi}}
    \end{align*}

  $\int_{-\infty}^{\infty} t\Phi(t)\phi(t)\dif t = \frac{1}{\sqrt{4\pi}}$ comes from the link: \href{https://en.wikipedia.org/wiki/List_of_integrals_of_Gaussian_functions}{List of integrals of Gaussian functions.}
    }

    \begin{eqnarray*}
  &&  \int_{\Omega}K(x,x_n)\dif \Phi(x)\\
    &=& \int_{-\infty}^{\infty} \left(1+\frac{1}{2}|x|+\frac{1}{2}|x_n|-\frac{1}{2}|x-x_n|\right)\phi(x)\dif x\\
    &=& 1+\frac{1}{2}\sqrt{\frac{2}{\pi}}+\frac{1}{2}|x_n|-\frac{1}{2}\left[\int_{-\infty}^{x_n}(x_n-x)\phi(x)\dif x+\int_{x_n}^{\infty} (x-x_n)\phi(x)\dif x\right]\\
    &=& 1+\sqrt{\frac{1}{2\pi}}+\frac{1}{2}|x_n|-\frac{1}{2}\left[\int_{-\infty}^{x_n}(x_n-x)\phi(x)\dif x+\int_{x_n}^{\infty} (x-x_n)\phi(x)\dif x\right]\\
    &=& 1+\sqrt{\frac{1}{2\pi}}+\frac{1}{2}|x_n|-\frac{1}{2}\left[2x_n\Phi(x_n)-x_n-2\int_{-\infty}^{x_n}x\phi(x)\dif x\right]\\
    &=& 1+\sqrt{\frac{1}{2\pi}}+\max(x_n,0)-x_n\Phi(x_n)-\frac{ e^{-x_n^2/2}}{\sqrt{2\pi}}
    \end{eqnarray*}
    Thus, the discrepancy becomes
    \begin{eqnarray*}
   && [D(P)]^2\\
    &= &1+\sqrt{\frac{2}{\pi}}-\frac{2}{N}\sum_{n=1}^N \left[1+\sqrt{\frac{1}{2\pi}}+\max(x_n,0)-x_n\Phi(x_n)-\frac{ e^{-x_n^2/2}}{\sqrt{2\pi}}\right]\\
    &&+\frac{1}{N^2}\sum_{n,m=1}^N \left[1+\frac{1}{2}|x_n|+\frac{1}{2}|x_m|-\frac{1}{2}|x_n-x_m|\right]\\
     &= &-\frac{2}{N}\sum_{n=1}^N \left[\max(x_n,0)-x_n\Phi(x_n)-\frac{ e^{-x_n^2/2}}{\sqrt{2\pi}}\right]+\frac{1}{N^2}\sum_{n,m=1}^N \left[\frac{1}{2}|x_n|+\frac{1}{2}|x_m|-\frac{1}{2}|x_n-x_m|\right]\\
     &=& -\frac{2}{N}\sum_{n=1}^N \left[\max(x_n,0)-x_n\Phi(x_n)-\phi(x_n)\right]+\frac{1}{N}\sum_{n=1}^N|x_n|-\frac{1}{2N^2}\sum_{n,m=1}^N|x_n-x_m|\\ &&(\text{the last expression is for coding purpose only})
    \end{eqnarray*}

   \item ($s>1$)
   \begin{enumerate}
       \item 
       i.i.d. standard Normal random variables, the joint pdf 
       $$\Phi(\vx) = \prod\limits_{j=1}^s\Phi_0(x_j) = \prod\limits_{j=1}^s \frac{1}{\sqrt{2\pi}}e^{-x_j^2/2}.$$
       Thus, 
       $$\int_{\reals^s\times \reals^s} K(\vx,\vt)\dif\Phi(\vx)\dif\Phi(\vt) = \left(1+\sqrt{\frac{2}{\pi}}\right)^s,$$
       $$\int_{\reals^d}K(\vx,\vx_n)\dif\Phi(\vx) = \prod\limits_{j=1}^s\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_j|-x_j[\Phi_0(x_j)-1/2]-\phi(x_j)\right].$$
       Thus, the discrepancy becomes:
       \begin{eqnarray*}
 &&[D(P)]^2\\
  &=& \left(1+\sqrt{\frac{2}{\pi}}\right)^s - \frac{2}{N}\sum\limits_{\vx\in P} \prod\limits_{j=1}^s\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_j|-x_j[\Phi_0(x_j)-1/2]-\phi(x_j)\right]\\
  &&+\frac{1}{N^2}\sum_{\vx,\vx'\in P}\prod_{j=1}^s \left[1+\frac{1}{2}|x_j|+\frac{1}{2}|x'_j|-\frac{1}{2}|x_j-x'_j|\right]
\end{eqnarray*}       
   \end{enumerate}

\end{enumerate}

\section{Notes on Issues (1/17/2019)}
$N$ is the sample size and I move the largest point in Sobol sequence to the boundary $1-10^{-15}$. $x$ is the Sobol sequence, $y$ is $x$ with largest point moved to $1-10^{-15}$, and $z$ is the uniform random numbers generated by Matlab. Then, I compare the normal discrepancies after inverse transformation. Here ere are some numerical results I have:
\begin{enumerate}
\item
Overall, the normal discrepancy of transformed $y$ is not very different from that of transformed $x$. 
    \item 
    In one of my simulations, the discrepancy of $y$ is smaller than discrepancy of $z$, but the after inverse transformation, the normal discrepancy of transformed $y$ becomes larger than the normal discrepancy of transformed $z$.
    \item
    I found that the normal discrepancy doesn't change much as the sample size $N$ changes, e.g., when $N=10$, the normal discrepancy of normal random numbers generated by Matlab is 0.6164; when $N=100$, it becomes 0.5765; when $N=1000$, it becomes 0.5647; when $N=10000$, it becomes 0.5642. 
    \item
    What's more, even when we calculate the normal discrepancy of a Sobol sequence (which is uniformly distributed on [0,1]. This sequence should have large normal discrepancy as it doesn't even contain any negative number.), with $N=100$, the normal discrepancy is 0.7571 which is not as large as I expected.
    \item
    This normal discrepancy can be large, e.g. the normal discrepancy of a sample with two points -10 and 10 is 5. However, the normal discrepancy of `randn(100,1)' is about 0.5694, and if we change one point to 10 (10 standard deviation above the mean), the normal discrepancy only changes to about 0.5699. If we use a smaller sample, e.g., the normal discrepancy of `randn(10,1)' is about 0.5878,   and if we change one point to 10, the normal discrepancy changes to about 0.6992. So, I think when the sample size is large, the normal discrepancy is not sensitive to the change of one point. 
\end{enumerate}
What Lulu and I suspect is that the problem lies in the kernel we choose. This normal discrepancy doesn't really distinguish the samples well.

Also, I think the discrepancy may become more different if we have a larger dimension and the sample is more sparse. But, note that for 1-d situation, the centered $L_2$ uniform discrepancy still distinguishes the samples very well even when the sample size is large.

\section{A Motivation Example}
Consider dimension of input factor $s=10$, and sample size $N=2^10$. Move the the point that is nearest to the origin in Sobol sequence $\vx$ to $(10^{-15},...,10^{-15})$, and the new sequence is denoted by $\vy$. $\vz$ is a sample of uniform random points of size $N$. The following table includes the uniform discrepancy and the normal discrepancy after inverse distribution transformation.
% Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{table}[H]
  \centering
    \begin{tabular}{ccc}
     Sample     & Uniform Discrepancy & Normal Discrepancy \\
    \hline
    $\vx$     & 0.0285 & 18.5713 \\
   $\vy$     & 0.0292 & 58.8191 \\
    $\vz$     & 0.0802 & 18.5748 \\
    \end{tabular}%
\end{table}% 

\section{Coordinate Exchange}
When we remove one point $\vx^i = [x^i_{1},x^i_{2},...,x^i_{s}]$ from the sample, the change in the squared discrepancy is:
\begin{eqnarray*}
&&D^2(P\backslash \vx^i)-D^2(P)\\
&=& -\frac{2}{N-1}\sum\limits_{\vx\in P\backslash \vx^i} \prod\limits_{j=1}^s\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_j|-x_j[\Phi_0(x_j)-1/2]-\phi(x_j)\right]\\
  &&+\frac{1}{(N-1)^2}\sum_{\vx,\vx'\in P\backslash\vx^i}\prod_{j=1}^s \left[1+\frac{1}{2}|x_j|+\frac{1}{2}|x'_j|-\frac{1}{2}|x_j-x'_j|\right]\\
  &&+\frac{2}{N}\sum\limits_{\vx\in P} \prod\limits_{j=1}^s\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_j|-x_j[\Phi_0(x_j)-1/2]-\phi(x_j)\right]\\
  &&-\frac{1}{N^2}\sum_{\vx,\vx'\in P}\prod_{j=1}^s \left[1+\frac{1}{2}|x_j|+\frac{1}{2}|x'_j|-\frac{1}{2}|x_j-x'_j|\right]\\
  &=& -\frac{2}{N-1}\sum\limits_{\vx\in P} \prod\limits_{j=1}^s\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_j|-x_j[\Phi_0(x_j)-1/2]-\phi(x_j)\right]\\
  &&+\frac{1}{(N-1)^2}\sum_{\vx,\vx'\in P}\prod_{j=1}^s \left[1+\frac{1}{2}|x_j|+\frac{1}{2}|x'_j|-\frac{1}{2}|x_j-x'_j|\right]\\
  &&+\frac{2}{N-1}\prod\limits_{j=1}^s\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x^i_{j}|-x_j[\Phi_0(x^i_{j})-1/2]-\phi(x^i_{j})\right]\\
  && - \frac{1}{(N-1)^2}\left(2\sum_{\vx'\in P\backslash \vx^i}\prod_{j=1}^s \left[1+\frac{1}{2}|x^i_{j}|+\frac{1}{2}|x'_j|-\frac{1}{2}|x^i_{j}-x'_j|\right]+\prod_{j=1}^s\left[1+|x^i_{j}|\right]\right)\\
  &&+\frac{2}{N}\sum\limits_{\vx\in P} \prod\limits_{j=1}^s\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_j|-x_j[\Phi_0(x_j)-1/2]-\phi(x_j)\right]\\
  &&-\frac{1}{N^2}\sum_{\vx,\vx'\in P}\prod_{j=1}^s \left[1+\frac{1}{2}|x_j|+\frac{1}{2}|x'_j|-\frac{1}{2}|x_j-x'_j|\right]\\
  &=&  -\frac{2}{N(N-1)}\sum\limits_{\vx\in P} \prod\limits_{j=1}^s\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_j|-x_j[\Phi_0(x_j)-1/2]-\phi(x_j)\right]\\
  && +\frac{2N-1}{N^2(N-1)^2} \sum_{\vx,\vx'\in P}\prod_{j=1}^s \left[1+\frac{1}{2}|x_j|+\frac{1}{2}|x'_j|-\frac{1}{2}|x_j-x'_j|\right]\\
&&+\frac{2}{N-1}\prod\limits_{j=1}^s\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x^i_{j}|-x_j[\Phi_0(x^i_{j})-1/2]-\phi(x^i_{j})\right]\\
  && - \frac{1}{(N-1)^2}\left(2\sum_{\vx'\in P\backslash\vx^i}\prod_{j=1}^s \left[1+\frac{1}{2}|x^i_{j}|+\frac{1}{2}|x'_j|-\frac{1}{2}|x^i_{j}-x'_j|\right]+\prod_{j=1}^s\left[1+|x^i_{j}|\right]\right)\\
\end{eqnarray*}

Define the row deletion function when we remove a point $\vx_i$ as
\begin{eqnarray}\label{eq:rowdelection}
d_r(\vx^i) &=& -2\prod\limits_{j=1}^s\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x^i_{j}|-x_j[\Phi_0(x^i_{j})-1/2]-\phi(x^i_{j})\right]\\ \nonumber
  && + \frac{1}{N-1}\left(2\sum_{\vx'\in P}\prod_{j=1}^s \left[1+\frac{1}{2}|x^i_{j}|+\frac{1}{2}|x'_j|-\frac{1}{2}|x^i_{j}-x'_j|\right]-\prod_{j=1}^s\left[1+|x^i_{j}|\right]\right)
\end{eqnarray}
(Note: The elements of the first and third tensor products are stored in the $i$th row of the sample matrix. The elements in the sum are stored in the $i$th column of the distance matrix $D$.)

Sample the index $i^*$ from $\{1,...,N\}$ with probability $
\frac{d_r(\vx^i)}{\sum\limits_{j=1}^Nd_r(\vx^j)}$.

The column deletion function for the $j$th column ($X_k$) of the sample is:
\begin{eqnarray}
d_c(X_k) &=& D^2(P)-D^2(P') \nonumber\\
&=& -2\sum_{\vx\in P}\prod\limits_{\substack{j=1\\j\neq k}}^s\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_{j}|-x_j[\Phi_0(x_{j})-1/2]-\phi(x_{j})\right]\nonumber\\ 
&&\left(\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_{k}|-x_k[\Phi_0(x_{k})-1/2]-\phi(x_{k})\right)\nonumber\\
&&+\frac{1}{N}\sum_{\vx,\vx'\in P}\prod_{\substack{j=1\\j\neq k}}^s \left[1+\frac{1}{2}|x_j|+\frac{1}{2}|x'_j|-\frac{1}{2}|x_j-x'_j|\right]\left(\frac{1}{2}|x_k|+\frac{1}{2}|x_k'|-\frac{1}{2}|x_k-x_k'|\right)
\end{eqnarray}

(Note that the terms in the tensor product are already stored in the distance matrix and are only calculated once.)

The delta function for exchanging the $i$th point $\vx^i$ with an alternative is (sample changes from $P$ to  $P' = P\backslash\vx^i\cup \vx$):
\begin{eqnarray*}
&&\Delta(\vx^i,\vx)\\
&=& [D(P')]^2-[D(P)]^2\\
&=& \frac{2}{N}\left(\prod\limits_{j=1}^s\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x^i_{j}|-x_j[\Phi_0(x^i_{j})-1/2]-\phi(x^i_{j})\right]\right.\\
&&\left.-\prod\limits_{j=1}^s\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_{j}|-x_j[\Phi_0(x_{j})-1/2]-\phi(x_{j})\right]\right)\\
&&+\frac{1}{N^2}\left(2\sum_{\vz\in P'}\prod_{j=1}^s \left[1+\frac{1}{2}|x_{j}|+\frac{1}{2}|z_j|-\frac{1}{2}|x_{j}-z_j|\right]-\prod_{j=1}^s\left[1+|x_{j}|\right]\right.\\
&& - \left.2\sum_{\vz\in P}\prod_{j=1}^s \left[1+\frac{1}{2}|x^i_{j}|+\frac{1}{2}|z_j|-\frac{1}{2}|x^i_{j}-z_j|\right]+\prod_{j=1}^s\left[1+|x^i_{j}|\right]\right)
\end{eqnarray*}

If only one coordinate $j^*$ of the point $\vx^{i^*}$ is allowed to change, the delta function for exchanging $x_{{i^*},{j^*}}$ with $x\in \mathbb{R}$ is:
\begin{eqnarray*}
&&\Delta(x_{{i^*},{j^*}}, x)\\
&=& \frac{2}{N}\prod\limits_{\substack{j=1,\\j\neq j^*}}^s\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x^{i^*}_{j}|-x_j[\Phi_0(x^{i^*}_{j})-1/2]-\phi(x^{i^*}_{j})\right]\\
&&\left[\frac{1}{2}\left(|x|-|x_{{i^*},{j^*}}|+x-x_{{i^*},{j^*}}\right)-x\Phi_0(x)+x_{{i^*},{j^*}}\Phi_0(x_{{i^*},{j^*}})-\phi(x)+\phi(x_{{i^*},{j^*}})\right]\\
&&+\frac{1}{N^2}\left(\sum_{\vz\in P\backslash \vx^{i^*}}\prod_{\substack{j=1,\\j\neq j^*}}^s\left[1+\frac{1}{2}|x_{j}|+\frac{1}{2}|z_j|-\frac{1}{2}|x_{j}-z_j|\right]\left[|x|-|x-z_{j^*}|-|x_{i^*,j^*}|+|x_{i^*,j^*}-z_{j^*}|\right]\right.\\
&&+\left.\prod_{\substack{j=1,\\j\neq j^*}}^s[1+|x_{i^*,j}|](|x|-|x_{i^*,j^*}|)\right)
\end{eqnarray*}
After choosing a particular dimension of a particular point, it becomes a univariate optimization problem of minimizing the delta function $\Delta(x_{{i^*},{j^*}}, x)$.
\newpage
\section{Numerical Results}
The proposed algorithm works as follows:
\begin{enumerate}
    \item 
    Generate a Sobol sequence of size $N$ with dimension $d$.
    \item
    Use inverse distribution transformation to transform uniform random numbers to generate normal random numbers.
    \item
    Use coordinate exchange algorithm to minimize the normal discrepancy.
\end{enumerate}

\underline{Examples}:
\begin{enumerate}
    \item 
    ($d=5, n=50$)
\begin{figure}[H]
\centering
{\includegraphics[width=8cm]{d5n50.pdf}}
\end{figure}
\begin{figure}[H]
\centering
{\includegraphics[width=8cm]{d5n50_invsobol.pdf}}
\end{figure}

\end{enumerate}

\end{document}

### 2019-04-21 referenc.tex
Initial Overleaf Import

%%%%%%%%%%%%%%%%%%%%%%%% referenc.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% sample references
% %
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%%%%%%%%%% Springer-Verlag %%%%%%%%%%%%%%%%%%%%%%%%%%
%
% BibTeX users please use
% \bibliographystyle{}
% \bibliography{}
%
\biblstarthook{References may be \textit{cited} in the text either by number (preferred) or by author/year.\footnote{Make sure that all references from the list are cited in the text. Those not cited should be moved to a separate \textit{Further Reading} section or chapter.} The reference list should ideally be \textit{sorted} in alphabetical order -- even if reference numbers are used for the their citation in the text. If there are several works by the same author, the following order should be used: 
\begin{enumerate}
\item all works by the author alone, ordered chronologically by year of publication
\item all works by the author with a coauthor, ordered alphabetically by coauthor
\item all works by the author with several coauthors, ordered chronologically by year of publication.
\end{enumerate}
The \textit{styling} of references\footnote{Always use the standard abbreviation of a journal's name according to the ISSN \textit{List of Title Word Abbreviations}, see \url{http://www.issn.org/en/node/344}} depends on the subject of your book:
\begin{itemize}
\item The \textit{two} recommended styles for references in books on \textit{mathematical, physical, statistical and computer sciences} are depicted in ~\cite{science-contrib, science-online, science-mono, science-journal, science-DOI} and ~\cite{phys-online, phys-mono, phys-journal, phys-DOI, phys-contrib}.
\item Examples of the most commonly used reference style in books on \textit{Psychology, Social Sciences} are~\cite{psysoc-mono, psysoc-online,psysoc-journal, psysoc-contrib, psysoc-DOI}.
\item Examples for references in books on \textit{Humanities, Linguistics, Philosophy} are~\cite{humlinphil-journal, humlinphil-contrib, humlinphil-mono, humlinphil-online, humlinphil-DOI}.
\item Examples of the basic Springer style used in publications on a wide range of subjects such as \textit{Computer Science, Economics, Engineering, Geosciences, Life Sciences, Medicine, Biomedicine} are ~\cite{basic-contrib, basic-online, basic-journal, basic-DOI, basic-mono}. 
\end{itemize}
}

\begin{thebibliography}{99.}%
% and use \bibitem to create references.
%
% Use the following syntax and markup for your references if 
% the subject of your book is from the field 
% "Mathematics, Physics, Statistics, Computer Science"
%
% Contribution 
\bibitem{science-contrib} Broy, M.: Software engineering --- from auxiliary to key technologies. In: Broy, M., Dener, E. (eds.) Software Pioneers, pp. 10-13. Springer, Heidelberg (2002)
%
% Online Document
\bibitem{science-online} Dod, J.: Effective substances. In: The Dictionary of Substances and Their Effects. Royal Society of Chemistry (1999) Available via DIALOG. \\
\url{http://www.rsc.org/dose/title of subordinate document. Cited 15 Jan 1999}
%
% Monograph
\bibitem{science-mono} Geddes, K.O., Czapor, S.R., Labahn, G.: Algorithms for Computer Algebra. Kluwer, Boston (1992) 
%
% Journal article
\bibitem{science-journal} Hamburger, C.: Quasimonotonicity, regularity and duality for nonlinear systems of partial differential equations. Ann. Mat. Pura. Appl. \textbf{169}, 321--354 (1995)
%
% Journal article by DOI
\bibitem{science-DOI} Slifka, M.K., Whitton, J.L.: Clinical implications of dysregulated cytokine production. J. Mol. Med. (2000) doi: 10.1007/s001090000086 
%
\bigskip

% Use the following (APS) syntax and markup for your references if 
% the subject of your book is from the field 
% "Mathematics, Physics, Statistics, Computer Science"
%
% Online Document
\bibitem{phys-online} J. Dod, in \textit{The Dictionary of Substances and Their Effects}, Royal Society of Chemistry. (Available via DIALOG, 1999), 
\url{http://www.rsc.org/dose/title of subordinate document. Cited 15 Jan 1999}
%
% Monograph
\bibitem{phys-mono} H. Ibach, H. L\"uth, \textit{Solid-State Physics}, 2nd edn. (Springer, New York, 1996), pp. 45-56 
%
% Journal article
\bibitem{phys-journal} S. Preuss, A. Demchuk Jr., M. Stuke, Appl. Phys. A \textbf{61}
%
% Journal article by DOI
\bibitem{phys-DOI} M.K. Slifka, J.L. Whitton, J. Mol. Med., doi: 10.1007/s001090000086
%
% Contribution 
\bibitem{phys-contrib} S.E. Smith, in \textit{Neuromuscular Junction}, ed. by E. Zaimis. Handbook of Experimental Pharmacology, vol 42 (Springer, Heidelberg, 1976), p. 593
%
\bigskip
%
% Use the following syntax and markup for your references if 
% the subject of your book is from the field 
% "Psychology, Social Sciences"
%
%
% Monograph
\bibitem{psysoc-mono} Calfee, R.~C., \& Valencia, R.~R. (1991). \textit{APA guide to preparing manuscripts for journal publication.} Washington, DC: American Psychological Association.
%
% Online Document
\bibitem{psysoc-online} Dod, J. (1999). Effective substances. In: The dictionary of substances and their effects. Royal Society of Chemistry. Available via DIALOG. \\
\url{http://www.rsc.org/dose/Effective substances.} Cited 15 Jan 1999.
%
% Journal article
\bibitem{psysoc-journal} Harris, M., Karper, E., Stacks, G., Hoffman, D., DeNiro, R., Cruz, P., et al. (2001). Writing labs and the Hollywood connection. \textit{J Film} Writing, 44(3), 213--245.
%
% Contribution 
\bibitem{psysoc-contrib} O'Neil, J.~M., \& Egan, J. (1992). Men's and women's gender role journeys: Metaphor for healing, transition, and transformation. In B.~R. Wainrig (Ed.), \textit{Gender issues across the life cycle} (pp. 107--123). New York: Springer.
%
% Journal article by DOI
\bibitem{psysoc-DOI}Kreger, M., Brindis, C.D., Manuel, D.M., Sassoubre, L. (2007). Lessons learned in systems change initiatives: benchmarks and indicators. \textit{American Journal of Community Psychology}, doi: 10.1007/s10464-007-9108-14.
%
%
% Use the following syntax and markup for your references if 
% the subject of your book is from the field 
% "Humanities, Linguistics, Philosophy"
%
\bigskip
%
% Journal article
\bibitem{humlinphil-journal} Alber John, Daniel C. O'Connell, and Sabine Kowal. 2002. Personal perspective in TV interviews. \textit{Pragmatics} 12:257--271
%
% Contribution 
\bibitem{humlinphil-contrib} Cameron, Deborah. 1997. Theoretical debates in feminist linguistics: Questions of sex and gender. In \textit{Gender and discourse}, ed. Ruth Wodak, 99--119. London: Sage Publications.
%
% Monograph
\bibitem{humlinphil-mono} Cameron, Deborah. 1985. \textit{Feminism and linguistic theory.} New York: St. Martin's Press.
%
% Online Document
\bibitem{humlinphil-online} Dod, Jake. 1999. Effective substances. In: The dictionary of substances and their effects. Royal Society of Chemistry. Available via DIALOG. \\
http://www.rsc.org/dose/title of subordinate document. Cited 15 Jan 1999
%
% Journal article by DOI
\bibitem{humlinphil-DOI} Suleiman, Camelia, Daniel C. OConnell, and Sabine Kowal. 2002. `If you and I, if we, in this later day, lose that sacred fire...´': Perspective in political interviews. \textit{Journal of Psycholinguistic Research}. doi: 10.1023/A:1015592129296.
%
%
%
\bigskip
%
%
% Use the following syntax and markup for your references if 
% the subject of your book is from the field 
% "Computer Science, Economics, Engineering, Geosciences, Life Sciences"
%
%
% Contribution 
\bibitem{basic-contrib} Brown B, Aaron M (2001) The politics of nature. In: Smith J (ed) The rise of modern genomics, 3rd edn. Wiley, New York 
%
% Online Document
\bibitem{basic-online} Dod J (1999) Effective Substances. In: The dictionary of substances and their effects. Royal Society of Chemistry. Available via DIALOG. \\
\url{http://www.rsc.org/dose/title of subordinate document. Cited 15 Jan 1999}
%
% Journal article by DOI
\bibitem{basic-DOI} Slifka MK, Whitton JL (2000) Clinical implications of dysregulated cytokine production. J Mol Med, doi: 10.1007/s001090000086
%
% Journal article
\bibitem{basic-journal} Smith J, Jones M Jr, Houghton L et al (1999) Future of health insurance. N Engl J Med 965:325--329
%
% Monograph
\bibitem{basic-mono} South J, Blass B (2001) The future of modern genomics. Blackwell, London 
%
\end{thebibliography}

### 2019-04-21 PlotKernel.m
Plotting function

@@ -1,0 +1,44 @@
+%% Plot of kernel
+
+clearvars
+format compact %eliminate blank lines in output
+close all %close all figures
+set(0,'defaultaxesfontsize',24,'defaulttextfontsize',24, ... %make font larger
+      'defaultLineLineWidth',5, ... %thick lines
+      'defaultLineMarkerSize',40) %big dots
+LatexInterpreter %LaTeX interpreted axis labels, tick labels, and legends
+%Next are MATLAB's plot colors
+MATLABBlue = [0, 0.447, 0.741];
+MATLABOrange = [0.85,  0.325, 0.098];
+MATLABPurple = [0.494,  0.184, 0.556];
+MATLABGreen = [0.466,  0.674, 0.188];
+MATLABDkOrange = [0.85,  0.325, 0.098]*0.6;
+MATLABLtOrange = 0.5*[0.85,  0.325, 0.098] + 0.5*[1 1 1];
+MATLABCyan = [0.3010, 0.7450, 0.9330];
+MATLABMaroon = [0.6350, 0.0780, 0.1840];
+MATLABYellow = [0.9290, 0.6940, 0.1250];
+blackSequence = repmat({[0 0 0]},1,7);
+colorSequence = {MATLABBlue, MATLABOrange, MATLABYellow, MATLABPurple, ...
+   MATLABGreen, MATLABCyan, MATLABMaroon};
+noYcolorSequence = {MATLABBlue, MATLABOrange, MATLABPurple, ...
+   MATLABGreen, MATLABCyan, MATLABMaroon};
+nColor = length(colorSequence);
+markerSequence = {'o','s','d','^','v','h'};
+markerSize = {15,15,15,15,15,15};
+nMarker = length(markerSequence);
+lineSequence = {'-','--',':','-.'};
+nLine = length(lineSequence);
+
+kerFun = @(t,x) 1 + abs(t) + abs(x) - abs(x-t);
+
+x = (-3:0.002:3)';
+
+xcent = [-3 -2 -1 1 2 3];
+
+y = kerFun(x,xcent);
+plot(x,y,'-')
+axis([-3 3 0 7])
+xlabel('$x$')
+ylabel('$K(x,t), \ t = -3, -2, \ldots, 3$')
+print('-depsc','KernelPict.eps')
+

### 2019-04-21 PlotKernel.m
more plots

@@ -31,14 +31,27 @@ nLine = length(lineSequence);
 
 kerFun = @(t,x) 1 + abs(t) + abs(x) - abs(x-t);
 
+
+%1-D plot
 x = (-3:0.002:3)';
-
 xcent = [-3 -2 -1 1 2 3];
-
 y = kerFun(x,xcent);
 plot(x,y,'-')
 axis([-3 3 0 7])
 xlabel('$x$')
-ylabel('$K(x,t), \ t = -3, -2, \ldots, 3$')
+ylabel('$K(t,x), \ t = -3, -2, \ldots, 3$')
 print('-depsc','KernelPict.eps')
+
+%3-D plot
+figure
+x = (-3:0.01:3)';
+[xx,yy] = meshgrid(x,x);
+z = kerFun(xx,yy);
+surf(xx,yy,z,'facecolor','interp','EdgeColor','None')
+axis([-3 3 -3 3 0 7])
+xlabel('$t$')
+ylabel('$x$')
+zlabel('$K(t,x)$')
+print('-depsc','Kernel3DPict.eps')
+
 

### 2019-04-22 PlotKernel.m
revised figures

@@ -29,7 +29,7 @@ nMarker = length(markerSequence);
 lineSequence = {'-','--',':','-.'};
 nLine = length(lineSequence);
 
-kerFun = @(t,x) 1 + abs(t) + abs(x) - abs(x-t);
+kerFun = @(t,x) 1 + 0.5*(abs(t) + abs(x) - abs(x-t));
 
 
 %1-D plot
@@ -37,7 +37,7 @@ x = (-3:0.002:3)';
 xcent = [-3 -2 -1 1 2 3];
 y = kerFun(x,xcent);
 plot(x,y,'-')
-axis([-3 3 0 7])
+axis([-3 3 0 4])
 xlabel('$x$')
 ylabel('$K(t,x), \ t = -3, -2, \ldots, 3$')
 print('-depsc','KernelPict.eps')
@@ -48,7 +48,7 @@ x = (-3:0.01:3)';
 [xx,yy] = meshgrid(x,x);
 z = kerFun(xx,yy);
 surf(xx,yy,z,'facecolor','interp','EdgeColor','None')
-axis([-3 3 -3 3 0 7])
+axis([-3 3 -3 3 0 4])
 xlabel('$t$')
 ylabel('$x$')
 zlabel('$K(t,x)$')

### 2019-04-22 Draft_Inv.tex

@@
 \usepackage{url}
+\usepackage{algpseudocode}
 \usepackage{natbib}
@@
 \newcommand{\vx}{\boldsymbol{x}}
+\newcommand{\vX}{\boldsymbol{X}}
 \newcommand{\vt}{\boldsymbol{t}}
@@
 \newcommand{\vy}{\boldsymbol{y}}
+\newcommand{\mX}{{\mathsf X}}
 \newcommand{\vinfty}{\boldsymbol{\infty}}
@@
 \DeclareMathOperator{\sign}{sign}
+\DeclareMathOperator{\argmax}{argmax}
 \newcommand{\Udes}{\mathcal{U}}
@@
 \newcommand{\cm}{\mathcal{M}}
+\newcommand{\ch}{\mathcal{H}}
 \newcommand{\Ftar}{F}
@@
 \newcommand{\bbone}{\mathbbm{1}}
+\newcommand{\Ex}{\mathbb{E}}
 \newcommand{\ip}[3][{}]{\ensuremath{\left \langle #2, #3 \right \rangle_{#1}}}
 \newcommand{\norm}[2][{}]{\ensuremath{\left \lVert #2 \right \rVert}_{#1}}
+\DeclareMathOperator{\cov}{cov}
 
@@
 Note that $\Ftar$ may differ from $F_u$ because $\Omega \ne \cube$ and/or $\Ftar$ is non-uniform.  
-A natural transformation, $\vPsi$, when $\Ftar$ has independent marginals is the inverse distribution transformation:
+A natural transformation, $\vPsi(\vu)=[\Psi_1(u_1),\ldots,\Psi_d(u_d)]$, when $\Ftar$ has independent marginals is the inverse distribution transformation:
 \begin{equation}\label{eq:inverse}
@@
 Experimental design theory based on  discrepancy assumes an experimental region, $\Omega$, and a target probability distribution, $\Ftar:\Omega \to [0,1]$, which is known a priori.
-In many of our examples, we assume that $\Ftar$ has a probability density, $\ftar$.
+We assume that $\Ftar$ has a probability density, $\ftar$.
 It is convenient to also work with measures, $\nu$, defined on $\Omega$.
@@
 
-In the remainder of this section we provide three interpretations of the discrepancy---the magnitude of $\Ftar - \FXdes$.
-One interpretation is the norm of $\Ftar - \FXdes$.
-The second interpretation is worst-case cubature error for integrands in a Hilbert space.
-The third interpretation is average case cubature error for stochastic processes.
+Our notation for discrepancy takes the form of 
+\[
+ D(F_{\Xdes},F,K), \ D(\Xdes,F,K), \ D(\Xdes,\varrho,K), \ D(\Xdes,\nu,K), \ D(\nu_{\Xdes},\nu,K), \text{ etc.}, 
+\]
+are all of which mean the same thing.
+The first argument always refers to the design, the second argument always refers to the target, and the third argument is a symmetric, positive definite kernel, which is explained below.
+We abuse the discrepancy notation because sometimes it is convenient to refer to the design as a set, $\Xdes$, other times by its empirical distribution, $F_{\Xdes}$, and other times by its empirical $\nu_{\Xdes}$.
+Likewise sometimes it convenient to refer the target as a probability measure,  $\nu$, other times by its distribution function, $F$, and other times by its density function, $\varrho$.
+
+In the remainder of this section we provide three interpretations of the discrepancy, summarized in Table \ref{tab:ThreeInterpTable}.
+One interpretation is the norm of $\nu - \nu_{\Xdes}$.
+The second and third interpretations consider the problem of evaluating the mean of a random variable $Y=f(\vX)$, or equivalently a multidimensional integral
+\[
+\mu = \Ex(Y) = \Ex[f(\vX)] = \int_{\Omega} f(\vx) \, \varrho(\vx) \, \dif \vx,
+\]
+where $\vX$ is a random vector with density $\varrho$. The second
+interpretation is worst-case cubature error for integrands, $f$, in the unit ball of a Hilbert space.
+The third interpretation is the root mean squared cubature error for integrands, $f$ that are stochastic processes.
+
+\begin{table}
+    \centering
+     \caption{Three interpretations of the discrepancy}
+     \vspace{-3ex}
+\begin{equation*}
+\begin{array}{c@{\qquad}ccc}
+     \text{Kernel Interpretation} & \text{Discrepancy } D(\Xdes,\nu,K) = D(\Xdes,\varrho,K)\\
+     \toprule \\[-1ex]
+     K(\vt,\vx) = \ip[\cm]{\delta_{\vt}}{\delta_{\vx}} & \norm[\cm]{\nu - \nu_{\Xdes}} \\[2ex]
+     f(\vx) = \ip[\ch]{K(\cdot,\vx)}{f} & \displaystyle \sup_{f \in \ch : \norm[\ch]{f} \le 1} \abs{\int_{\Omega} f(\vx) \, \varrho(\vx) \, \dif \vx - \frac 1N \sum_{i=1}^N f(\vx_i)}\\[4ex]
+    K(\vt,\vx) = \cov\bigl(f(\vt), f(\vx) \bigr) & \displaystyle \sqrt{\Ex \abs{\int_{\Omega} f(\vx) \, \varrho(\vx) \, \dif \vx - \frac 1N \sum_{i=1}^N f(\vx_i)}^2}\\
+\end{array}
+\end{equation*}
+    \label{tab:ThreeInterpTable}
+\end{table}
 
@@
 \begin{align} 
-    D^2(\Xdes,\nu,K) & := \norm[\cm]{\nu - \nu_{\Xdes}}^2 = \int_{\Omega \times \Omega} K(\vt,\vx) \, (\nu - \nu_{\Xdes})(\dif \vt) (\nu - \nu_{\Xdes})(\dif \vx) \\
+    D^2(\Xdes,\nu,K) & := \norm[\cm]{\nu - \nu_{\Xdes}}^2 \\
+    \nonumber
+    & = \int_{\Omega \times \Omega} K(\vt,\vx) \, (\nu - \nu_{\Xdes})(\dif \vt) (\nu - \nu_{\Xdes})(\dif \vx) \\
     \nonumber
@@
 \end{align}
-The first argument refers to the design, the second to the target measure, and the third refers to the kernel used to define the kernel used to define the Hilbert space norm for $\cm$.
-The formula for the discrepancy may be written equivalently in terms of the probability density, $\rho$, corresponding to the probability measure, $\varrho$:
+The formula for the discrepancy may be written equivalently in terms of the probability distribution, $F$,  or the probability density, $\varrho$, corresponding to the target probability measure, $\nu$:
 \begin{align}
 \nonumber
-    D^2(\Xdes,\varrho,K)  & = \int_{\Omega \times \Omega} K(\vt,\vx) \, \varrho(\vt) \varrho (\vx) \, \dif \vt\dif \vx\\
+    D^2(\Xdes,F,K)  & = \int_{\Omega \times \Omega} K(\vt,\vx) \, \dif F( \vt) \dif F(\vx)\\
+    & \qquad \qquad - \frac 2N \sum_{i=1}^N \int_{\Omega} K(\vt,\vx_i)  \, \dif F(\vt) + \sum_{i,k=1}^N K(\vx_i,\vx_k), \\
+\nonumber
+   & = \int_{\Omega \times \Omega} K(\vt,\vx) \, \varrho(\vt) \varrho (\vx) \, \dif \vt\dif \vx\\
     & \qquad \qquad - \frac 2N \sum_{i=1}^N \int_{\Omega} K(\vt,\vx_i)  \, \varrho(\vt) \, \dif \vt + \sum_{i,k=1}^N K(\vx_i,\vx_k).
@@
 The equivalent formulas for the discrepancy in \eqref{discDef} depend inherently on the choice of $K$.  That is key to the answering our question \eqref{BigQ}.  A kernel often used is 
-\begin{align}
+\begin{equation} \label{OrigKernel}
      K(\vt,\vx)  = \prod\limits_{j=1}^d\left[1+ |t_j|+ |x_j|- |x_j-t_j|\right].
-\end{align}
+\end{equation}
+This kernel is plotted in Figure \ref{fig:kernelpict} for $d=1$.  Note that for this kernel in one dimension the distance between two Dirac measures is 
+\begin{equation*}
+    \norm[\cm]{\delta_{x} - \delta_{t}} = \sqrt{\abs{x-t}}.
+\end{equation*}
+
+\begin{figure}
+    \centering
+    \includegraphics[height = 4cm]{KernelPict.eps} \qquad
+    \includegraphics[height = 4cm]{Kernel3DPict.eps}
+    \caption{The kernel defined in \eqref{OrigKernel} for $d=1$.}
+    \label{fig:kernelpict}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Definition in Terms of a Norm on a Hilbert Space of Measures}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 We propose an efficient algorithm that assures low normal discrepancy of the generated $d$-dim standard normal random numbers.
+
+In this section, to better illustrate the coordinate exchange method, we represent a $N$ points $d$-dim design $\{\vx_i\}_{i=1}^N$ with a design matrix $$\mX = \left(\begin{array}{c}\vx_1^T\\ \vdots\\\vx_N^T\end{array}\right).$$ We propose using the coordinate exchange method to optimize the normal discrepancy of a current design.
+The coordinate exchange method was first proposed by Meyer and Nachtsheim \cite{meyer1995coordinate}, and it rapidly becomes a widely used algorithm to construct exact optimal designs in experimental design community.
+The coordinate exchange method searches for the ``worst" coordinate $x_{ij}$ of the current design, and replace it with a better coordinate that improves the current design criterion.
+With only one coordinate $x_{ij}$  changeable, optimizing the design criterion becomes essentially a univariate optimization problem that can be solve easily and efficiently.
+In general, with a current design $\mX^{(0)}$ the coordinate exchange method functions as follows:
 \begin{algorithm}[ht]
 \begin{algorithmic}[1]
-\caption{Algorithm to generate a $d$-dim low normal discrepancy sequence}
-\State Start with a $d$-dim low uniform discrepancy sequence, e.g., Sobol sequence 
-\State 
+\caption{Coordinate exchange method}
+\State Set $k=0$.
+\State Compute the row deletion function $d_r(i)$ ($i=1,...,N$) for $N$ rows of $\mX^{(k)}$ and choose the row $i^*$ with the largest row deletion value, i,e, $i^* = \argmax_{i} d_r(i)$. 
+\State Compute the column deletion function $d_c(j)$ ($j=1,...,d$) for $d$ columns of $\mX^{k}$ and choose the column $j^*$ with the largest column deletion value, i.e., $j^* = \argmax_{j} d_c(j)$. 
+\State Solve the univariate nonlinear optimization problem
+$$\max_{x} \Delta(x_{i^*j^*},x),\,\,\,\,\text{s.t.} x\in \mathbb{R},$$
+and denote the optimal solution as $x^*$.
+\If{$\Delta(x_{i^*j^*},x^*)>0$} 
+\State {replace $x_{i^*j^*}$ with $x^*$ and the denote the new design as $\mX^{(k+1)}$.}
+\State {$k=k+1$.}
+\Else 
+\State{terminate the algorithm and conclude the current design is optimal.} 
+\EndIf
 \end{algorithmic}
 \end{algorithm}
+
+\begin{algorithm}[ht]
+\begin{algorithmic}[2]
+\caption{Generate a $d$-dim low normal discrepancy sequence}
+\State Start with a $d$-dim low uniform discrepancy design $\{\vu_i\}_{i=1}^N$, e.g., Sobol sequence.
+\State Perform inverse distribution transformation on $\{\vu_i\}_{i=1}^N$ to generate $d$-dim standard normal design $\{\vx_i\}_{i=1}^N$.
+\State Improve the design $\{\vx_i\}_{i=1}^N$ with coordinate exchange algorithm by minimizing its the normal discrepancy.
+\end{algorithmic}
+\end{algorithm}
+
 \section{Simulation}

### 2019-05-18 Draft_Inv.tex
Updates from Overleaf

@@
 \usepackage{psfrag,bbm,epsf}
-\usepackage{amssymb, color,enumerate,float,mathtools,algorithmicx}
+\usepackage{xspace,subfigure}
+\usepackage{amssymb, xcolor,enumerate,float,mathtools,algorithmicx}
 \usepackage{algorithm}
@@
 \usepackage{natbib}
+\usepackage{showlabels}
 
@@
 \newcommand{\naturals}{\mathbb{R}}
+\newcommand{\va}{\boldsymbol{a}}
+\newcommand{\vb}{\boldsymbol{b}}
 \newcommand{\vc}{\boldsymbol{c}}
@@
 \newcommand{\vu}{\boldsymbol{u}}
+\newcommand{\vv}{\boldsymbol{v}}
 \newcommand{\vy}{\boldsymbol{y}}
+\newcommand{\fraku}{\mathfrak{u}}
+\newcommand{\frakv}{\mathfrak{v}}
 \newcommand{\mX}{{\mathsf X}}
@@
 \newcommand{\ch}{\mathcal{H}}
+\newcommand{\MATLAB}{\textsc{Matlab}\xspace}
 \newcommand{\Ftar}{F}
@@
 \DeclareMathOperator{\cov}{cov}
+\DeclareMathOperator{\err}{err}
+\newcommand{\unif}{\textup{unif}}
+\newcommand{\normal}{\textup{normal}}
 
@@
 \newcommand{\LK}[1]{{\color{green}Lulu: #1}} %choose your color
-\newcommand{\YL}[1]{{\color{red}Yiou: #1}} %choose your color
+\newcommand{\YL}[1]{{\color{teal}Yiou: #1}} %choose your color
 
@@
 % your contribution title if the original one is too long
-\institute{Yiou Li \at DePaul University, 1 E. Jackson
-Chicago, IL 60604, \email{yli139@depaul.edu}
+\institute{Yiou Li \at DePaul University, 2320 N. Kenmore Avenue, Chicago, IL 60614 \email{yli139@depaul.edu}
 \and Lulu Kang \at Illinois Institute of Technology, 10 W 32nd Street, Chicago, IL 60616 \email{lkang2@iit.edu} 
@@
 
-Low discrepancy designs, $\Udes = \{\vu_i\}_{i=1}^N$, are typically constructed so that their empirical distribution, $F_\Udes$, approximates $F_u$, the uniform distribution on the unit cube, \cube.  
-The discrepancy measures how large $F_u-F_\Udes$ is.
+Low discrepancy designs, $\Udes = \{\vu_i\}_{i=1}^N$, are typically constructed so that their empirical distribution, $F_\Udes$, approximates $F_\unif$, the uniform distribution on the unit cube, \cube.
+The discrepancy measures how large $F_\unif-F_\Udes$ is.
 
@@
 \end{equation}
-Note that $\Ftar$ may differ from $F_u$ because $\Omega \ne \cube$ and/or $\Ftar$ is non-uniform.  
-A natural transformation, $\vPsi(\vu)=[\Psi_1(u_1),\ldots,\Psi_d(u_d)]$, when $\Ftar$ has independent marginals is the inverse distribution transformation:
+Note that $\Ftar$ may differ from $F_\unif$ because $\Omega \ne \cube$ and/or $\Ftar$ is non-uniform.  
+A natural transformation, $\vPsi(\vu)=[\Psi_1(u_1),\ldots,\Psi_d(u_d)]$, when $\Ftar$ has independent marginals, is the inverse distribution transformation:
 \begin{equation}\label{eq:inverse}
-\Psi_j(u_j) = F_j^{-1}(u_j), \quad \text{where } \Ftar(\vx) = F_1(u_1) \cdots F_d(u_d).
+\Psi_j(u_j) = F_j^{-1}(u_j), \quad j =1, \ldots, d, \qquad \text{where } \Ftar(\vx) = F_1(u_1) \cdots F_d(u_d).
 \end{equation}
-A number of transformation methods for different distributions can be found in \cite{devroye2006nonuniform}.
+A number of transformation methods for different distributions can be found in \cite{devroye2006nonuniform}. \FJH{How about Prof. Fang's books?}
 
@@
 \begin{equation} \label{BigQ} \tag{Q}
-\text{\emph{does small $F_u - F_\Udes$ imply small $\Ftar - F_\Xdes$?}}
+\text{\emph{does small $F_\unif - F_\Udes$ imply small $\Ftar - F_\Xdes$?}}
 \end{equation}
@@
 We discuss both cases.  
-For illustrative purposes, we consider the case where $\Ftar$ is the multivariate normal distribution.
+For illustrative purposes, we consider the case where $\Ftar$ is the multivariate standard normal distribution.
 
 In the rest of this chapter, we first explain the discrepancy that measures how large $\Ftar - F_\Xdes$ is and motivate it from three different perspectives.
-Next, we the inverse transformation can lead to inconsistency in terms the discrepancies of the designs before and after transformation.
-We also proposed a remedy method to improve the design in terms of the discrepancy between $\Ftar$ and $F_\Xdes$. 
+Next, we show how the inverse transformation can lead to does not always preserve the low discrepancy of a design.
+We also propose a remedy method to improve the design in terms of the discrepancy between $\Ftar$ and $F_\Xdes$. 
 Numerical examples are used to show the performance of the method.
@@
 \]
-are all of which mean the same thing.
+all of which mean the same thing.
 The first argument always refers to the design, the second argument always refers to the target, and the third argument is a symmetric, positive definite kernel, which is explained below.
-We abuse the discrepancy notation because sometimes it is convenient to refer to the design as a set, $\Xdes$, other times by its empirical distribution, $F_{\Xdes}$, and other times by its empirical $\nu_{\Xdes}$.
-Likewise sometimes it convenient to refer the target as a probability measure,  $\nu$, other times by its distribution function, $F$, and other times by its density function, $\varrho$.
+We abuse the discrepancy notation because sometimes it is convenient to refer to the design as a set, $\Xdes$, other times by its empirical distribution, $F_{\Xdes}$, and other times by its empirical measure, $\nu_{\Xdes}$.
+Likewise, sometimes it is convenient to refer the target as a probability measure,  $\nu$, other times by its distribution function, $F$, and other times by its density function, $\varrho$.
 
 In the remainder of this section we provide three interpretations of the discrepancy, summarized in Table \ref{tab:ThreeInterpTable}.
+These results are derived previously in various places, including \cite{Hic99a}.
 One interpretation is the norm of $\nu - \nu_{\Xdes}$.
 The second and third interpretations consider the problem of evaluating the mean of a random variable $Y=f(\vX)$, or equivalently a multidimensional integral
-\[
+\begin{equation}\label{eq:integration}
 \mu = \Ex(Y) = \Ex[f(\vX)] = \int_{\Omega} f(\vx) \, \varrho(\vx) \, \dif \vx,
-\]
+\end{equation}
 where $\vX$ is a random vector with density $\varrho$. The second
 interpretation is worst-case cubature error for integrands, $f$, in the unit ball of a Hilbert space.
-The third interpretation is the root mean squared cubature error for integrands, $f$ that are stochastic processes.
+The third interpretation is the root mean squared cubature error for integrands, $f$ which are realizations of a stochastic processes.
 
@@
 f(\vx) = \ip[\ch]{K(\cdot,\vx)}{f} & \displaystyle \sup_{f \in \ch : \norm[\ch]{f} \le 1} \abs{\int_{\Omega} f(\vx) \, \varrho(\vx) \, \dif \vx - \frac 1N \sum_{i=1}^N f(\vx_i)}\\[4ex]
-    K(\vt,\vx) = \cov\bigl(f(\vt), f(\vx) \bigr) & \displaystyle \sqrt{\Ex \abs{\int_{\Omega} f(\vx) \, \varrho(\vx) \, \dif \vx - \frac 1N \sum_{i=1}^N f(\vx_i)}^2}\\
+K(\vt,\vx) = \cov\bigl(f(\vt), f(\vx) \bigr) & \displaystyle \sqrt{\Ex \abs{\int_{\Omega} f(\vx) \, \varrho(\vx) \, \dif \vx - \frac 1N \sum_{i=1}^N f(\vx_i)}^2}\\\bottomrule
 \end{array}
@@
 \subsection{Definition in Terms of a Norm on a Hilbert Space of Measures}
+\label{sec:HilbertMeasures}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{equation}
+The squared distance between two Dirac measures in $\cm$ is then
+\begin{equation} \label{distDelta}
+   \norm[\cm]{\delta_{\vx} - \delta_{\vt}}^2 = K(\vt,\vt) - 2K(\vt,\vx) + K(\vx,\vx), \qquad \forall \vt, \vx \in \Omega.
+\end{equation}
+
 It is straightforward to show that $ K$ is symmetric in its arguments and positive-definite, namely:
-\begin{gather*}
+\begin{subequations} \label{eq:sympd}
+\begin{gather}
 K(\vx, \vt) = K(\vt, \vx) \qquad \forall \vt, \vx\in \Omega,\\
-\sum\limits_{i, k=1}^N c_i c_k  K(\vx_i,\vx_k) > 0, \qquad \forall N\in\mathbb{N}, \  \vc \in\mathbb{R}^N, \ \vc \ne \vzero,  \ \Xdes \in\Omega.
-\end{gather*}
-For arbitrary measures $\lambda, \nu \in \cm$, their inner product can be expressed in terms of a double integral of the kernel, $K$:
+\sum\limits_{i, k=1}^N c_i c_k  K(\vx_i,\vx_k) > 0, \qquad \forall N\in\mathbb{N}, \  \vc \in\mathbb{R}^N, \ \vc \ne \vzero,  \ \Xdes \subset \Omega.
+\end{gather}
+\end{subequations}
+The inner product of arbitrary measures $\lambda, \nu \in \cm$ can be expressed in terms of a double integral of the kernel, $K$:
 \begin{equation} \label{ipMdef}
@@
 
-The discrepancy of the design $\Xdes$ with respect to the target probability measure $\nu$ using the kernel $K$, can be defined as the norm of the difference between the target probability measure, $\nu$, and the empirical probability measure for $\Xdes$:
-\begin{subequations} \label{discDef}
+The discrepancy of the design $\Xdes$ with respect to the target probability measure $\nu$ using the kernel $K$ can be defined as the norm of the difference between the target probability measure, $\nu$, and the empirical probability measure for $\Xdes$:
+\begin{subequations} \label{eq:discDef}
 \begin{align} 
@@
     \nonumber
-    & = \int_{\Omega \times \Omega} K(\vt,\vx) \, \nu(\dif \vt) \nu (\dif \vx)\\
-    & \qquad \qquad - \frac 2N \sum_{i=1}^N \int_{\Omega} K(\vt,\vx_i) \, \nu(\dif \vt) + \sum_{i,k=1}^N K(\vx_i,\vx_k).
+    & = \int_{\Omega \times \Omega} K(\vt,\vx) \, \nu(\dif \vt) \nu (\dif \vx) - \frac 2N \sum_{i=1}^N \int_{\Omega} K(\vt,\vx_i) \, \nu(\dif \vt)\\
+    & \qquad \qquad  + \frac{1}{N^2} \sum_{i,k=1}^N K(\vx_i,\vx_k).
 \end{align}
@@
 \nonumber
-    D^2(\Xdes,F,K)  & = \int_{\Omega \times \Omega} K(\vt,\vx) \, \dif F( \vt) \dif F(\vx)\\
-    & \qquad \qquad - \frac 2N \sum_{i=1}^N \int_{\Omega} K(\vt,\vx_i)  \, \dif F(\vt) + \sum_{i,k=1}^N K(\vx_i,\vx_k), \\
+    D^2(\Xdes,F,K)  & = \int_{\Omega \times \Omega} K(\vt,\vx) \, \dif F( \vt) \dif F(\vx) - \frac 2N \sum_{i=1}^N \int_{\Omega} K(\vt,\vx_i)  \, \dif F(\vt) \\ &\qquad \qquad  + \frac{1}{N^2}  \sum_{i,k=1}^N K(\vx_i,\vx_k), \\
 \nonumber
-   & = \int_{\Omega \times \Omega} K(\vt,\vx) \, \varrho(\vt) \varrho (\vx) \, \dif \vt\dif \vx\\
-    & \qquad \qquad - \frac 2N \sum_{i=1}^N \int_{\Omega} K(\vt,\vx_i)  \, \varrho(\vt) \, \dif \vt + \sum_{i,k=1}^N K(\vx_i,\vx_k).
+   & = \int_{\Omega \times \Omega} K(\vt,\vx) \, \varrho(\vt) \varrho (\vx) \, \dif \vt\dif \vx - \frac 2N \sum_{i=1}^N \int_{\Omega} K(\vt,\vx_i)  \, \varrho(\vt) \, \dif \vt \\
+    & \qquad \qquad + \frac{1}{N^2}  \sum_{i,k=1}^N K(\vx_i,\vx_k).
 \end{align}
 \end{subequations}
-Here, and below we abuse the notation for discrepancy, but we always preserve the meaning of the first second and third arguments.  Thus,
-\[
-D(\Xdes,\nu,K), \ D(\Xdes,F,K), \ D(\Xdes,\varrho,K), \ D(\nu_{\Xdes},\nu,K), \text{ etc.} 
-\]
-are all equivalent.
 
-The equivalent formulas for the discrepancy in \eqref{discDef} depend inherently on the choice of $K$.  That is key to the answering our question \eqref{BigQ}.  A kernel often used is 
-\begin{equation} \label{OrigKernel}
-     K(\vt,\vx)  = \prod\limits_{j=1}^d\left[1+ |t_j|+ |x_j|- |x_j-t_j|\right].
+The formulas for the discrepancy in \eqref{eq:discDef} depend inherently on the choice of $K$.  That is key to answering our question \eqref{BigQ}.  An often used kernel is 
+\begin{equation} \label{eq:OrigKernel}
+     K(\vt,\vx)  = \prod\limits_{j=1}^d\left[1+ \frac 12 \left(|t_j|+ |x_j|- |x_j-t_j| \right)\right].
 \end{equation}
-This kernel is plotted in Figure \ref{fig:kernelpict} for $d=1$.  Note that for this kernel in one dimension the distance between two Dirac measures is 
+This kernel is plotted in Figure \ref{fig:kernelpict} for $d=1$.  Note that for this kernel in one dimension the distance between two Dirac measures by \eqref{distDelta} is 
 \begin{equation*}
@@
     \includegraphics[height = 4cm]{Kernel3DPict.eps}
-    \caption{The kernel defined in \eqref{OrigKernel} for $d=1$.}
+    \caption{The kernel defined in \eqref{eq:OrigKernel} for $d=1$.}
     \label{fig:kernelpict}
@@
 
+The discrepancy for the uniform distribution on the unit cube defined in terms of the above kernel is commonly called the $L^2$ discrepancy and is expressed as
+\begin{align} 
+\nonumber
+    D^2(\Udes,F_\unif,K)
+    & = \int_{(0,1)^d \times (0,1)^d} K(\vt,\vx) \, \dif \vt \dif \vx - \frac 2N \sum_{i=1}^N \int_{(0,1)^d} K(\vt,\vu_i) \, \dif \vt\\
+    \nonumber
+    & \qquad \qquad  + \frac{1}{N^2} \sum_{i,k=1}^N K(\vu_i,\vu_k) \\
+    \nonumber
+    & = \left( \frac 43 \right)^d 
+     - \frac 2N \sum_{i=1}^N \prod_{j=1}^d \left[1 + u_{ij} - \frac{u_{ij}^2}{2} \right] \\
+     & \qquad \qquad + \frac 1{N^2} \sum_{i,k=1}^N \prod_{j=1}^d \left[1+ \min(u_{ij},u_{ik})\right]
+\end{align}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Definition in Terms of a Norm on a Hilbert Space of Measures}
+\subsection{Definition in Terms of a Deterministic Cubature Error Bound}
+\label{sec:DetermBound}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{A Discrepancy Defined for Normal Distribution}
+Now let $(\ch, \ip[\ch]{\cdot}{\cdot})$ be a reproducing kernel Hilbert space (RKHS) of functions \cite{Aro50}, $f: \Omega \rightarrow \mathbb{R}$, which appear as the integrand in \eqref{eq:integration}.
+By definition, the reproducing kernel, $K$, is the unique function defined on $\Omega \times \Omega$ with the properties that $K(\cdot, \vx)\in \ch$ for any $\vx \in \Omega$ and $f(\vx)=\ip[\ch]{K(\cdot,\vx)}{f}$.
+This second property, implies that $K$ reproduces function values via the inner product.
+It can be verified that $K$ is symmetric in its arguments and positive definite as in \eqref{eq:sympd}.
 
-Consider any symmetric and positive semi-definite kernel function $K(\vx,\vt)$ on the experiment region $\Omega$. 
-In other words, the kernel function satisfies 
+The integral $\mu = \int_{\Omega} f(\vx) \, \varrho(\vx) \, \dif \vx$, which was identified as $\Ex[f(\vX)]$ in \eqref{eq:integration}, can be approximated by a sample mean, 
+\begin{equation}\label{eq:cubature}
+\hat{\mu}=\frac{1}{N}\sum_{i=1}^N f(\vx_i).
+\end{equation}
+The quality of this approximation to the integral, or cubature, depends in part on how well the empirical distribution of the design, $\Xdes = \{\vx_i\}_{i=1}^N$, matches the target distribution $F$ associated with the density function $\varrho$.
+
+Define the cubature error as  
+\begin{align}
+\nonumber 
+\err(f,\Xdes) & = \mu - \hat{\mu} = \int_{\Omega} f(\vx)\, \varrho(\vx) \dif \vx -\frac{1}{N}\sum_{i=1}^N f(\vx_i) \\
+& =\int_\Omega f(\vx) \, \dif[F(\vx)-F_{\Xdes}(\vx)]. \label{eq:err}
+\end{align}
+Under modest assumptions on the reproducing kernel,  $\err(\cdot, \Xdes)$ is a bounded, linear functional, so. 
+by the Riesz representation theorem, there exists a unique representer, $\xi \in \ch$, such that 
+\[
+\err(f, \Xdes)=\ip[\ch]{f}{\xi}, \quad \forall f\in \ch.
+\]
+The reproducing kernel allows us to write down an explicit formula for that representer, namely, $\xi(\vx)=\ip[\ch]{K(\cdot,\vx)}{\xi}=\err(K(\cdot,\vx),\Xdes)$.
+By the Cauchy-Schwarz inequality, there is a tight bound on the squared cubature error, namely
+\begin{equation}\label{eq:wcErrA}
+\abs{\err(f,\Xdes)}^2=\ip[\ch]{f}{\xi}^2\leq \norm[\ch]{f}^2 \norm[\ch]{\xi}^2.
+\end{equation}
+The first term on the right describes the contribution to the cubature error made by the nature of the integrand, while the second term describes the contribution made by the quality of the cubature rule.
+
+The square norm of the representer of the error functional is 
 \begin{align*}
-K(\vx, \vt) &= K(\vt, \vx), \,\,\,\forall \vt, \vx\in \Omega,\\
-\sum\limits_{i, k=1}^n c_ic_k & K(\vx_i,\vx_k)\geq 0, \,\,\,\forall n\in\mathbb{N^+}, c_i\in\mathbb{R}, \vx_i\in\Omega.
+\norm[\ch]{\xi}^2& =\ip[\ch]{\xi}{\xi}=\err(\xi,\Xdes) \quad \text{since $\err(\cdot,\Xdes)$ represents the error functional}\\
+& = \err(\err(K(\cdot,\cdot \cdot),\Xdes),\Xdes) \quad \text{since } \xi(\vx)=\err(K(\cdot,\vx),\Xdes)\\
+& =\int_{\Omega\times \Omega} K(\vt,\vx)\dif[F(\vx)-F_{\Xdes}(\vx)] \, \dif[F(\vt)-F_{\Xdes}(\vt)].
 \end{align*}
-The discrepancy of a design $P = \{\vx_i\}_{i=1}^N$ on $\Omega$ with respect to a distribution $\Ftar$ is then defined as
-\begin{equation}\label{eq:Disc}
-D(P) = \left\{\int_{\Omega\times\Omega} K(\vx,\vt)\dif [\Ftar(\vx)-F_{P}(\vx)]\dif [\Ftar(\vt)-F_{P}(\vt)]\right\}^{1/2},
+We can equate this formula for $\norm[\ch]{\xi}^2$ with the formula for $D^2(\Xdes,F,K)$ in  \eqref{eq:discDef}.
+Thus, the tight, worst-case cubature error  bound in \eqref{eq:wcErrA} can be written as
+\begin{equation}\label{eq:wcErrB}
+\abs{\err(f,\Xdes)} \le \norm[\ch]{f} D(\Xdes,F,K).
 \end{equation}
-and thus, 
-\begin{align}\label{eq:Disc2}\nonumber
-[D(P)]^2  =& \int_{\Omega\times\Omega}  K(\vx,\vt)\dif F_{*}(\vx)\dif F_{*}(\vt) \\
-- &\frac{2}{N}\sum\limits_{\vx\in P}\int_{\Omega}K(\vx,\vt)\dif F_{*}(\vt) +\frac{1}{N^2}\sum\limits_{\vx,\vx'\in P}K(\vx,\vx')
+This implies our second interpretation of the discrepancy in Table \ref{tab:ThreeInterpTable}.
+
+We now identify the RKHS for the kernel $K$ defined in \eqref{eq:OrigKernel} Let $(\va,\vb)$ be some $d$ dimensional box containing the origin in the interior or on the boundary.
+For any $\fraku \subseteq \{1, \ldots, d\}$, define $\partial^\fraku f(\vx_\fraku) : = \partial^{|\fraku|}f(\vx_\fraku,\vzero)/\partial \vx_\fraku$, the mixed first-order partial derivative of $f$ with respect to the $x_j$ for $j\in \fraku$, while setting $x_j=0$ for all $j \notin \fraku$.
+Here, $\vx_{\fraku} = (x_j)_{j \in \fraku}$, and $|\fraku|$ denotes the cardinality of $\fraku$.
+By convention, $\partial^{\emptyset}f := f(\vzero)$.
+The inner product for the reproducing kernel $K$ defined in  \eqref{eq:OrigKernel} is defined as
+\begin{align}\label{eq:inner}
+\langle f,g \rangle_{\ch} &:= \sum_{\fraku\subseteq \{1,...,d\}}\int_{(\va,\vb)}\partial^{\fraku}f(\vx_\fraku)\partial^{\fraku}g(\vx_\fraku) \, \dif \vx_\fraku \\
+\nonumber
+& = f(\vzero)g(\vzero)  + \int_{a_1}^{b_1} \partial^{\{1\}}f(x_1)\partial^{\{1\}}g(x_1) \, \dif x_1 \\
+\nonumber 
+& \qquad + \int_{a_2}^{b_2} \partial^{\{2\}}f(x_2)\partial^{\{2\}}g(x_2) \, \dif x_2 + \cdots \\
+\nonumber 
+& \qquad + \int_{a_2}^{b_2} \int_{a_1}^{b_1} \partial^{\{1,2\}}f(x_1,x_2)\partial^{\{1,2\}}g(x_1,x_2) \, \dif x_1 \dif x_2+ \cdots \\
+\nonumber 
+& \qquad + \int_{(\va,\vb)} \partial^{\{1,\ldots, d\}}f(\vx)\partial^{\{1, \ldots, d\}}g(\vx) \, \dif \vx. 
 \end{align}
-In \cite{Hic99a}, it is showed that, any discrepancy determined by a reproducing kernel function $K$ and a distribution $\Ftar$ is a goodness-of-fit statistic that measures how well the empirical distribution $F_P$ of design $P$ approximates the distribution $\Ftar$.
-What's more, the order of computation for evaluating the discrepancy is at worst $\mathcal{O}(N^2)$.
 
- Let $P = \{\vx_i\}_{i=1}^N$ be a design on $\Omega = \mathbb{R}^d$. 
- According to \eqref{eq:Disc2}, the squared discrepancy of the design $P$ with respect to the $d$-dimensional standard multivariate normal probability distribution $N({\bf 0}, {\bf I}_d)$ with cdf $\Phi$ is
-\begin{eqnarray}\label{eqn:discrepancy}\nonumber
-[D(P)]^2 &=& \int_{\Omega\times\Omega} K(\vx,\vt)\dif \Phi(\vx)\dif \Phi(\vt)\\
-&-&\frac{2}{N}\sum_{i=1}^N \int_{\Omega}K(\vx,\vx_i)\dif \Phi(\vx)+\frac{1}{N^2}\sum_{i,k=1}^N K(\vx_i,\vx_k).
-\end{eqnarray}
+To establish that the inner product defined above corresponds to the reproducing kernel  $K$ defined in \eqref{eq:OrigKernel}, we note that
+\begin{align*}
+\partial^{\fraku} K((\vx_u,{\bf 0}),\vt) & =\prod_{j \in \fraku}\frac 12 \left[\sign(x_j) - \sign(x_j - t_j) \right] \\
+& =
+\prod\limits_{j \in \fraku}\sign(t_j) \bbone_{(\min(0,t_j),\max(0,t_j))}(x_j).
+\end{align*}
+Thus, $K(\cdot,\vt)$ possesses sufficient regularity to have finite $\ch$-norm.  Furthermore, $K$ exhibits the reproducing property for the above inner product because
+\begin{align*}
+\MoveEqLeft{\langle K(\cdot,\vt),f \rangle}_{\ch} \\
+&= \sum_{\fraku\subseteq \{1,...,d\}}\int_{(\va,\vb)} \partial^{\fraku}K((\vx_u,{\bf 0}),\vt)\partial^{\fraku}f(\vx_u,{\bf 0})  \, \dif \vx_u \\
+&= \sum_{\fraku\subseteq \{1,...,d\}}\int_{(\va,\vb)}  \prod\limits_{j \in \fraku}\sign(t_j) \bbone_{(\min(0,t_j),\max(0,t_j))}(x_j) \partial^{\fraku}f(\vx_u,{\bf 0})  \, \dif \vx_u \\
+& =     \sum_{\fraku\subseteq \{1,...,d\}}\sum_{\frakv\subseteq \fraku}(-1)^{|\fraku|-|\frakv|}f(\vt_\frakv,{\bf 0})= f(\vt).
+\end{align*}
 
-We need to choose a kernel function that can facilitate the analytical derivation of the discrepancy for both standard normal and uniform distribution. 
-A commonly used discrepancy to measure for the uniform distribution on $[0,1]^d$ is the centered $L_2$ discrepancy \cite{Hic97a} defined as:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Definition in Terms of the Root Mean Squared Cubature Error}
+\label{sec:RandomBound}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Assume $\Omega$ is a measurable subset in $\mathbb{R}^d$ and $F$ is the target probability distribution defined on $\Omega$ as defined earlier. 
+Now, let $f: \Omega \rightarrow \mathbb{R}$ be a stochastic process with a constant pointwise mean, i.e., 
+\[
+\Ex_{f\in \mathcal{A}}[f(\vx)]=m, \qquad \forall \vx\in \Omega,
+\]
+where $\mathcal{A}$ is the sample space for this stochastic process. 
+Now we interpret $K$ as the \emph{covariance kernel} for the stocastic process:
+\[
+K(\vt,\vx):=\Ex_{f\in \mathcal{A}}\left( [f(\vt)-m][f(\vx)-m]\right)=\cov(f(\vt),f(\vx)),\qquad \forall \vt, \vx\in \Omega. 
+\]
+It is straightforward to see that the kernel function is symmetric and positive definite.
+
+Define the error functional $\err(\cdot,\Xdes)$ in the same way as in \eqref{eq:err}.  Now, the mean squared error is 
 \begin{align*}
-[D_2(P)]^2 =& \left(\frac{13}{12}\right)^d - \frac{2}{N}\sum\limits_{\vz\in P}\prod_{j=1}^d \left(1+\frac{1}{2}|z_j-1/2|-1/2|z_j-1/2|^2\right)\\
-\hspace{5ex}&+ \frac{1}{N^2}\sum\limits_{\vz,\vz'\in P}\prod_{j=1}^d\left[1+\frac{1}{2}|z_j-1/2|+\frac{1}{2}|z_j'-1/2|-\frac{1}{2}|z_j-z_j'|\right],    
+&\Ex_{f\in\mathcal{A}}[(\err(f,\Xdes)]^2= \Ex_{f\in\mathcal{A}} \left\{\int_{\Omega}f(\vx)\dif F(\vx)-\frac{1}{N}\sum_{i=1}^N f(\vx_i) \right\}^2\\
+=&\Ex_{f\in\mathcal{A}}\left\{\int_{\Omega}(f(\vx)-m)\dif F(\vx)-\frac{1}{N}\sum_{i=1}^N (f(\vx_i)-m) \right\}^2\\
+=&\int_{\Omega^2}\Ex_{f\in \mathcal{A}}[ (f(\vt)-m)(f(\vx)-m)] \, \dif F(\vt)\dif F(\vx)\\
+&-\frac{2}{N}\sum_{i=1}^N \int_{\Omega} \Ex_{f\in\mathcal{A}}[(f(\vx)-m)(f(\vx_i)-m)]\,\dif F(\vx)\\
+&+\frac{1}{N^2}\sum_{i,k=1}^N\Ex_{f\in\mathcal{A}}[(f(\vx_i)-m)(f(\vx_k)-m)]\\
+=&\int_{\Omega^2}K(\vt,\vx) \, \dif F(\vt)\dif F(\vx)-\frac{2}{N}\sum_{i=1}^N \int_{\Omega} K(\vx, \vx_i)\dif F(\vx)+\frac{1}{N^2} \sum_{i,k=1}^N K(\vx_i,\vx_k). 
+\end{align*}
+Therefore, we can equate the discrepancy $D(\Xdes, F, K)$ defined in \eqref{eq:discDef} as the root mean squared error:
+\[
+D(\Xdes, F, K) =\sqrt{\Ex_{f\in\mathcal{A}}[(\err(f,\Xdes)]^2}=\sqrt{\Ex\abs{\int_{\Omega}f(\vx)\varrho(\vx)\dif \vx-\frac{1}{N}\sum_{i=1}^N f(\vx_i)}^2}.
+\]
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{When Transformed Low Discrepancy Points Also Have Low Discrepancy}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Having motivated the definition of discrepancy in \eqref{eq:discDef} from three perspectives, we now turn our attention to the question posed in \eqref{BigQ}, namely, does a transformation of low discrepancy points with respect to the uniform distribution yield low discrepancy points with respect to the new target distribution.
+In this section, we show a positive result, yet recognize some qualifications.
+
+Consider some symmetric, positive definite kernel, $K_\unif : (0,1)^d \times (0,1)^d \to \reals$, some uniform design $\Udes$, some other domain, $\Omega$, some other target distribution, $F$, and some transformation $\vPsi:(0,1)^d \to \Omega$ as defined in \eqref{eq:transPts}.
+Then the squared discrepancy of the uniform design can be expressed according to \eqref{eq:discDef} as follows:
+\begin{align} 
+\nonumber
+    \MoveEqLeft{D^2(\Udes,F_{\unif},K_\unif)} \\
+    \nonumber
+    & = \int_{(0,1)^d \times (0,1)^d} K_\unif(\vu,\vv) \,  \dif \vu \dif \vv - \frac 2N \sum_{i=1}^N \int_{\Omega} K_\unif(\vu,\vu_i) \, \dif \vu\\
+    \nonumber
+    & \qquad \qquad  + \frac{1}{N^2} \sum_{i,k=1}^N K_\unif(\vu_i,\vu_k) \\
+    \nonumber
+    & = \int_{\Omega \times \Omega} K_\unif(\vPsi^{-1}(\vt),\vPsi^{-1}(\vx)) \, \abs{\frac{\partial \vPsi^{-1}(\vt)}{\partial \vt}} \abs{\frac{\partial \vPsi^{-1}(\vx)}{\partial \vx}} \,\dif \vt \dif \vx \\
+    \nonumber 
+    & \qquad \qquad  - \frac 2N \sum_{i=1}^N \int_{\Omega} K_\unif(\vPsi^{-1}(\vt),\vPsi^{-1}(\vx_i)) \, \abs{\frac{\partial \vPsi^{-1}(\vt)}{\partial \vt}} \, \dif \vt\\
+    \nonumber
+    & \qquad \qquad  + \frac{1}{N^2} \sum_{i,k=1}^N K_\unif(\vPsi^{-1}(\vx_i),\vPsi^{-1}(\vx_k)) \\
+    & = D^2(\Xdes,F,K)
+\end{align}
+where the kernel $K$ is defined as
+\begin{subequations} \label{eq:BigQYes}
+\begin{equation} \label{eq:BigQYesa}
+    K(\vt,\vx) = K_{\unif}(\vPsi^{-1}(\vt),\vPsi^{-1}(\vx))
+\end{equation}
+\emph{and provided that} the density, $\varrho$, corresponding to the target distribution, $F$, satisfies
+\begin{equation} \label{eq:BigQYesb}
+    \varrho(\vx) = \abs{\frac{\partial \vPsi^{-1}(\vx)}{\partial \vx}}
+\end{equation}
+\end{subequations}
+The above argument is summarized in the following theorem.
+
+\begin{theorem}
+Suppose that the design $\Xdes$ is constructed by transforming the design $\Udes$ according to the transformation \eqref{eq:transPts}.
+Also suppose that conditions \eqref{eq:BigQYes} are satisfied.
+Then $\Xdes$ has the same discrepancy with respect to the target distribution, $F$, defined by the kernel $K$ as does the original design $\Udes$ with respect to the uniform distribution and defined by the kernel $K_\unif$.
+That is,
+\begin{equation}
+     D(\Xdes,F,K) = D(\Udes,F_{\unif},K_\unif)
+\end{equation}
+As a consequence, under conditions \eqref{eq:BigQYes}, question \eqref{BigQ} has a positive answer.
+\end{theorem}
+
+Condition \eqref{eq:BigQYesb} may be easy to satisfy.
+For example, it is automatically satisfied by the inverse cumulative distribution transform \eqref{eq:inverse}.
+Condition \eqref{eq:BigQYesa} is simply a matter of definition of the kernel, $K$, but it is definition with consequences.
+From the perspective of Section \ref{sec:HilbertMeasures}, changing the kernel means changing the definition of the distance between two Dirac measures.
+From the perspective of Section \ref{sec:DetermBound}, changing the kernel means changing the definition of the Hilbert space of integrands, $f$, in \eqref{eq:integration}.
+From the perspective of Section \ref{sec:RandomBound}, changing the kernel means changing the definition of the covariance kernel for the integrands, $f$, in \eqref{eq:integration}.
+
+To illustrate this point, consider a cousin of the kernel in \eqref{eq:OrigKernel}, which places the reference point at $\boldsymbol{0.5} = (0.5, \ldots, 0.5)$, the center of the unit cube $(0,1)^d$:
+\begin{align}
+\label{eq:L2kernel}
+    K_{\unif}(\vu,\vv) &= \prod_{j=1}^d\left[1+\frac{1}{2}|u_j-0.5|+\frac{1}{2}|v_j-0.5|-\frac{1}{2}|u_j-v_j|\right] \\
+    \nonumber
+    & = K(\vu - \boldsymbol{0.5}, \vv - \boldsymbol{0.5}) \qquad \text{for $K$ defined in \eqref{eq:OrigKernel}}. 
+\end{align}
+This kernel defines the centered $L^2$-discrepancy \cite{Hic97a}.
+Consider the standard multivariate normal distribution, $F_\normal$, and choose the inverse normal distribution,
+\begin{equation*}
+    \vPsi(\vu) = (\Phi^{-1}(u_1), \ldots, \Phi^{-1}(u_d)),
+\end{equation*}
+where $\Phi$ denotes the standard normal distribution function.  Then condition \eqref{eq:BigQYesb} is automatically satisfied, and condition \eqref{eq:BigQYesa} is  satisfied by defining
+\begin{align}
+\nonumber
+     K(\vt,\vx) &= K_{\unif}(\vPsi^{-1}(\vt),\vPsi^{-1}(\vx)) \\
+     \nonumber
+      &= \prod_{j=1}^d\left[1+\frac{1}{2}|\Phi^{-1}(t_j)-0.5|+\frac{1}{2}|\Phi^{-1}(x_j)-0.5| \right . \\
+      & \qquad \qquad \left . -\frac{1}{2}|\Phi^{-1}(t_j)-\Phi^{-1}(x_j)|\right].
+\end{align}
+In one dimension, the distance between two Dirac measures defined using the kernel $K_\unif$ above is $\norm{\delta_{x} - \delta_{t}} = \sqrt{x-t}$, whereas the distance defined using the kernel $K$ above is $\norm{\delta_{x} - \delta_{t}} = \sqrt{\Phi^{-1}(x)-\Phi^{-1}(t)}$.
+Under kernel $K$, the distance between two Dirac measures can never be greater than one.
+Such an assumption may be unpalatable.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Do Transformed Low Discrepancy Points Have Low Discrepancy More Generally}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+From the discussion above, it appears that condition \eqref{eq:BigQYesa} can be too restrictive.
+We would like to compare the discrepancies of designs under kernels that do not satisfy that restriction.
+In particular, we consider the centered $L^2$-discrepancy for designs on $(0,1)^d$ defined by the kernel in \eqref{eq:L2kernel}:
+\begin{align*}
+\MoveEqLeft{D^2(\Udes, F_\unif, K_\unif)} \\
+& = \left(\frac{13}{12}\right)^d - \frac{2}{N}\sum_{i=1}^N \prod_{j=1}^d \left(1+\frac{1}{2}|u_{ij}-1/2|-\frac12|u_{ij}-1/2|^2\right)\\
+& \qquad + \frac{1}{N^2}\sum_{i,k=1}^N\prod_{j=1}^d\left[1+\frac{1}{2}|u_{ij}-1/2|+\frac{1}{2}|u_{kj}-1/2|-\frac{1}{2}|u_{ij}-u_{kj}|\right],    
+\end{align*}
+We also consider the discrepancy for designs defined with respect to the standard normal distribution defined by the kernel \eqref{eq:OrigKernel}.
+We choose this kernel because it has a more realistic interpretation in terms of the distance between two Dirac measures.
+This discrepancy is
+\begin{align}\label{eq:DisNormald>1}
+\nonumber
+\MoveEqLeft{D^2(\Xdes, F_\normal, K) = \left(1+\sqrt{\frac{2}{\pi}}\right)^d}\\
+\nonumber
+  & - \frac{2}{N}\sum\limits_{\vx\in \Xdes} \prod\limits_{j=1}^d\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_j|-x_j[\Phi(x_j)-1/2]-\phi(x_j)\right]\\
+  &+\frac{1}{N^2}\sum_{\vx,\vt\in \Xdes}\prod_{j=1}^d \left[1+\frac{1}{2}|x_j|+\frac{1}{2}|t_j|-\frac{1}{2}|x_j-t_j|\right]. 
+\end{align}
+When $d=1$, the discrepancy \eqref{eq:DisNormald>1} can be further simplified to
+\begin{align}\label{eq:DisNormald=1}\nonumber
+D^2(\Xdes, \Phi_1, K)=& -\frac{2}{N}\sum_{i=1}^N \left[\max(x_i,0)-x_i\Phi_1(x_i)-\phi(x_i)\right]\\
++&\frac{1}{N}\sum_{i=1}^N|x_i|-\frac{1}{2N^2}\sum_{i,j=1}^N|x_i-x_j|. 
+\end{align}
+In both \eqref{eq:DisNormald=1} and \eqref{eq:DisNormald>1}, $\phi(\cdot)$ is the pdf of $N(0,1)$. 
+The derivations are in the Appendix.
+
+The discrepancy for the uniform distribution on unit cube $(0,1)^d$ we adapt in this work is the centered $L_2$-discrepancy \cite{Hic97a} defined as:
+\begin{align*}
+[D_2(\Udes, F_\unif, K_2)]^2 =& \left(\frac{13}{12}\right)^d - \frac{2}{N}\sum\limits_{\vu\in \Udes}\prod_{j=1}^d \left(1+\frac{1}{2}|u_j-1/2|-1/2|u_j-1/2|^2\right)\\
+\hspace{5ex}&+ \frac{1}{N^2}\sum\limits_{\vu,\vu'\in \Udes}\prod_{j=1}^d\left[1+\frac{1}{2}|u_j-1/2|+\frac{1}{2}|u_j'-1/2|-\frac{1}{2}|u_j-u_j'|\right],    
 \end{align*}
@@
 \begin{equation}\label{eqn:oril2kernel}
-K_2(\vx,\vt) = \prod\limits_{j=1}^s\left[1+\frac{1}{2}|x_j-1/2|+\frac{1}{2}|t_j-1/2|-\frac{1}{2}|x_j-t_j|\right].
+K_2(\vx,\vt) = \prod\limits_{j=1}^d\left[1+\frac{1}{2}|x_j-1/2|+\frac{1}{2}|t_j-1/2|-\frac{1}{2}|x_j-t_j|\right],
 \end{equation}
-Shifting experimental region to $[-1/2,1/2]^d$, the reproducing kernel in \eqref{eqn:oril2kernel} becomes
-\begin{align}\label{eqn:l2kernel}
-K(\vx,\vt) & = \prod\limits_{j=1}^d\left[1+\frac{1}{2}|x_j|+\frac{1}{2}|t_j|-\frac{1}{2}|x_j-t_j|\right].  
-\end{align}
-Next we extend the domain of this kernel function to $\mathbb{R}^d$, and show that this kernel function is a reproducing kernel with a proper defined inner product.
+which is the same as \eqref{eq:OrigKernel}, except it is anchored to the center $(1/2,\cdots,1/2)$ of the cube but not the origin.
+The centered $L_2$-discrepancy is invariant under reflections of $\Udes$ about any plane $x_j = 1/2$.
 
-We define an inner product as follows. 
+With the kernel in \eqref{eq:OrigKernel}, now we define a discrepancy for multivariate standard normal distribution on $\mathbb{R}^d$ that also refers to the center of the experimental region, $(0,\cdots,0)$.
+Firstly, we show that this kernel function is a reproducing kernel with a properly defined inner product as follows.
 \begin{equation}\label{eq:inner}
@@
 The vector $(\vx_u,{\bf 0})$ is a $d$-dimensional vector with the dimension indexed by $u$ denoted as $\vx_u$ and the rest are set to be ${\bf 0}$. 
-In particular, for $u = \{1,...,d\}$, we have $(\vx_u,{\bf 0}) = \vx$; for $u=\emptyset$, we have $(\vx_u,{\bf 0}) = {\bf 0}$.
+In particular, for $u = \{1,...,d\}$, we have $(\vx_u,{\bf 0}) = \vx$; for $u=\emptyset$, we have $(\vx_u,{\bf 0}) = {\bf 0}$. In particular, when $d=1$,
+\begin{equation*}
+\langle f,g \rangle = f(0)g(0)+\int_{\mathbb{R}}f'(x)g'(x)\dif x.
+\end{equation*}
 
-With the inner product \eqref{eq:inner}, it is easy to see that above kernel function in \eqref{eqn:l2kernel} is symmetric and positive semi-definite on $\Omega = \mathbb{R}^d$, i.e., the domain of the $d$-dim multivariate normal distribution.
+With the inner product \eqref{eq:inner}, it is easy to see that above kernel function in \eqref{eq:OrigKernel} is symmetric and positive semi-definite on $\Omega = \mathbb{R}^d$, i.e., the domain of the $d$-dim multivariate normal distribution.
 Note that $K({\bf 0},\vt) = 1$ and
@@
 \end{align*}
-With the reproducing kernel \eqref{eqn:l2kernel}, we can analytically derive the  squared discrepancy for the standard normal distribution. 
-For univariate standard normal distribution $N(0,1)$ 
+With the reproducing kernel \eqref{eq:OrigKernel}, we can analytically derive the discrepancy for the standard normal distribution.
+
+Let $\Xdes = \{\vx_i\}_{i=1}^N$ be a design on $\Omega = \mathbb{R}^d$. 
+The squared discrepancy of the design $\Xdes$ with respect to the $d$-dimensional standard multivariate normal probability distribution $N({\bf 0}, {\bf I}_d)$ with cdf $\Phi$ is
+\begin{eqnarray}\label{eqn:discrepancy}\nonumber
+D^2(\Xdes, \Phi, K) &=& \int_{\Omega\times\Omega} K(\vx,\vt)\dif \Phi(\vx)\dif \Phi(\vt)\\
+&-&\frac{2}{N}\sum_{i=1}^N \int_{\Omega}K(\vx,\vx_i)\dif \Phi(\vx)+\frac{1}{N^2}\sum_{i,k=1}^N K(\vx_i,\vx_k).
+\end{eqnarray}
+The cdf $\Phi(\vx)=\prod_{j=1}^d \Phi_1(x_j)$, where $\Phi_1(\cdot)$ is the cdf of $N(0,1)$. 
+With simple calculation, the squared discrepancy \eqref{eqn:discrepancy} can be  computed explicitly as
+\begin{align}\label{eq:DisNormald>1}\nonumber
+&D^2(\Xdes, \Phi, K)\\\nonumber
+  &= \left(1+\sqrt{\frac{2}{\pi}}\right)^d - \frac{2}{N}\sum\limits_{\vx\in \Xdes} \prod\limits_{j=1}^d\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_j|-x_j[\Phi_1(x_j)-1/2]-\phi(x_j)\right]\\
+  &+\frac{1}{N^2}\sum_{\vx,\vt\in \Xdes}\prod_{j=1}^d \left[1+\frac{1}{2}|x_j|+\frac{1}{2}|t_j|-\frac{1}{2}|x_j-t_j|\right]. 
+\end{align}
+When $d=1$, the discrepancy \eqref{eq:DisNormald>1} can be further simplified to
 \begin{align}\label{eq:DisNormald=1}\nonumber
-[D(P)]^2=& -\frac{2}{N}\sum_{n=1}^N \left[\max(x_n,0)-x_n\Phi(x_n)-\phi(x_n)\right]\\
-+&\frac{1}{N}\sum_{n=1}^N|x_n|-\frac{1}{2N^2}\sum_{n,m=1}^N|x_n-x_m|. 
+D^2(\Xdes, \Phi_1, K)=& -\frac{2}{N}\sum_{i=1}^N \left[\max(x_i,0)-x_i\Phi_1(x_i)-\phi(x_i)\right]\\
++&\frac{1}{N}\sum_{i=1}^N|x_i|-\frac{1}{2N^2}\sum_{i,j=1}^N|x_i-x_j|. 
 \end{align}
-For multivariate standard normal distribution $N({\bf 0}, {\bf I}_d)$, 
-\begin{align}\label{eq:DisNormald>1}\nonumber
-&[D(P)]^2\\\nonumber
-  &= \left(1+\sqrt{\frac{2}{\pi}}\right)^d - \frac{2}{N}\sum\limits_{\vx\in P} \prod\limits_{j=1}^d\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_j|-x_j[\Phi(x_j)-1/2]-\phi(x_j)\right]\\
-  &+\frac{1}{N^2}\sum_{\vx,\vt\in P}\prod_{j=1}^d \left[1+\frac{1}{2}|x_j|+\frac{1}{2}|t_j|-\frac{1}{2}|x_j-t_j|\right]. 
-\end{align}
-In both \eqref{eq:DisNormald=1} and \eqref{eq:DisNormald>1}, $\phi(\cdot)$ and $\Phi(\cdot)$ are the pdf and cdf for the univeriate standard normal distribution $N(0,1)$, respectively. 
-The derivations are in Appendix.
+In both \eqref{eq:DisNormald=1} and \eqref{eq:DisNormald>1}, $\phi(\cdot)$ is the pdf of $N(0,1)$. 
+The derivations are in the Appendix.
 
 \section{Inconsistency in Discrepancy}\label{sec:inconsistency}
+Using the inverse transformation method, we can generate the standard multivariate normal distribution $N({\bf 0},{\bf I}_d)$ by applying $x_{i,j}=\Phi^{-1}_j(u_{i,j})$ for $j=1,\ldots,d$ and $i=1,\ldots, N$.
+However, the inverse transformation would lead to inconsistency between the discrepancy before and after the transformation. 
+Although $\Udes = \{\vu_i\}_{i=1}^N$ is the low-discrepancy points for the uniform distribution in $[0,1]^d$, the following examples shows that it is not necessarily so that $\Xdes=\{\vx_i\}_{i=1}^N$ is also low-discrepancy.
+In other words, for two uniform designs, $\Udes_1$ and $\Udes_2$, the fact that $D(\Udes_1,F_\unif, K)\leq D(\Udes_2,F_\unif, K)$ does not imply that the inverse transformed normal design $\Xdes_1$ and $\Xdes_2$ also have $D(\Xdes_1,\Phi, K)\leq D(\Xdes_2,\Phi, K)$.
+Note that the two discrepancies $D(\Udes, F_\unif, K)$ and $D(\Xdes, \Phi, K)$ are based on the same kernel, hence the inconsistency is only due to the inverse transformation.
 
-Let $\mathcal{H}$ be a reproducing kernel Hilbert space associated with the reproducing kernel function $K$: $\mathbb{R}\times \mathbb{R}\rightarrow\mathbb{R}$. 
-One fundamental problem in mathematics and statistics is to compute the mean value $\mu$ of any given function $g\in \mathcal{H}$. 
-\[
-\mu=\mathbb{E}(g(X))=\int_{\mathbb{R}}g(x)\phi(x)dx=\int_{\mathbb{R}} g(x)d\Phi(x), 
-\]
-where $\phi(\cdot)$ and $\Phi(\cdot)$ are the pdf and cdf functions of the standard normal distribution $N(0,1)$. 
-When
+Let $d=5$ and $n=50$. 
+We generate $B=20$ samples from uniform distribution in $[0,1]^5$ and then use the inverse distribution transformation to obtain samples following $N({\bf 0}, {\bf I}_5)$. 
+The discrepancy for uniform distribution is the $L_2$-discrepancy $D_2(\Udes,F_\unif,K_2)$ and for the standard normal distribution is \eqref{eq:DisNormald>1}. 
+Figure \ref{fig:UniVsNormDisc} plots the discrepancy for normal distribution against the $L_2$-discrepancy for each of the $B=20$ samples. 
+If the inverse transformation makes the design consistent in terms of the discrepancy, the points in \ref{fig:UniVsNormDisc} should be approximately aligned on a straight line. 
+Clearly, some samples with low uniform discrepancy turn out to have large normal discrepancy after inverse transformation.
+Thus, inverse transformation cannot ensure the consistency of the design in terms of the discrepancy.
 
-To illustrate the inconsistency in discrepancy before and after inverse distribution transformation, we consider a toy example with $s=5$ and $n=50$.
-20 randomly generated uniform random samples are adapted to generate samples from standard multivariate normal distribution using inverse distribution transformation.
-The following figure \ref{fig:UniVsNormDisc} shows that a sample with low uniform discrepancy may not guarantee a sample with low normal discrepancy after inverse distribution transformation.
-
-\begin{figure}[H]
-\label{fig:UniVsNormDisc}
-\centering
-{\includegraphics[width=8cm]{d5n50UniVsNormDisc2.pdf}}
-\caption{Uniform Discrepancy Vs. Normal Discrepancy after Inverse Transformation}
+\begin{figure}[ht]
+\begin{center}
+\includegraphics[width=8cm]{d5n50.eps}
+\caption{Uniform Discrepancy Vs. Normal Discrepancy. \label{fig:UniVsNormDisc}}
+\end{center}
 \end{figure}
 
-We further investigate the correlation between uniform discrepancy and the normal discrepancy after the inverse distribution transformation.
-For different variable dimension from $s=1$ to $s=10$, the sample correlation coefficients between the uniform discrepancies of 1000 uniform random samples of size 50 and the normal discrepancies of the corresponding normal random samples generated using inverse distribution transformation are calculated.
-From figure \ref{fig:UniVsNormDisc}, it can be seen that the phenomenon of inconsistency in discrepancy becomes more pronounced as the sample becomes more sparse.
+We further investigate the relationship between the uniform discrepancy of a design and the normal discrepancy of the same design after inverse transformation.
+Varying the dimension $d$ from 1 to 10, we calculate the sample correlation coefficients between the two discrepancies of the $B=500$ uniform designs of size $N=50$ and corresponding normal designs after inverse transformation, and plot the correlations against $d$ in \ref{fig:UniVsNormDisc}.
+It can be seen that the phenomenon of inconsistency in discrepancies becomes more pronounced as $d$ increases.
 
-\begin{figure}[htbp]
+\begin{figure}[ht]
 \label{fig:DimVsDisc}
 \centering
-{\includegraphics[width=8cm]{dimVsdisc.pdf}}
+{\includegraphics[width=8cm]{dimVsdisc.eps}}
 \caption{Correlation between Uniform Discrepancy and Normal Discrepancy with Different Variable Dimensions}
@@
 
-\section{Improvement by the Coordinate-Exchange Algorithm}
-The common practice to generate $d-$dim standard normal random numbers is inverse distribution transformation.
-However, as discussed in section \ref{sec:inconsistency}, a random sequence with low uniform discrepancy doesn't guarantee a low normal discrepancy sequence after inverse distribution transformation.
-We propose an efficient algorithm that assures low normal discrepancy of the generated $d$-dim standard normal random numbers.
+The root cause of this inconsistency can be revealed as follows. 
+For simplicity, let $d=1$. 
+Taking the inverse transformation $x_{i}=\Phi^{-1}_1(u_{i})$ in the normal discrepancy \eqref{eqn:discrepancy}, 
+\begin{align*}
+&D^2(\Xdes, \Phi_1, K) = \int_{[0,1]^2} K(\Phi^{-1}_1(u),\Phi^{-1}_1(u'))\dif \Phi(\Phi^{-1}_1(u))\dif \Phi(\Phi^{-1}_1(u'))\\
+&-\frac{2}{N}\sum_{i=1}^N \int_0^1 K(\Phi^{-1}_1(u),\Phi^{-1}_1(u_i))\dif \Phi(\Phi^{-1}_1(u))+\frac{1}{N^2}\sum_{i,k=1}^N K(\Phi^{-1}_1(u_i), \Phi^{-1}_1(u_j))\\
+&=\int_{[0,1]^2} K(\Phi^{-1}_1(u),\Phi^{-1}_1(u'))\dif u\dif u'\\
+&-\frac{2}{N}\sum_{i=1}^N \int_0^1 K(\Phi^{-1}_1(u),\Phi^{-1}_1(u_i))\dif u+\frac{1}{N^2}\sum_{i,k=1}^N K(\Phi^{-1}_1(u_i), \Phi^{-1}_1(u_j))\\
+&=D^2(\Udes,F_\unif,\tilde{K}),
+\end{align*}
+where $\tilde{K}(\cdot,\cdot)=K(\Phi^{-1}_1(\cdot), \Phi^{-1}_1(\cdot)): [0, 1]\rightarrow \mathbb{R}_{+}$. 
+Although $\tilde{K}(\cdot,\cdot)$ is still a valid kernel function for the uniform distribution, the resulting discrepancy $D(\Udes,F_\unif, \tilde{K})$ is no longer the same as $D_2(\Udes, F_\unif, K_2)$, and their difference only increases as the dimension $d$ becomes higher due to the effect of the product in $D_2(\Udes, F_\unif, K_2)$.
+The difference in kernel $K_2$ and $\tilde{K}$ also leads to different RKHS of integrand functions.
 
-In this section, to better illustrate the coordinate exchange method, we represent a $N$ points $d$-dim design $\{\vx_i\}_{i=1}^N$ with a design matrix $$\mX = \left(\begin{array}{c}\vx_1^T\\ \vdots\\\vx_N^T\end{array}\right).$$ We propose using the coordinate exchange method to optimize the normal discrepancy of a current design.
-The coordinate exchange method was first proposed by Meyer and Nachtsheim \cite{meyer1995coordinate}, and it rapidly becomes a widely used algorithm to construct exact optimal designs in experimental design community.
-The coordinate exchange method searches for the ``worst" coordinate $x_{ij}$ of the current design, and replace it with a better coordinate that improves the current design criterion.
-With only one coordinate $x_{ij}$  changeable, optimizing the design criterion becomes essentially a univariate optimization problem that can be solve easily and efficiently.
-In general, with a current design $\mX^{(0)}$ the coordinate exchange method functions as follows:
+\section{Improvement by the Coordinate-Exchange Method}\label{sec:CoordEx}
+
+In this section, we propose an efficient algorithm that improves the design's quality in terms of the discrepancy for the target standard normal distribution. 
+We start with a low-discrepancy uniform design, such as a Sobol sequence, and apply the inverse transformation to the design so that the transformed design approximates the target distribution, which is the standard normal distribution in this work.
+Following the optimal design approach, we consider the discrepancy of the normal design as the design criterion and apply a certain optimization algorithm to further improve the design, until the discrepancy reaches the minimum.
+
+The optimization algorithm we choose is the coordinate-exchange algorithm, which was firstly introduced in \cite{meyer1995coordinate}, and then applied widely to construct various kinds of optimal design \cite{sambo2014coordinate,overstall2017bayesian,kang2018stochastic}.
+The coordinate-exchange algorithm is an iterative optimization method.
+It finds the ``worst" coordinate $x_{ij}$ of the current design, and replace it with a better coordinate that improves the current design criterion. 
+The most appealing advantage of the coordinate-exchange algorithm is that it renders the $N\times d$ dimension of the decision variables of the original optimal design problem to just one dimension as it changes one coordinate at a time.
+This greatly reduces the difficulty of the optimization problem.
+
+We format the $N$ points of $d$-dim design points $\{\vx_i\}_{i=1}^N$ into a design matrix  $\mX^\top =[\vx_1,\ldots, \vx_N]$, and $x_{ij}$ refers to the $(i,j)$-th element of $\mX$, and it also refers to the $j$-th dimension of the $i$-th sample point.
+To find the ``worst'' coordinate, we use row and column deletion function, as in \cite{kang2018stochastic}.
+Define the row deletion function of the $i$-th row as follows. 
+\begin{eqnarray}\label{eq:rowdeletion}
+&& d_r(i) = D^2(\Xdes)-D^2(\Xdes\backslash \vx_i)\nonumber\\
+&=& -2\prod\limits_{s=1}^dc(x_{is}) + \frac{1}{N-1}\left(2\sum_{j=1}^N\prod_{s=1}^d h(x_{is},x_{js})-\prod_{s=1}^d h(x_{is},x_{is})\right). 
+\end{eqnarray}
+We use $D(\Xdes)$ as a simplified notation for the discrepancy as the target design is always standard normal distribution and the kernel function is \eqref{eq:OrigKernel}. 
+The notation $\Xdes\backslash \vx_i$ means that the design $\Xdes$ without the $i$-th point $\vx_i$. 
+Here $c(x)$ and $h(x,y)$ are 
+\begin{align*}
+c(x) &= 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x|-x[\Phi_1(x)-1/2]-\phi(x),\\
+h(x,y) &= 1+\frac{1}{2}|x|+\frac{1}{2}|y|-\frac{1}{2}|x-y|.
+\end{align*}
+The definition of $d_r(i)$ represents the change in $D^2(\Xdes)$ when $\vx_i$ is removed from the design. 
+If $d_r(i)\geq 0$, it means that removing $\vx_i$ would lead to a smaller discrepancy. 
+Thus, it is reasonable to assume $\vx_i$ has the potential to be updated and leads to a smaller discrepancy. 
+Among all the design points that $d_r(i)\geq 0$, we should pick the $i_0$ that has largest $d_r(i)$, because removing $\vx_i$ leads to the biggest improvement, so we consider this row has the biggest potential.
+On the other hand, if $d_r(i)< 0$, it means that removing $\vx_i$ would make the discrepancy bigger, and thus make the design worse, so we should keep $\vx_i$ in the design. 
+However, if $d_r(\vx_i)\leq 0$ for $i=1,\ldots, N$, and we must pick a row index, then we should pick the $i_0$ that has the smallest $\abs{d_r(\vx_i)}$ because removing $\vx_{i_0}$ would make the design worse with the least degree compared to other indices.
+Combining both scenarios, we should pick the row index by 
+\[
+i^*=\argmax_{i=1,\ldots,N} d_r(i).
+\]
+Similarly, we define the column deletion function as follows. 
+\begin{eqnarray}\label{eq:coldeletion}
+d_c(j) &=& -\frac{2}{N}\sum_{i=1}^N(c(x_{ij})-1)\prod\limits_{\substack{s=1,\\ s\neq j}}^dc(x_{is})\nonumber\\ 
+&&+\frac{1}{N^2}\sum_{\substack{i=1,\\ r=1}}^N\left(h(x_{ij},x_{rj})-1\right)\prod_{\substack{s=1\\s\neq j}}^d h(x_{is},x_{rs}).
+\end{eqnarray}
+We pick the column index by 
+\[
+j^*=\argmax_{j=1,\ldots,d} d_c(j).
+\]
+Once the $(i^*, j^*)$-th coordinate is identified to be changed, we compute the delta function $\Delta(x_{i^*j^*},x)$, which represents the decrease in $D^2(\Xdes)$, if $x_{i^*j^*}$ is replaced by $x \in \mathbb{R}$.
+The delta function can be computed as follows. 
+\begin{eqnarray}\label{eq:deltafunction}
+&&\Delta(x_{{i^*j^*}}, x)\nonumber\\
+&=& -\frac{2}{N}\left(c(x_{i^*j^*})-c(x)\right)\prod\limits_{\substack{j=1,\\j\neq j^*}}^dc(x_{i^*j})\nonumber\\
+&&+\frac{1}{N^2}\left(2\sum_{\substack{i=1,\\i\neq i^*}}^N(h(x_{i^*j^*},x_{ij^*})-h(x,x_{ij^*}))\prod_{\substack{j=1,\\j\neq j^*}}^dh(x_{i^*j},x_{ij})\right.\nonumber\\
+&&\left.+(|x_{i^*j^*}|-|x|)\prod_{\substack{j=1,\\j\neq j^*}}^d[1+|x_{i^*j}|]\right)
+\end{eqnarray} 
+We summarize the coordinate-exchange algorithm in Algorithm 1. 
 \begin{algorithm}[ht]
-\begin{algorithmic}[1]
+\begin{algorithmic}[1]\label{alg:coorex}
 \caption{Coordinate exchange method}
@@
 \If{$\Delta(x_{i^*j^*},x^*)>0$} 
-\State {replace $x_{i^*j^*}$ with $x^*$ and the denote the new design as $\mX^{(k+1)}$.}
+\State {replace $x_{i^*j^*}$ with $x^*$ and the define the new design as $\mX^{(k+1)}$.}
 \State {$k=k+1$.}
@@
 
-\begin{algorithm}[ht]
-\begin{algorithmic}[2]
-\caption{Generate a $d$-dim low normal discrepancy sequence}
-\State Start with a $d$-dim low uniform discrepancy design $\{\vu_i\}_{i=1}^N$, e.g., Sobol sequence.
-\State Perform inverse distribution transformation on $\{\vu_i\}_{i=1}^N$ to generate $d$-dim standard normal design $\{\vx_i\}_{i=1}^N$.
-\State Improve the design $\{\vx_i\}_{i=1}^N$ with coordinate exchange algorithm by minimizing its the normal discrepancy.
-\end{algorithmic}
-\end{algorithm}
+It's worth pointing out that although the three functions, $d_r, d_c$ and $\Delta$ need to computed in each iteration for multiple times, most evaluations only involve $c(x_{ij})$ and $h(x_{ij},x_{rs})$, $i,r = 1,...,N, j,s=1,...,d$, which only need to be computed once before the design is updated.
+The maximization of $\Delta$ function is a one-dimension unconstrained optimization and can be easily solved by any unconstrained nonlinear optimization methods.
 
@@
 
-\section{Conclusion}
+To demonstrate the performance of the $d$-dim standard normal design proposed in Section \ref{sec:CoordEx}, we compare three algorithms: (1) Randn: embedded normal random number generator `randn' from MATLAB;  (2) NG1: inverse transformed Sobol sequence; (3) NG2: improved NG1 with proposed Algorithm 1.
+We have tried different combinations of dimension and sample size, and let the sample size become larger as the dimension becomes higher. 
+Using each algorithm we generate 500 designs, and for each design, we compute the discrepancy \eqref{eq:DisNormald>1} and compare the distribution of discrepancies from different algorithms as shown in Figure \ref{fig:comparison}.
+We summarize the observations as follows. 
+\begin{enumerate}
+\item
+NG1 and NG2 both outperform Randn by a great margin.
+\item 
+When the sample is relatively dense, i.e., $N/d$ ratio is large, NG1 and NG2 have similar performance, but the proposed NG2 is slightly better, as it takes the extra step to improve the relative high discrepancy via Algorithm 1.
+\item
+As the sample becomes more sparse, i.e., $N/d$ ratio is smaller, the proposed NG2 becomes much superior to NG1.
+\end{enumerate}
+Therefore, the inverse transformation of low-discrepancy uniform designs, such as Sobol sequences is still preferable when the sample size is large relative to the dimension, and we recommend using the proposed remedy approach to further improve the inverse transformed Sobol sequences when the sample size is small or moderate.
+
+\begin{figure}[ht]\label{fig:comparison}
+\centering
+{\subfigure[$d=2,N=30$] {\includegraphics[width=5.5cm]{boxplot_d2n30.eps}}}
+\quad
+{\subfigure [$d=3, N=50$]
+{\includegraphics[width=5.5cm]{boxplot_d3n50.eps}}}
+\quad
+{\subfigure[$d=4, N=70$] {\includegraphics[width=5.5cm]{boxplot_d4n70.eps}}}
+\quad
+{\subfigure[$d=5, N=90$] {\includegraphics[width=5.5cm]{boxplot_d5n90.eps}}}
+\quad
+{\subfigure[$d=6, N=110$] {\includegraphics[width=5.5cm]{boxplot_d6n110.eps}}}
+\quad
+{\subfigure[$d=7, N=130$] {\includegraphics[width=5.5cm]{boxplot_d7n130.eps}}}
+\caption{Performance Comparison of Three Generators}\label{fig:generatorcomp}
+\end{figure}
+
+\section{Discussion}
+In this chapter, we summarize the three interpretations of the discrepancy. 
+It is a measure on how well the empirical distribution of a design approximates the target distribution or a tight upper bound of some quadrature of an integral approximation, or the root mean squared cubature error of an integral approximation when the integrand is a stochastic process.
+Then, we point out a flaw of the inverse transformation method, which is used to generate random samples (or designs) following any non-uniform distribution. 
+The flaw is that any low-discrepancy uniform designs do not necessarily lead to low-discrepancy for the inverse transformed designs. 
+To explain this issue, we choose the standard normal distribution as an example for non-uniform distributions. 
+We show that the low-discrepancy uniform design may not preserve the low-discrepancy after inverse distribution transformation into a standard normal distribution. 
+As a remedy approach, we propose a coordinate-exchange algorithm to further minimize the $L_2$-discrepancy of the design from the inverse transformation of the low-discrepancy uniform design.
+
+It's worth pointing out that the discrepancy defined in \eqref{eq:discDef} can be generalized to any $d$-dim distribution $\varrho$ with mean $\boldsymbol{\mu} = (\mu_1,\cdots,\mu_d)$.
+The centered reproducing kernel in \eqref{eq:OrigKernel} should be
+\begin{equation} \label{ExtKernel}
+     K(\vt,\vx)  = \prod\limits_{j=1}^d\left[1+ \frac 12 \left(|t_j-\mu_j|+ |x_j-\mu_j|- |x_j-t_j| \right)\right].
+\end{equation}
+Then the discrepancy $D(\Xdes,\Ftar,K)$ can be computed using \eqref{eq:discDef}, and the two integrals in \eqref{eq:discDef} may require numerical approximations for some target distribution. 
+If the analytic formula of $D(\Xdes,\Ftar,K)$ can be derived, the coordinate-exchange algorithms can be applied in a similar fashion to improve the inverse transformation method.
 
@@
 \begin{proof}
-We first derive $[D(p)]^2$ for $d=1$ case. 
+We first derive $D^2(\Xdes,\Phi_1,K)$ for $d=1$ case. 
 To compute the discrepancy, we first integrate the kernel once:
 \begin{align*}
-\MoveEqLeft{\int_{-\infty}^\infty K(x,t) \, \dif \Phi(x)}\\
+\MoveEqLeft{\int_{-\infty}^\infty K(x,t) \, \dif \Phi_1(x)}\\
 =&\int_{-\infty}^{\infty} \left(1+\frac{1}{2}|x|+\frac{1}{2}|t|-\frac{1}{2}|x-t|\right)\phi(x) \, \dif x\\
 =& 1+ \frac{1}{\sqrt{2\pi}} + \frac{1}{2}|t|-\frac{1}{2}\left[\int_{-\infty}^{t}(t-x)\phi(x) \, \dif x+\int_{t}^{\infty} (x-t)\phi(x) \, \dif x\right]\\
-=& 1+ \frac{1}{\sqrt{2\pi}} + \frac{1}{2}|t| - t [\Phi(t)-1/2] - \phi(t) .
+=& 1+ \frac{1}{\sqrt{2\pi}} + \frac{1}{2}|t| - t [\Phi_1(t)-1/2] - \phi(t) .
 \end{align*}
@@
 \begin{align*}
-\MoveEqLeft{\int_{-\infty}^\infty \int_{-\infty}^\infty K(x,t) \, \dif \Phi(x) \dif \Phi(t)}\\
-& =  \int_{-\infty}^{\infty} \left( 1+\frac{1}{\sqrt{2\pi}} + \frac{1}{2}|t| - t [\Phi(t)-1/2] + \phi(t)\right)\phi(t) \, \dif t\\
-&= 1+ \sqrt{\frac{2}{\pi}} + \int_{-\infty}^{\infty} \{ - t \Phi(t)\phi(t)  +  [\phi(t)]^2 \} \, \dif t\\
+\MoveEqLeft{\int_{-\infty}^\infty \int_{-\infty}^\infty K(x,t) \, \dif \Phi_1(x) \dif \Phi_1(t)}\\
+& =  \int_{-\infty}^{\infty} \left( 1+\frac{1}{\sqrt{2\pi}} + \frac{1}{2}|t| - t [\Phi_1(t)-1/2] + \phi(t)\right)\phi(t) \, \dif t\\
+&= 1+ \sqrt{\frac{2}{\pi}} + \int_{-\infty}^{\infty} \{ - t \Phi_1(t)\phi(t)  +  [\phi(t)]^2 \} \, \dif t\\
 &= 1+\sqrt{\frac{2}{\pi}}-\frac{1}{\sqrt{4\pi}}+\int_{-\infty}^{\infty}\frac{1}{2\pi}e^{-t^2}\dif t\\
@@
 \end{align*}
-Notice that $\int_{-\infty}^{\infty} t\Phi(t)\phi(t)\dif t = \frac{1}{\sqrt{4\pi}}$ and 
+Notice that $\int_{-\infty}^{\infty} t\Phi_1(t)\phi(t)\dif t = \frac{1}{\sqrt{4\pi}}$ and 
 \begin{eqnarray*}
-&&\int_{\Omega}K(x,x_n)\dif \Phi(x)\\
+&&\int_{\Omega}K(x,x_n)\dif \Phi_1(x)\\
 &=& \int_{-\infty}^{\infty} \left(1+\frac{1}{2}|x|+\frac{1}{2}|x_n|-\frac{1}{2}|x-x_n|\right)\phi(x)\dif x\\
@@
 &=& 1+\sqrt{\frac{1}{2\pi}}+\frac{1}{2}|x_n|-\frac{1}{2}\left[\int_{-\infty}^{x_n}(x_n-x)\phi(x)\dif x+\int_{x_n}^{\infty} (x-x_n)\phi(x)\dif x\right]\\
-&=& 1+\sqrt{\frac{1}{2\pi}}+\frac{1}{2}|x_n|-\frac{1}{2}\left[2x_n\Phi(x_n)-x_n-2\int_{-\infty}^{x_n}x\phi(x)\dif x\right]\\
-&=& 1+\sqrt{\frac{1}{2\pi}}+\max(x_n,0)-x_n\Phi(x_n)-\frac{ e^{-x_n^2/2}}{\sqrt{2\pi}}. 
+&=& 1+\sqrt{\frac{1}{2\pi}}+\frac{1}{2}|x_n|-\frac{1}{2}\left[2x_n\Phi_1(x_n)-x_n-2\int_{-\infty}^{x_n}x\phi(x)\dif x\right]\\
+&=& 1+\sqrt{\frac{1}{2\pi}}+\max(x_n,0)-x_n\Phi_1(x_n)-\frac{ e^{-x_n^2/2}}{\sqrt{2\pi}}. 
 \end{eqnarray*}
@@
 \begin{eqnarray*}
-&& [D(P)]^2\\
-&= &1+\sqrt{\frac{2}{\pi}}-\frac{2}{N}\sum_{n=1}^N \left[1+\sqrt{\frac{1}{2\pi}}+\max(x_n,0)-x_n\Phi(x_n)-\frac{ e^{-x_n^2/2}}{\sqrt{2\pi}}\right]\\
+&& D^2(\Xdes,\Phi_1,K)=1+\sqrt{\frac{2}{\pi}}-\frac{2}{N}\sum_{n=1}^N \left[1+\sqrt{\frac{1}{2\pi}}+\max(x_n,0)-x_n\Phi_1(x_n)-\frac{ e^{-x_n^2/2}}{\sqrt{2\pi}}\right]\\
 &&+\frac{1}{N^2}\sum_{n,m=1}^N \left[1+\frac{1}{2}|x_n|+\frac{1}{2}|x_m|-\frac{1}{2}|x_n-x_m|\right]\\
-&= &-\frac{2}{N}\sum_{n=1}^N \left[\max(x_n,0)-x_n\Phi(x_n)-\frac{ e^{-x_n^2/2}}{\sqrt{2\pi}}\right]+\frac{1}{N^2}\sum_{n,m=1}^N \left[\frac{1}{2}|x_n|+\frac{1}{2}|x_m|-\frac{1}{2}|x_n-x_m|\right]\\
-&=& -\frac{2}{N}\sum_{n=1}^N \left[\max(x_n,0)-x_n\Phi(x_n)-\phi(x_n)\right]+\frac{1}{N}\sum_{n=1}^N|x_n|-\frac{1}{2N^2}\sum_{n,m=1}^N|x_n-x_m|.\\
+&= &-\frac{2}{N}\sum_{n=1}^N \left[\max(x_n,0)-x_n\Phi_1(x_n)-\frac{ e^{-x_n^2/2}}{\sqrt{2\pi}}\right]+\frac{1}{N^2}\sum_{n,m=1}^N \left[\frac{1}{2}|x_n|+\frac{1}{2}|x_m|-\frac{1}{2}|x_n-x_m|\right]\\
+&=& -\frac{2}{N}\sum_{n=1}^N \left[\max(x_n,0)-x_n\Phi_1(x_n)-\phi(x_n)\right]+\frac{1}{N}\sum_{n=1}^N|x_n|-\frac{1}{2N^2}\sum_{n,m=1}^N|x_n-x_m|.\\
 \end{eqnarray*}
 For the distribution $N({\bf 0}, {\bf I}_d)$, the joint pdf is $$\prod\limits_{j=1}^d\phi(x_j) = \prod\limits_{j=1}^d \frac{1}{\sqrt{2\pi}}e^{-x_j^2/2}.$$
-Here the cdf function $\Phi$ used interchangeably for $N({\bf 0}, {\bf I}_d)$ and $N(0, 1)$, depending if the variable is a vector or scalar. Thus, 
+Here the cdf function $\Phi(\vx)=\prod_{j=1}^d \Phi_1(x_j)$. Thus, 
 \begin{align*}
 \int_{\reals^d\times \reals^d} K(\vx,\vt)&\dif\Phi(\vx)\dif\Phi(\vt) = \left(1+\sqrt{\frac{2}{\pi}}\right)^d, \\
-\int_{\reals^d}K(\vx,\vx_n)\dif\Phi(\vx) = \prod\limits_{j=1}^s&\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_j|-x_j[\Phi(x_j)-1/2]-\phi(x_j)\right].
+\int_{\reals^d}K(\vx,\vx_n)\dif\Phi(\vx) = \prod\limits_{j=1}^d&\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_j|-x_j[\Phi(x_j)-1/2]-\phi(x_j)\right].
 \end{align*}
@@
 \begin{eqnarray*}
-&&[D(P)]^2\\
-&=& \left(1+\sqrt{\frac{2}{\pi}}\right)^d - \frac{2}{N}\sum\limits_{\vx\in P} \prod\limits_{j=1}^d\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_j|-x_j[\Phi(x_j)-1/2]-\phi(x_j)\right]\\
+&&D^2(\Xdes, \Phi, K)\\
+&=& \left(1+\sqrt{\frac{2}{\pi}}\right)^d - \frac{2}{N}\sum\limits_{\vx\in P} \prod\limits_{j=1}^d\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_j|-x_j[\Phi_1(x_j)-1/2]-\phi(x_j)\right]\\
 &&+\frac{1}{N^2}\sum_{\vx,\vt\in P}\prod_{j=1}^d \left[1+\frac{1}{2}|x_j|+\frac{1}{2}|t_j|-\frac{1}{2}|x_j-t_j|\right]. 
@@
 %\bibliography{FJH23,FJHown23}
-\bibliography{Ref.bib}
+\bibliography{Ref.bib,FJH23,FJHown23}
 

### 2019-05-19 InvPts_verB.tex
latest updates

--- 2019-05-18 Draft_Inv.tex
@@
 \label{eq:L2kernel}
-    K_{\unif}(\vu,\vv) &= \prod_{j=1}^d\left[1+\frac{1}{2}|u_j-0.5|+\frac{1}{2}|v_j-0.5|-\frac{1}{2}|u_j-v_j|\right] \\
+    K_{\unif}(\vu,\vv) &= \prod_{j=1}^d\left[1+\frac{1}{2}\left(\left|u_j-1/2\right|+ \left|v_j- 1/2 \right|-\left |u_j-v_j \right| \right) \right] \\
     \nonumber
@@
 Consider the standard multivariate normal distribution, $F_\normal$, and choose the inverse normal distribution,
-\begin{equation*}
+\begin{equation} \label{eq:invNormTrans}
     \vPsi(\vu) = (\Phi^{-1}(u_1), \ldots, \Phi^{-1}(u_d)),
-\end{equation*}
+\end{equation}
 where $\Phi$ denotes the standard normal distribution function.  Then condition \eqref{eq:BigQYesb} is automatically satisfied, and condition \eqref{eq:BigQYesa} is  satisfied by defining
@@
      \nonumber
-      &= \prod_{j=1}^d\left[1+\frac{1}{2}|\Phi^{-1}(t_j)-0.5|+\frac{1}{2}|\Phi^{-1}(x_j)-0.5| \right . \\
-      & \qquad \qquad \left . -\frac{1}{2}|\Phi^{-1}(t_j)-\Phi^{-1}(x_j)|\right].
+      &= \prod_{j=1}^d\left[1+\frac{1}{2}\left(\left|\Phi^{-1}(t_j)-1/2\right|+ \left|\Phi^{-1}(x_j)- 1/2 \right| \right . \right . \\
+      & \qquad \qquad \left.  \left . -\left|\Phi^{-1}(t_j)-\Phi^{-1}(x_j)\right|\right)\right].
 \end{align}
@@
 
-From the discussion above, it appears that condition \eqref{eq:BigQYesa} can be too restrictive.
+From the discussion above indicates that condition \eqref{eq:BigQYesa} can be too restrictive.
 We would like to compare the discrepancies of designs under kernels that do not satisfy that restriction.
-In particular, we consider the centered $L^2$-discrepancy for designs on $(0,1)^d$ defined by the kernel in \eqref{eq:L2kernel}:
+In particular, we consider the centered $L^2$-discrepancy for uniform designs on $(0,1)^d$ defined by the kernel in \eqref{eq:L2kernel}:
 \begin{align*}
 \MoveEqLeft{D^2(\Udes, F_\unif, K_\unif)} \\
-& = \left(\frac{13}{12}\right)^d - \frac{2}{N}\sum_{i=1}^N \prod_{j=1}^d \left(1+\frac{1}{2}|u_{ij}-1/2|-\frac12|u_{ij}-1/2|^2\right)\\
-& \qquad + \frac{1}{N^2}\sum_{i,k=1}^N\prod_{j=1}^d\left[1+\frac{1}{2}|u_{ij}-1/2|+\frac{1}{2}|u_{kj}-1/2|-\frac{1}{2}|u_{ij}-u_{kj}|\right],    
+& = \left(\frac{13}{12}\right)^d - \frac{2}{N}\sum_{i=1}^N \prod_{j=1}^d \left[1+\frac{1}{2}\left(|u_{ij}-1/2|-|u_{ij}-1/2|^2\right) \right]\\
+& \qquad + \frac{1}{N^2}\sum_{i,k=1}^N\prod_{j=1}^d\left[1+\frac{1}{2}\left(|u_{ij}-1/2|+|u_{kj}-1/2|-|u_{ij}-u_{kj}| \right) \right],  
 \end{align*}
-We also consider the discrepancy for designs defined with respect to the standard normal distribution defined by the kernel \eqref{eq:OrigKernel}.
-We choose this kernel because it has a more realistic interpretation in terms of the distance between two Dirac measures.
-This discrepancy is
+where again, $F_\unif$ denotes the uniform distribution on $(0,1)^d$, and $\Udes$ denotes a design on $(0,1)^d$
+
+Changing perspectives slightly, if $F_\unif'$ denotes the uniform distribution on the cube of volume one centered at the origin, $(-\boldsymbol{0.5},\boldsymbol{0.5})^d$, and the design $\Udes'$ is constructed by  subtracting $\boldsymbol{0.5}$ from each point in the design $\Udes$:
+\begin{equation} \label{eq:Updef}
+    \Udes' = \{\vu -\boldsymbol{0.5} : \vu \in \Udes \},
+\end{equation}
+then 
+\begin{equation} \label{eq:desEquiv}
+     D(\Udes',F'_\unif,K) = D(\Udes, F_\unif, K_\unif),
+\end{equation}
+where $K$ is the kernel defined above in \eqref{eq:OrigKernel}.
+Recall that the origin is a special point in the definition of the inner product corresponding to this $K$ as a reproducing kernel in \eqref{eq:inner}.
+
+Therefore, this $K$ from \eqref{eq:OrigKernel} is an appropriate kernel to use to define the the discrepancy for designs defined with respect to the standard normal distribution, which is also centered at the origin.
+Such a discrepancy is
 \begin{align}\label{eq:DisNormald>1}
@@
 \nonumber
-  & - \frac{2}{N}\sum\limits_{\vx\in \Xdes} \prod\limits_{j=1}^d\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_j|-x_j[\Phi(x_j)-1/2]-\phi(x_j)\right]\\
-  &+\frac{1}{N^2}\sum_{\vx,\vt\in \Xdes}\prod_{j=1}^d \left[1+\frac{1}{2}|x_j|+\frac{1}{2}|t_j|-\frac{1}{2}|x_j-t_j|\right]. 
+  & - \frac{2}{N}\sum_{i=1}^N \prod\limits_{j=1}^d\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_{ij}|-x_{ij}\left(\Phi(x_{ij})-\frac 12 \right)-\phi(x_{ij})\right]\\
+  &+\frac{1}{N^2}\sum_{i,k=1}^N \prod_{j=1}^d \left[1+\frac{1}{2}\left(|x_{ij}|+|x_{kj}|-|x_{ij}-x_{kj}|\right)\right]. 
 \end{align}
-When $d=1$, the discrepancy \eqref{eq:DisNormald>1} can be further simplified to
-\begin{align}\label{eq:DisNormald=1}\nonumber
-D^2(\Xdes, \Phi_1, K)=& -\frac{2}{N}\sum_{i=1}^N \left[\max(x_i,0)-x_i\Phi_1(x_i)-\phi(x_i)\right]\\
-+&\frac{1}{N}\sum_{i=1}^N|x_i|-\frac{1}{2N^2}\sum_{i,j=1}^N|x_i-x_j|. 
-\end{align}
-In both \eqref{eq:DisNormald=1} and \eqref{eq:DisNormald>1}, $\phi(\cdot)$ is the pdf of $N(0,1)$. 
-The derivations are in the Appendix.
+Here, $\phi$ is the standard normal probability density function. 
+The derivation of \eqref{eq:DisNormald>1} is given in the Appendix.
 
-The discrepancy for the uniform distribution on unit cube $(0,1)^d$ we adapt in this work is the centered $L_2$-discrepancy \cite{Hic97a} defined as:
-\begin{align*}
-[D_2(\Udes, F_\unif, K_2)]^2 =& \left(\frac{13}{12}\right)^d - \frac{2}{N}\sum\limits_{\vu\in \Udes}\prod_{j=1}^d \left(1+\frac{1}{2}|u_j-1/2|-1/2|u_j-1/2|^2\right)\\
-\hspace{5ex}&+ \frac{1}{N^2}\sum\limits_{\vu,\vu'\in \Udes}\prod_{j=1}^d\left[1+\frac{1}{2}|u_j-1/2|+\frac{1}{2}|u_j'-1/2|-\frac{1}{2}|u_j-u_j'|\right],    
-\end{align*}
-with the reproducing kernel:
-\begin{equation}\label{eqn:oril2kernel}
-K_2(\vx,\vt) = \prod\limits_{j=1}^d\left[1+\frac{1}{2}|x_j-1/2|+\frac{1}{2}|t_j-1/2|-\frac{1}{2}|x_j-t_j|\right],
-\end{equation}
-which is the same as \eqref{eq:OrigKernel}, except it is anchored to the center $(1/2,\cdots,1/2)$ of the cube but not the origin.
-The centered $L_2$-discrepancy is invariant under reflections of $\Udes$ about any plane $x_j = 1/2$.
+%\section{Inconsistency in Discrepancy}\label{sec:inconsistency}
+Now we numerically compare the discrepancy of a uniform design, $\Udes'$ given by \eqref{eq:Updef} and the discrepancy of a design constructed by the inverse normal transformation, i.e.,  $\Xdes = \vPsi(\Udes)$ for $\vPsi$ in \eqref{eq:invNormTrans}, where the $\Udes$ leading to both is identical.
+We do not expect the magnitudes of the discrepancies to be the same, but we ask
+\begin{multline} \tag{Q'}
+    \text{does } D(\Udes'_1,F'_\unif, K)\leq D(\Udes_2',F_\unif', K) \\
+    \text{imply }
+     D(\vPsi(\Udes_1),F_\normal, K)\leq D(\vPsi(\Udes_2),F_\normal, K)?
+\end{multline}
+Again, $K$ is given by \eqref{eq:OrigKernel}.  So we are actually comparing discrepancies defined by the same kernels, but \emph{not kernels that satisfy \eqref{eq:BigQYesa}}.
 
-With the kernel in \eqref{eq:OrigKernel}, now we define a discrepancy for multivariate standard normal distribution on $\mathbb{R}^d$ that also refers to the center of the experimental region, $(0,\cdots,0)$.
-Firstly, we show that this kernel function is a reproducing kernel with a properly defined inner product as follows.
-\begin{equation}\label{eq:inner}
-\langle f,g \rangle = \sum_{u\subseteq \{1,...,d\}}\int_{\mathbb{R}^{|u|}}\frac{\partial^{|u|}}{\partial \vx_u}f(\vx_u,{\bf 0})\frac{\partial^{|u|}}{\partial \vx_u}g(\vx_u,{\bf 0})\dif \vx_u,
-\end{equation}
-where $u$ is an index set and $u\subseteq \{1, \ldots, d\}$ and $|u|$ is the cardinality of $u$. 
-Using the following operators, 
-$$\partial \vx_u = \prod\limits_{k\in u}\partial x_k \text{ and } \dif \vx_u = \prod\limits_{k\in u}\dif x_k , $$
-the $|u|$-th order partial derivative in \eqref{eq:inner} is with respective to $\vx_{u}$, the subset of variables indexed by $u$, and the integration is also with respect to the same subset of variables.
-The vector $(\vx_u,{\bf 0})$ is a $d$-dimensional vector with the dimension indexed by $u$ denoted as $\vx_u$ and the rest are set to be ${\bf 0}$. 
-In particular, for $u = \{1,...,d\}$, we have $(\vx_u,{\bf 0}) = \vx$; for $u=\emptyset$, we have $(\vx_u,{\bf 0}) = {\bf 0}$. In particular, when $d=1$,
-\begin{equation*}
-\langle f,g \rangle = f(0)g(0)+\int_{\mathbb{R}}f'(x)g'(x)\dif x.
-\end{equation*}
+\FJH{Fred got to here}
 
-With the inner product \eqref{eq:inner}, it is easy to see that above kernel function in \eqref{eq:OrigKernel} is symmetric and positive semi-definite on $\Omega = \mathbb{R}^d$, i.e., the domain of the $d$-dim multivariate normal distribution.
-Note that $K({\bf 0},\vt) = 1$ and
-\begin{align*}
-\frac{\partial^{|u|} K((\vx_u,{\bf 0}),\vt)}{\partial \vx_u}& =\prod_{i\in u}\frac 12 \left[\sign(x_i) - \sign(x_i - t_i) \right] \\
-= &\begin{cases}
-\prod\limits_{i\in u}\sign(t_i), & \min(0,t_i) < x_i \leq \max(0,t_i), i\in u\\
-0, & \textrm{otherwise}.
-\end{cases}.
-\end{align*}
-Thus, $\langle K(\cdot,\vt), K(\cdot,\vt) \rangle < \infty $, and
-\begin{align*}
-\langle f, K(\cdot,\vt) \rangle &= \sum_{u\subseteq \{1,...,d\}}\int_{\mathbb{R}^{|u|}}\frac{\partial^{|u|}}{\partial \vx_u}f(\vx_u,{\bf 0})\frac{\partial^{|u|} K((\vx_u,{\bf 0}),\vt)}{\partial \vx_u}\dif \vx_u \\
-& =     \sum_{u\subseteq \{1,...,d\}}\sum_{v\subseteq u}(-1)^{|u|-|v|}f(\vt_v,{\bf 0})\\
-& = f(\vt)
-\end{align*}
-With the reproducing kernel \eqref{eq:OrigKernel}, we can analytically derive the discrepancy for the standard normal distribution.
-
-Let $\Xdes = \{\vx_i\}_{i=1}^N$ be a design on $\Omega = \mathbb{R}^d$. 
-The squared discrepancy of the design $\Xdes$ with respect to the $d$-dimensional standard multivariate normal probability distribution $N({\bf 0}, {\bf I}_d)$ with cdf $\Phi$ is
-\begin{eqnarray}\label{eqn:discrepancy}\nonumber
-D^2(\Xdes, \Phi, K) &=& \int_{\Omega\times\Omega} K(\vx,\vt)\dif \Phi(\vx)\dif \Phi(\vt)\\
-&-&\frac{2}{N}\sum_{i=1}^N \int_{\Omega}K(\vx,\vx_i)\dif \Phi(\vx)+\frac{1}{N^2}\sum_{i,k=1}^N K(\vx_i,\vx_k).
-\end{eqnarray}
-The cdf $\Phi(\vx)=\prod_{j=1}^d \Phi_1(x_j)$, where $\Phi_1(\cdot)$ is the cdf of $N(0,1)$. 
-With simple calculation, the squared discrepancy \eqref{eqn:discrepancy} can be  computed explicitly as
-\begin{align}\label{eq:DisNormald>1}\nonumber
-&D^2(\Xdes, \Phi, K)\\\nonumber
-  &= \left(1+\sqrt{\frac{2}{\pi}}\right)^d - \frac{2}{N}\sum\limits_{\vx\in \Xdes} \prod\limits_{j=1}^d\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_j|-x_j[\Phi_1(x_j)-1/2]-\phi(x_j)\right]\\
-  &+\frac{1}{N^2}\sum_{\vx,\vt\in \Xdes}\prod_{j=1}^d \left[1+\frac{1}{2}|x_j|+\frac{1}{2}|t_j|-\frac{1}{2}|x_j-t_j|\right]. 
-\end{align}
-When $d=1$, the discrepancy \eqref{eq:DisNormald>1} can be further simplified to
-\begin{align}\label{eq:DisNormald=1}\nonumber
-D^2(\Xdes, \Phi_1, K)=& -\frac{2}{N}\sum_{i=1}^N \left[\max(x_i,0)-x_i\Phi_1(x_i)-\phi(x_i)\right]\\
-+&\frac{1}{N}\sum_{i=1}^N|x_i|-\frac{1}{2N^2}\sum_{i,j=1}^N|x_i-x_j|. 
-\end{align}
-In both \eqref{eq:DisNormald=1} and \eqref{eq:DisNormald>1}, $\phi(\cdot)$ is the pdf of $N(0,1)$. 
-The derivations are in the Appendix.
-
-\section{Inconsistency in Discrepancy}\label{sec:inconsistency}
-Using the inverse transformation method, we can generate the standard multivariate normal distribution $N({\bf 0},{\bf I}_d)$ by applying $x_{i,j}=\Phi^{-1}_j(u_{i,j})$ for $j=1,\ldots,d$ and $i=1,\ldots, N$.
-However, the inverse transformation would lead to inconsistency between the discrepancy before and after the transformation. 
-Although $\Udes = \{\vu_i\}_{i=1}^N$ is the low-discrepancy points for the uniform distribution in $[0,1]^d$, the following examples shows that it is not necessarily so that $\Xdes=\{\vx_i\}_{i=1}^N$ is also low-discrepancy.
-In other words, for two uniform designs, $\Udes_1$ and $\Udes_2$, the fact that $D(\Udes_1,F_\unif, K)\leq D(\Udes_2,F_\unif, K)$ does not imply that the inverse transformed normal design $\Xdes_1$ and $\Xdes_2$ also have $D(\Xdes_1,\Phi, K)\leq D(\Xdes_2,\Phi, K)$.
-Note that the two discrepancies $D(\Udes, F_\unif, K)$ and $D(\Xdes, \Phi, K)$ are based on the same kernel, hence the inconsistency is only due to the inverse transformation.
-
-Let $d=5$ and $n=50$. 
-We generate $B=20$ samples from uniform distribution in $[0,1]^5$ and then use the inverse distribution transformation to obtain samples following $N({\bf 0}, {\bf I}_5)$. 
+Let $d=5$ and $N=50$. 
+We generate $B=20$ independent and identically distributed (IID) uniform designs with $50$ points on $(0,1)^5$ and then use the inverse distribution transformation to obtain samples following $N({\bf 0}, {\bf I}_5)$.
 The discrepancy for uniform distribution is the $L_2$-discrepancy $D_2(\Udes,F_\unif,K_2)$ and for the standard normal distribution is \eqref{eq:DisNormald>1}. 

### 2019-05-20 normal_multidiscrepancy.m
revisions

@@ -1,0 +1,35 @@
+%calculate normal discrepancy of a multidimensional sample 
+% input: x - Nxd vector of sample points
+% output: disc - scalar, discrepancy of x w.r.t. normal probability
+% distribution
+
+function [disc] = normal_multidiscrepancy(x) 
+d = size(x,2);
+N = size(x,1);
+D = Distance_Matrix(x);
+
+%use matrix to calculate last sum of discrepancy
+vec_x = reshape(x',1,[]);
+rep_x1 = repmat(vec_x,N,1);
+rep_x2 = repmat(x,1,N);
+
+part_2Mat = reshape((1+1/2*abs(rep_x1)+1/2*abs(rep_x2)-1/2*D)',d,[])';
+
+part_2 = sum(prod(part_2Mat,2));
+
+% use loop, to assure the above code is correct
+% temp1 = 0;
+% for i = 1:N
+%     for k = 1:N
+%         temp=1;
+%         for j = 1:d
+%         temp = temp*(1+1/2*abs(x(i,j))+1/2*abs(x(k,j))-1/2*abs(x(i,j)-x(k,j)));
+%         end
+%     temp1 = temp1+temp;
+%     end
+% end
+
+disc = sqrt((1+sqrt(2/pi))^d-2/N*sum(prod(1+1/sqrt(2*pi)+1/2*abs(x)-x.*(normcdf(x)-1/2)-normpdf(x),2))+1/N^2*part_2);
+end
+
+

### 2019-05-20 test_multidisc.m

@@ -1,0 +1,82 @@
+%test the normal discrepancy after inverse transformation of a low
+%discrepancy sequence for dimonesion d.
+%input: N - scalar, number of points in low discrepancy sequence
+%       d - scalar, dimension of variable
+%ouput: disc_normal - discrepancy of points after inverse transformation
+%w.r.t. normal distribution 
+
+function [disc_x, disc_y, disc_normalx, disc_normaly] = test_multidisc(N,d)
+repeat = 20;
+%d=6;
+% s = 2; %size per dimension
+% N = s^d;
+N = 50;
+
+%try different dimensions
+corr = zeros(10,1);
+for d = 5
+    disc_z = zeros(repeat,1);
+    disc_normalz = zeros(repeat,1);
+    for i = 1:repeat
+        %generate sobol sequence
+        %     p = sobolset(d);
+        %     p = scramble(p,'MatousekAffineOwen');
+        %     x = net(p,N);
+        
+        %     disc_x = uniform_multidiscrepancy(x); %discrepancy of x w.r.t. uniforma measure
+        %     disc_x
+        %     normal_1 = norminv(x); % the normal points using low discrepancy sequence x
+        %     disc_normalx = normal_multidiscrepancy(normal_1); %discrepancy of inverse transformed x w.r.t. normal measure
+        %     disc_normalx
+        %
+        %     %shift the largest point in x to the right a little bit
+        %     y = x;
+        %     changed = 10^(-15);
+        %
+        %     %randomly pick a point to change
+        %     y(randsample(N,1),:) = changed+zeros(1,d);
+        %
+        %     %pick the smallest one to change
+        %     % distances = sqrt(sum(bsxfun(@minus, y, zeros(N,d)).^2,2));
+        %     % y(find(distances==min(distances)),:) = changed+zeros(1,d);
+        %
+        %
+        %     disc_y = uniform_multidiscrepancy(y); %discrepancy of y w.r.t. uniforma measure
+        %     disc_y
+        %     normal_2 = norminv(y); % the normal points using shifted low discrepancy sequence y
+        %     disc_normaly = normal_multidiscrepancy(normal_2); %discrepancy of inverse transformed y w.r.t. normal measure
+        %     disc_normaly
+        
+        %start with random uniform numbers
[…]

### 2019-05-20 uniform_multidiscrepancy.m

@@ -1,0 +1,38 @@
+%calculate uniform discrepancy of a multidimensional sample
+% input: x - Nxd vector of sample points
+%        d - scalar, dimension of sample
+% output: disc - scalar, cented L2 discrepancy of x w.r.t. uniform probability
+% distribution
+
+function [disc] = uniform_multidiscrepancy(x) 
+
+d = size(x,2);
+N = size(x,1);
+D = Distance_Matrix(x);
+
+
+%use matrix to calculate last sum of discrepancy
+vec_x = reshape(x',1,[]); %1xNd:vector of design points
+rep_x1 = repmat(vec_x,N,1); %NxNd: matrix of vec_x repeated N times, gives the |x_j| for the part_2
+rep_x2 = repmat(x,1,N); %NxNd: matrix of x repeated N times and placed columnwise
+
+part_2Mat = reshape((1+1/2*abs(rep_x1-1/2)+1/2*abs(rep_x2-1/2)-1/2*D)',d,[])';
+
+part_2 = sum(sum(prod(part_2Mat,2)));
+
+% use loop, to assure the above code is correct
+% temp1 = 0;
+% for i = 1:N
+%     for k = 1:N
+%         temp=1;
+%         for j = 1:d
+%         temp = temp*(1+1/2*abs(x(i,j)-1/2)+1/2*abs(x(k,j)-1/2)-1/2*abs(x(i,j)-x(k,j)));
+%         end
+%     temp1 = temp1+temp;
+%     end
+% end
+
+disc = sqrt((13/12)^d-2/N*sum(prod(1+1/2*abs(x-1/2)-1/2*(x-1/2).^2,2))+1/N^2*part_2);
+end
+
+

### 2019-05-20 InvPts_verB.tex
Updates from Overleaf

@@
 
-Changing perspectives slightly, if $F_\unif'$ denotes the uniform distribution on the cube of volume one centered at the origin, $(-\boldsymbol{0.5},\boldsymbol{0.5})^d$, and the design $\Udes'$ is constructed by  subtracting $\boldsymbol{0.5}$ from each point in the design $\Udes$:
+Changing perspectives slightly, if $F_\unif'$ denotes the uniform distribution on the cube of volume one centered at the origin, $(-0.5,0.5)^d$, and the design $\Udes'$ is constructed by  subtracting $\boldsymbol{0.5}$ from each point in the design $\Udes$:
 \begin{equation} \label{eq:Updef}

### 2019-05-20 Distance_Matrix.m

@@ -1,0 +1,15 @@
+%calculate the distance |x_j-x'_j| matrix of each dimension of each pair of points in a sample
+%input: x - Nxd matrix with N points and dimension d
+%output: D - Nx(dN) [D_1|D_2|...|D_N], with D_i = [|x_i1-x_11|,...,|x_id-x_1d|;....;|x_i1-x_N1|,...,|x_id-x_Nd|]
+
+function [D] = Distance_Matrix(x)
+
+d = size(x,2);
+N = size(x,1);
+
+D = zeros(N,d*N);
+
+for i = 1:N
+    D(:,((i-1)*d+1): (i*d)) = abs(bsxfun(@minus, x(i,:), x));
+end
+end

### 2019-05-20 Code/test_multiNormal.m
Re-arrange

@@ -1,0 +1,24 @@
+function test_multiNormal
+
+%start with grid
+
+d = 2;
+s = 10; %sample size on each dimension
+N = s^2; %total sample size
+unigrid_sample = (combvec((1:2:2*s-1)/(2*s),(1:2:2*s-1)/(2*s)))'; %change this line to construct grid sample with a different dimension
+grid_sample = norminv(unigrid_sample);
+
+grid_normDisc = normal_multidiscrepancy(grid_sample)
+
+rand_normDisc = zeros(1000,1);
+for i = 1:1000
+    rand_sample = randn(N,d);
+    rand_normDisc(i) = normal_multidiscrepancy(rand_sample);
+end
+averand_normDisc = mean(rand_normDisc)
+
+
+
+end
+
+

### 2019-05-26 InvPts_verB.tex
Updates from Overleaf

@@
 \usepackage{amssymb, xcolor,enumerate,float,mathtools,algorithmicx}
-\usepackage{algorithm}
+\usepackage{algpseudocode}
+\usepackage{algorithm, algorithmicx}
 \usepackage[numbers]{natbib}
@@
 \usepackage{url}
-\usepackage{algpseudocode}
 \usepackage{natbib}
 \usepackage{showlabels}
+
+\algnewcommand\algorithmicparam{\textbf{Parameters:}}
+\algnewcommand\PARAM{\item[\algorithmicparam]}
+\algnewcommand\algorithmicinput{\textbf{Input:}}
+\algnewcommand\INPUT{\item[\algorithmicinput]}
+%\algnewcommand\STATE{\item}
+\algnewcommand\RETURN{\State \textbf{Return }}
 
@@
 \DeclareMathOperator{\sign}{sign}
-\DeclareMathOperator{\argmax}{argmax}
+\DeclareMathOperator*{\argmax}{argmax}
 \newcommand{\Udes}{\mathcal{U}}
@@
 \newcommand{\normal}{\textup{normal}}
+\newcommand{\frakd}{\mathfrak{d}}
+\newcommand{\tK}{\widetilde{K}}
+\newcommand{\tOmega}{\widetilde{Omega}}
 
@@
     \centering
-    \includegraphics[height = 4cm]{KernelPict.eps} \qquad
-    \includegraphics[height = 4cm]{Kernel3DPict.eps}
+    \includegraphics[height = 4cm]{code/KernelPict.eps} \qquad
+    \includegraphics[height = 4cm]{code/Kernel3DPict.eps}
     \caption{The kernel defined in \eqref{eq:OrigKernel} for $d=1$.}
@@
 We do not expect the magnitudes of the discrepancies to be the same, but we ask
-\begin{multline} \tag{Q'}
+\begin{multline} \tag{Q'} \label{eq:BigQPrime}
     \text{does } D(\Udes'_1,F'_\unif, K)\leq D(\Udes_2',F_\unif', K) \\
@@
 
-\FJH{Fred got to here}
-
 Let $d=5$ and $N=50$. 
-We generate $B=20$ independent and identically distributed (IID) uniform designs with $50$ points on $(0,1)^5$ and then use the inverse distribution transformation to obtain samples following $N({\bf 0}, {\bf I}_5)$.
-The discrepancy for uniform distribution is the $L_2$-discrepancy $D_2(\Udes,F_\unif,K_2)$ and for the standard normal distribution is \eqref{eq:DisNormald>1}. 
-Figure \ref{fig:UniVsNormDisc} plots the discrepancy for normal distribution against the $L_2$-discrepancy for each of the $B=20$ samples. 
-If the inverse transformation makes the design consistent in terms of the discrepancy, the points in \ref{fig:UniVsNormDisc} should be approximately aligned on a straight line. 
-Clearly, some samples with low uniform discrepancy turn out to have large normal discrepancy after inverse transformation.
-Thus, inverse transformation cannot ensure the consistency of the design in terms of the discrepancy.
+We generate $B=20$ independent and identically distributed (IID) uniform designs, $\Udes$ with $N=50$ points on $(0,1)^5$ and then use the inverse distribution transformation to obtain IID random $N({\bf 0}, {\mathsf I}_5)$ designs, $\Xdes = \vPsi(\Udes)$.
+Figure \ref{fig:UniVsNormDisc} plots the discrepancies for normal designs, $D(\vPsi(\Udes),F_\normal, K)$,  against the discrepancies for the uniform designs, $D(\Udes,F_\unif,K_\unif) = D(\Udes',F_\unif',K)$ for each of the $B=20$ designs.
+Question \eqref{eq:BigQPrime} has a positive answer if and only if the lines passing through any two points on this plot should all have non-negative slope.
+However, that is not the case.
+Thus \eqref{eq:BigQPrime} is false.
 
@@
 \begin{center}
-\includegraphics[width=8cm]{d5n50.eps}
+\includegraphics[width=8cm]{code/d5n50.eps}
 \caption{Uniform Discrepancy Vs. Normal Discrepancy. \label{fig:UniVsNormDisc}}
@@
 
-We further investigate the relationship between the uniform discrepancy of a design and the normal discrepancy of the same design after inverse transformation.
-Varying the dimension $d$ from 1 to 10, we calculate the sample correlation coefficients between the two discrepancies of the $B=500$ uniform designs of size $N=50$ and corresponding normal designs after inverse transformation, and plot the correlations against $d$ in \ref{fig:UniVsNormDisc}.
-It can be seen that the phenomenon of inconsistency in discrepancies becomes more pronounced as $d$ increases.
+We further investigate the relationship between the discrepancy of a uniform design and the  discrepancy of the same design after inverse normal transformation.
+Varying the dimension $d$ from $1$ to $10$, we calculate the sample correlation between $D(\vPsi(\Udes),F_\normal, K)$ and $D(\Udes,F_\unif,K_\unif) = D(\Udes',F_\unif',K)$ for $B=500$ IID designs of size $N=50$.
+Figure \ref{fig:UniVsNormDisc} displays the correlation as a function of $d$.
+Although the correlation is positive, it degrades with increasing $d$.
 
-\begin{figure}[ht]
-\label{fig:DimVsDisc}
+\FJH{Fred does not understand this example.}
+A simple example of integral approximation below shows that a naively inverse transformed sequence $\Udes$ could result in ridiculous estimate even if $D(\Udes,F_\unif, \tilde{K})$ is small.
+
+\emph{Example}: Consider estimating the integral $\int_{\mathbb{R}^d} e^{|x_1|+\cdots+|x_d|}\dif \Phi(\vx)$ using Monte Carlo method, with $d=10$ and $N=200$ points.
+
+% Table generated by Excel2LaTeX from sheet 'Sheet1'
+\begin{table}[htbp]
   \centering
-{\includegraphics[width=8cm]{dimVsdisc.eps}}
-\caption{Correlation between Uniform Discrepancy and Normal Discrepancy with Different Variable Dimensions}
-\end{figure}
+  \caption{Estimate}
+    \begin{tabular}{rcccc}
+    \hline
+   $\Udes$       & $D(\Udes,F_\unif, \tilde{K})$     & $D(\vPsi(\Udes),F_\normal, K)$     & Estimate \\
+    \hline
+    $x$     &   0.1754    &  18.61     & 198.68 \\
+    $y$     &  0.1800      &  286.35     & $1.54\times 10^{32}$ \\
+    \hline
+    \end{tabular}%
+  \label{tab:addlabel}%
+\end{table}%
 
-The root cause of this inconsistency can be revealed as follows. 
-For simplicity, let $d=1$. 
-Taking the inverse transformation $x_{i}=\Phi^{-1}_1(u_{i})$ in the normal discrepancy \eqref{eqn:discrepancy}, 
-\begin{align*}
-&D^2(\Xdes, \Phi_1, K) = \int_{[0,1]^2} K(\Phi^{-1}_1(u),\Phi^{-1}_1(u'))\dif \Phi(\Phi^{-1}_1(u))\dif \Phi(\Phi^{-1}_1(u'))\\
-&-\frac{2}{N}\sum_{i=1}^N \int_0^1 K(\Phi^{-1}_1(u),\Phi^{-1}_1(u_i))\dif \Phi(\Phi^{-1}_1(u))+\frac{1}{N^2}\sum_{i,k=1}^N K(\Phi^{-1}_1(u_i), \Phi^{-1}_1(u_j))\\
-&=\int_{[0,1]^2} K(\Phi^{-1}_1(u),\Phi^{-1}_1(u'))\dif u\dif u'\\
-&-\frac{2}{N}\sum_{i=1}^N \int_0^1 K(\Phi^{-1}_1(u),\Phi^{-1}_1(u_i))\dif u+\frac{1}{N^2}\sum_{i,k=1}^N K(\Phi^{-1}_1(u_i), \Phi^{-1}_1(u_j))\\
-&=D^2(\Udes,F_\unif,\tilde{K}),
-\end{align*}
-where $\tilde{K}(\cdot,\cdot)=K(\Phi^{-1}_1(\cdot), \Phi^{-1}_1(\cdot)): [0, 1]\rightarrow \mathbb{R}_{+}$. 
-Although $\tilde{K}(\cdot,\cdot)$ is still a valid kernel function for the uniform distribution, the resulting discrepancy $D(\Udes,F_\unif, \tilde{K})$ is no longer the same as $D_2(\Udes, F_\unif, K_2)$, and their difference only increases as the dimension $d$ becomes higher due to the effect of the product in $D_2(\Udes, F_\unif, K_2)$.
-The difference in kernel $K_2$ and $\tilde{K}$ also leads to different RKHS of integrand functions.
-
+\FJH{Fred got to here}
 \section{Improvement by the Coordinate-Exchange Method}\label{sec:CoordEx}
@@
 The coordinate-exchange algorithm is an iterative optimization method.
-It finds the ``worst" coordinate $x_{ij}$ of the current design, and replace it with a better coordinate that improves the current design criterion. 
-The most appealing advantage of the coordinate-exchange algorithm is that it renders the $N\times d$ dimension of the decision variables of the original optimal design problem to just one dimension as it changes one coordinate at a time.
-This greatly reduces the difficulty of the optimization problem.
+It finds the ``worst" coordinate $x_{ij}$ of the current design and replace it with a better coordinate that decreases the discrepancy. 
+The most appealing advantage of the coordinate-exchange algorithm is that at each step one need only solve a univariate optimization problem.
 
-We format the $N$ points of $d$-dim design points $\{\vx_i\}_{i=1}^N$ into a design matrix  $\mX^\top =[\vx_1,\ldots, \vx_N]$, and $x_{ij}$ refers to the $(i,j)$-th element of $\mX$, and it also refers to the $j$-th dimension of the $i$-th sample point.
-To find the ``worst'' coordinate, we use row and column deletion function, as in \cite{kang2018stochastic}.
-Define the row deletion function of the $i$-th row as follows. 
-\begin{eqnarray}\label{eq:rowdeletion}
-&& d_r(i) = D^2(\Xdes)-D^2(\Xdes\backslash \vx_i)\nonumber\\
-&=& -2\prod\limits_{s=1}^dc(x_{is}) + \frac{1}{N-1}\left(2\sum_{j=1}^N\prod_{s=1}^d h(x_{is},x_{js})-\prod_{s=1}^d h(x_{is},x_{is})\right). 
-\end{eqnarray}
+First, we define the point deletion function, $\frakd_p$, as the change in square discrepancy resulting from removing the a point from the design:
+\begin{equation}\label{eq:rowdeletion}
+\frakd_p(i) = D^2(\Xdes)-D^2(\Xdes\backslash \{\vx_i\}).
+\end{equation}
+Here, the design $\Xdes\backslash \{\vx_i\}$ is the $N-1$ point design with the point $\{\vx_i\}$ removed.
+We suppress the choice of target distribution and kernel in the above discrepancy notation for simplicity.
+We then choose
+\begin{equation} \label{eq:rowchoice}
+    i^*=\argmax_{i=1,\ldots,N} \frakd_p(i).
+\end{equation}
+If $\frakd_p(i^*) > 0$, it means that the smaller design with $\vx_{i^*}$ removed has a smaller discrepancy.
+Thus, it is reasonable to assume that moving $\vx_{i^*}$ might lead to a smaller discrepancy.
+On the other hand, if $\frakd_p(i^*)< 0$, it means that removing any $\vx_i$ makes the discrepancy bigger, but removing $\vx_{i^*}$ does the least damage.
+Again,  $\vx_{i^*}$ is a prime candidate for modification.
+
+Next, we define a coordinate deletion function, $\frakd_{c}$, as the change in the square discrepancy resulting from removing a coordinate in our calculation of the discrepancy:
+\begin{equation}\label{eq:coorddeletion}
+\frakd_c(k) = D^2(\Xdes)-D^2(\Xdes_{-k}).
+\end{equation}
+Here, the design $\Xdes_{-k}$ still has $N$ points but now only $d$ dimensions, the $k^{\text{th}}$ coordinate having been removed.
+For this calculation to be feasible, we need the target distribution to independent marginals defined on the domain.
+Also, the kernel to be of product form.
+To simplify the notation, we assume a somewhat stronger condition, namely that each term in the product defining the kernel is the same for every coordinate:
+\begin{equation}
+    \label{eq:prodkernel}
+    \Omega = \tOmega \times \cdots \times \tOmega, \qquad K(\vt,\vx) = \prod_{k=1}^d \tK(t_k,x_k), \qquad \tK:\tOmega \times \tOmega \to \reals.
+\end{equation}
+where the term in the product is 
+We then choose 
+\begin{equation} \label{eq:rowchoice}
+    k^*=\argmax_{k=1, \ldots, d} \frakd_c(k).
+\end{equation}
+For reasons analogous to those given above, the $k^{*\text{th}}$ coordinate seems the best candidate for change.
+
+Let $\Xdes^*(x)$ denote the design that results from replacing $x_{i^*k^*}$ by $x$.
+We now define $\Delta(x)$ as improvement in the squared discrepancy resulting from replacing $\Xdes$ by $\Xdes^*(x)$:
+\begin{equation}\label{eq:deltafun}
+\Delta(x) = D^2(\Xdes)-D^2(\Xdes^*(x)).
+\end{equation}
+If we can find an $x$ for which $\Delta(x)$ is positive, then we can reduce the discrepancy.  This is the rationale for the coordinate-exchange algorithm given in  Algorithm \ref{alg:coorex}.
+
+\begin{algorithm}[ht]
+\caption{Coordinate exchange method\label{alg:coorex}}
+\begin{algorithmic}[1]
+\INPUT An initial design $\Xdes$ on the domain $\Omega$, a target distribution, $F$, and a kernel, $K$ of the form \eqref{eq:prodkernel}.
+\State Compute the point deletion function $\frakd_p(1), \ldots, \frakd_p(N)$ for the design $\Xdes$, and choose the row $i^*$ with the largest row deletion value, i.e.
+$i^* = \argmax_{i} \frakd_p(i)$.
+\State Compute the coordinate deletion function $\frakd_c(1), \ldots, \frakd_c(d)$ and choose the column $j^*$ with the largest column deletion value, i.e., $k^* = \argmax_{k} \frakd_c(k)$. 
+\State Choose the replacement value for $x_{i^*k^*}$ by solving the univariate nonlinear optimization problem
+\[
+x^* = \argmax_{x \in \Omega_k} \Delta(x).
+\]
+\If{$\Delta(x^*>0$} 
+\State {Replace $x_{i^*k^*}$ with $x^*$ in the design $\Xdes$, i.e., let  $\Xdes(x^*)$ replace the old $\Xdes$.}
+\Else 
+\State{Terminate the algorithm and the design $\Xdes$.} 
+\EndIf
+\end{algorithmic}
+\end{algorithm}
+
+For kernels of product form, \eqref{eq:prodkernel}, and target distributions with independent marginals, the formula for the squared discrepancy in \eqref{eq:discDef} becomes
+\begin{align}
+\nonumber
+    D^2(\Xdes,\rho,K)  & = \prod_{k=1}^d c_k  - \frac 2N \sum_{i=1}^N \prod_{k=1}^d h_k(x_{ik}) + \frac{1}{N^2}  \sum_{i,j=1}^N \prod_{k=1}^d K_k(x_{ik},x_{jk}),
+    \intertext{where}
+    c_k & = \int_{\Omega_k \times \Omega_k} \tK_k(t_k,x_k) \, \varrho_k(t) \varrho_k (x) \, \dif t\dif x, \\
+    h_k(x) & = \int_{\Omega_k} \tK_k(t,x)  \, \varrho_k(t) \, \dif t.
+\end{align}
+Then the point deletion function becomes fred
+\begin{align}\label{eq:rowdeletionA}
+\frakd_p(i) 
+&= \frac{2}{N}\biggl[ \frac{1}{N-1} \sum_{\substack{j=1 \\ j \ne i}}^N \prod_{k=1}^d h_k(x_{ik}) - \prod_{k=1}^d h_k(x_{ik})  \biggr] \\
+& \qquad \qquad + \frac{1}{N^2}\biggl[\frac{1-2N}{(N-1)^2}\sum_{\substack{j,m=1 \\ j,m \ne i}}^N \tK_k(x_{jk},x_{mk}) + \sum_{j=1}^N\prod_{s=1}^d h(x_{is},x_{js})-\prod_{s=1}^d h(x_{is},x_{is})\biggr].
+\end{align}
 We use $D(\Xdes)$ as a simplified notation for the discrepancy as the target design is always standard normal distribution and the kernel function is \eqref{eq:OrigKernel}. 
@@
 \begin{algorithm}[ht]
-\begin{algorithmic}[1]\label{alg:coorex}
+\begin{algorithmic}[1]%\label{alg:coorex}
 \caption{Coordinate exchange method}
@@
 \centering
-{\subfigure[$d=2,N=30$] {\includegraphics[width=5.5cm]{boxplot_d2n30.eps}}}
+{\subfigure[$d=2,N=30$] {\includegraphics[width=5.5cm]{code/boxplot_d2n30.eps}}}
 \quad
 {\subfigure [$d=3, N=50$]
-{\includegraphics[width=5.5cm]{boxplot_d3n50.eps}}}
+{\includegraphics[width=5.5cm]{code/boxplot_d3n50.eps}}}
 \quad
-{\subfigure[$d=4, N=70$] {\includegraphics[width=5.5cm]{boxplot_d4n70.eps}}}
+{\subfigure[$d=4, N=70$] {\includegraphics[width=5.5cm]{code/boxplot_d4n70.eps}}}
 \quad
-{\subfigure[$d=5, N=90$] {\includegraphics[width=5.5cm]{boxplot_d5n90.eps}}}
+{\subfigure[$d=5, N=90$] {\includegraphics[width=5.5cm]{code/boxplot_d5n90.eps}}}
 \quad
-{\subfigure[$d=6, N=110$] {\includegraphics[width=5.5cm]{boxplot_d6n110.eps}}}
+{\subfigure[$d=6, N=110$] {\includegraphics[width=5.5cm]{code/boxplot_d6n110.eps}}}
 \quad
-{\subfigure[$d=7, N=130$] {\includegraphics[width=5.5cm]{boxplot_d7n130.eps}}}
+{\subfigure[$d=7, N=130$] {\includegraphics[width=5.5cm]{code/boxplot_d7n130.eps}}}
 \caption{Performance Comparison of Three Generators}\label{fig:generatorcomp}

### 2019-05-26 code/CE_Normal.m

@@ -1,0 +1,25 @@
+%use coordinate exchange to optimize the discrepancy
+
+function [low_discNormal,normaldisc] = CE_Normal(x)
+
+delta = 0.01;
+maxrun = 50;
+count = 0;
+opt_delta=-1;
+
+while opt_delta< -1*10^(-10) && count<maxrun
+    [x,opt_delta] = coordinate_exchange(x);
+    count = count+1;
+    normaldisc = normal_multidiscrepancy(x);
+end
+
+low_discNormal=x;
+
+
+end
+
+
+
+
+
+

### 2019-05-26 code/compare_generator.m

@@ -1,0 +1,72 @@
+%compare proposed generator with 'randn'
+
+function  compare_generator
+
+repeat = 500;
+disc_opt = zeros(repeat,1);
+disc_randn = zeros(repeat,1);
+disc_low = zeros(repeat,1);
+d=2;
+n=30;
+
+for i = 1:repeat 
+    %generate normal random numbers using inverse distribution transformation
+    p = sobolset(d);
+    p = scramble(p,'MatousekAffineOwen');
+    uniform = net(p,n);
+    x = norminv(uniform);
+    disc_low(i) = normal_multidiscrepancy(x);
+    [low_discNormal,new_normaldisc] = CE_Normal(x);
+    disc_opt(i) = new_normaldisc;   
+    rand_sample = randn(n,d);
+    disc_randn(i) = normal_multidiscrepancy(rand_sample);
+    repeat_index=repeat_index+1;
+end
+
+%read data
+disc_opt = disc_d7n130(1:500);
+disc_low = disc_d7n130(501:1000);
+disc_randn = disc_d7n130(1001:1500);
+
+
+%plot opt Vs randn
+disc = [disc_opt;disc_randn];
+g = [ones(repeat,1);2*ones(repeat,1)];
+
+figure
+subplot(2,1,1);
+boxplot(disc,g)
+%title('Discrepancies of Proposed Generator and Randn Generator')
+ylabel('Normal Discrepancy')
+a = get(gca,'XTickLabel');
+set(gca,'XTickLabel',a,'FontName','Times','fontsize',21)
+xticklabels({'NG2','Randn'})
+
+%plot opt Vs inversed Sobol
+disc = [disc_low;disc_opt];
+g = [ones(repeat,1);2*ones(repeat,1)];
+
+subplot(2,1,2);
+boxplot(disc,g)
+%title('Discrepancies of Proposed Generator and Inversed Sobol')
+ylabel('Normal Discrepancy')
+a = get(gca,'XTickLabel');
+set(gca,'XTickLabel',a,'FontName','Times','fontsize',21)
+xticklabels({'NG1','NG2'})
+
+%plot opt, inversed Sobol and randn
+disc = [disc_low;disc_opt;disc_randn];
+g = [ones(repeat,1);2*ones(repeat,1);3*ones(repeat,1)];
+
+figure
+boxplot(disc,g)
+%title('Discrepancies of Three Generators')
+ylabel('Normal Discrepancy')
[…]

### 2019-05-26 code/coordinate_exchange.m

@@ -1,0 +1,56 @@
+function [x,opt_delta] = coordinate_exchange(x)
+
+N = size(x,1); %number of points
+d = size(x,2); %dimension
+
+temp_x = x';
+
+c = @(a) 1+1/sqrt(2*pi)+1/2*abs(a)-a*(normcdf(a)-1/2)-normpdf(a);
+h = @(a,b) 1+1/2*abs(a)+1/2*abs(b)-1/2*abs(a-b);
+
+c_mat = arrayfun(c,x); %function c evaluated all elements of x;
+
+%[(h_mat)_1;(h_mat)_2;...;(h_mat)_N], with (h_mat)_i as a Nxd matrix = [h(x_i1,x_11),...,h(x_id,x_1d);....;h(x_i1,x_N1),...,h(x_id,x_Nd)]
+h_mat = zeros(N^2,d); %function h(x_ij,x_rj) for i,r=1,...,N,j=1,...,d.
+D = zeros(N,N*d); %distance matrix
+
+for i = 1:N
+    D(:,((i-1)*d+1): (i*d)) = abs(bsxfun(@minus, x(i,:), x));
+end
+
+h_mat = (reshape((1+1/2*abs(repmat((temp_x(:))',N,1))+ 1/2*abs(repmat(x,1,N))-1/2*abs(D))',d,N*N))';
+
+row_deletion = -2*prod(c_mat,2)+(N-1)*(2*sum(reshape(prod(h_mat,2),N,N)',2)-prod((1+abs(x)),2));
+
+col_deletion = zeros(d,1);
+for j = 1:d
+    c_new = zeros(N,d);
+    h_new = zeros(N^2,d);
+    c_new = c_mat;
+    c_new(:,j) = c_mat(:,j)-1;
+    h_new = h_mat;
+    h_new(:,j) = h_mat(:,j)-1;
+    col_deletion(j) = -2*sum(prod(c_new,2))+1/N*sum(prod(h_new,2));
+end
+
+[opt_rowde,row_choice] = max(row_deletion);
+[opt_colde,col_choice] = max(col_deletion);
+
+change_row = x(row_choice,:);
+change_point = change_row(col_choice);
+change_col = x(:,col_choice);
+change_col(row_choice) = [];
+change_row(col_choice) = [];
+h_change = h_mat((row_choice-1)*N+2:row_choice*N,:);
+h_change(:,col_choice) = [];
+
+h_prime = @(z) h(z,change_col);
[…]

### 2019-05-26 InvPts_verB.tex
Updates from Overleaf
updating from home computer

@@
 \newcommand{\tK}{\widetilde{K}}
-\newcommand{\tOmega}{\widetilde{Omega}}
+\newcommand{\tOmega}{\widetilde{\Omega}}
+\newcommand{\tvarrho}{\widetilde{\varrho}}
 
@@
 
-For kernels of product form, \eqref{eq:prodkernel}, and target distributions with independent marginals, the formula for the squared discrepancy in \eqref{eq:discDef} becomes
+For kernels of product form, \eqref{eq:prodkernel}, and target distributions with independent and identical marginals, the formula for the squared discrepancy in \eqref{eq:discDef} becomes
 \begin{align}
 \nonumber
-    D^2(\Xdes,\rho,K)  & = \prod_{k=1}^d c_k  - \frac 2N \sum_{i=1}^N \prod_{k=1}^d h_k(x_{ik}) + \frac{1}{N^2}  \sum_{i,j=1}^N \prod_{k=1}^d K_k(x_{ik},x_{jk}),
+    D^2(\Xdes,\rho,K)  & = c^d  - \frac 2N \sum_{i=1}^N \prod_{k=1}^d h(x_{ik}) + \frac{1}{N^2}  \sum_{i,j=1}^N \prod_{k=1}^d \tK(x_{ik},x_{jk}),
     \intertext{where}
-    c_k & = \int_{\Omega_k \times \Omega_k} \tK_k(t_k,x_k) \, \varrho_k(t) \varrho_k (x) \, \dif t\dif x, \\
-    h_k(x) & = \int_{\Omega_k} \tK_k(t,x)  \, \varrho_k(t) \, \dif t.
+    c & = \int_{\tOmega \times \tOmega} \tK(t_k,x_k) \, \tvarrho(t) \tvarrho (x) \, \dif t\dif x, \\
+    h(x) & = \int_{\tOmega} \tK_k(t,x)  \, \tvarrho(t) \, \dif t.
 \end{align}
-Then the point deletion function becomes fred
-\begin{align}\label{eq:rowdeletionA}
+Then the point deletion function becomes 
+\begin{align}
+\nonumber
 \frakd_p(i) 
-&= \frac{2}{N}\biggl[ \frac{1}{N-1} \sum_{\substack{j=1 \\ j \ne i}}^N \prod_{k=1}^d h_k(x_{ik}) - \prod_{k=1}^d h_k(x_{ik})  \biggr] \\
-& \qquad \qquad + \frac{1}{N^2}\biggl[\frac{1-2N}{(N-1)^2}\sum_{\substack{j,m=1 \\ j,m \ne i}}^N \tK_k(x_{jk},x_{mk}) + \sum_{j=1}^N\prod_{s=1}^d h(x_{is},x_{js})-\prod_{s=1}^d h(x_{is},x_{is})\biggr].
+&= \frac{2}{N}\biggl[ \frac{1}{N-1} \sum_{\substack{j=1 \\ j \ne i}}^N \prod_{k=1}^d h(x_{ik}) - \prod_{k=1}^d h(x_{ik})  \biggr] \\
+\nonumber
+& \qquad \qquad + \frac{1}{N^2}\biggl[\frac{1-2N}{(N-1)^2}\sum_{\substack{j,m=1 \\ j,m \ne i}}^N \prod_{k=1}^d \tK(x_{jk},x_{mk}) + 2 \sum_{\substack{j=1 \\ j \ne i}}^N\prod_{k=1}^d \tK(x_{ik},x_{jk}) \\
+& \qquad \qquad + \prod_{k=1}^d \tK(x_{ik},x_{ik})\biggr].  \label{eq:rowdeletionA}
 \end{align}

### 2019-05-26 InvPts_verB.tex
Changes from remote

--- 2019-05-26 InvPts_verB.tex
@@
 \newcommand{\tK}{\widetilde{K}}
-\newcommand{\tOmega}{\widetilde{Omega}}
+\newcommand{\tOmega}{\widetilde{\Omega}}
+\newcommand{\Order}{\mathcal{O}}
 
@@
 \begin{equation}\label{eq:rowdeletion}
-\frakd_p(i) = D^2(\Xdes)-D^2(\Xdes\backslash \{\vx_i\}).
+\frakd_p(i) = D^2(\Xdes)-\left(\frac{N-1}{N}\right)^2 D^2(\Xdes\backslash \{\vx_i\}).
 \end{equation}
@@
 \end{equation}
-If $\frakd_p(i^*) > 0$, it means that the smaller design with $\vx_{i^*}$ removed has a smaller discrepancy.
-Thus, it is reasonable to assume that moving $\vx_{i^*}$ might lead to a smaller discrepancy.
-On the other hand, if $\frakd_p(i^*)< 0$, it means that removing any $\vx_i$ makes the discrepancy bigger, but removing $\vx_{i^*}$ does the least damage.
-Again,  $\vx_{i^*}$ is a prime candidate for modification.
+The definition of $i^*$ means that removing $\vx_{i^*}$ from the design $\Xdes$ results in the smallest discrepancy among all possible deletions.
+Thus, $\vx_{i^*}$ is helping the least, which makes it a prime candidate for modification.
 
@@
     \label{eq:prodkernel}
-    \Omega = \tOmega \times \cdots \times \tOmega, \qquad K(\vt,\vx) = \prod_{k=1}^d \tK(t_k,x_k), \qquad \tK:\tOmega \times \tOmega \to \reals.
+    \Omega = \tOmega \times \cdots \times \tOmega, \qquad K(\vt,\vx) = \prod_{k=1}^d [1+ \tK(t_k,x_k)], \qquad \tK:\tOmega \times \tOmega \to \reals.
 \end{equation}
@@
 \nonumber
-    D^2(\Xdes,\rho,K)  & = \prod_{k=1}^d c_k  - \frac 2N \sum_{i=1}^N \prod_{k=1}^d h_k(x_{ik}) + \frac{1}{N^2}  \sum_{i,j=1}^N \prod_{k=1}^d K_k(x_{ik},x_{jk}),
+    D^2(\Xdes,\rho,K)  & = c^d  - \frac 2N \sum_{i=1}^N H(\vx_{i}) + \frac{1}{N^2}  \sum_{i,j=1}^N K(\vx_{i},x_{j}),
     \intertext{where}
-    c_k & = \int_{\Omega_k \times \Omega_k} \tK_k(t_k,x_k) \, \varrho_k(t) \varrho_k (x) \, \dif t\dif x, \\
-    h_k(x) & = \int_{\Omega_k} \tK_k(t,x)  \, \varrho_k(t) \, \dif t.
+    c & = \int_{\Omega_k \times \Omega_k} \tK_k(t_k,x_k) \, \varrho_k(t) \varrho_k (x) \, \dif t\dif x, \\
+    H(\vx) = \prod_{k=1}^d [1+ h(x_{k})]
+    h(x) & = \int_{\Omega_k} \tK_k(t,x)  \, \varrho_k(t) \, \dif t.
 \end{align}
-Then the point deletion function becomes fred
-\begin{align}\label{eq:rowdeletionA}
+For a standard multivariate normal target distribution and the kernel defined in \eqref{eq:OrigKernel}, we have
+\begin{align*}
+c &= 1+\sqrt{\frac{2}{\pi}}, \\
+h(x) &= \frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x|-x[\Phi(x)-1/2]-\phi(x),\\
+\tK(t,x) &= \frac{1}{2} (|t|+ |x|- |x-t|).
+\end{align*}
+
+The point deletion function defined in \eqref{eq:rowdeletion} then can be expressed as
+\begin{align}
+\nonumber
 \frakd_p(i) 
-&= \frac{2}{N}\biggl[ \frac{1}{N-1} \sum_{\substack{j=1 \\ j \ne i}}^N \prod_{k=1}^d h_k(x_{ik}) - \prod_{k=1}^d h_k(x_{ik})  \biggr] \\
-& \qquad \qquad + \frac{1}{N^2}\biggl[\frac{1-2N}{(N-1)^2}\sum_{\substack{j,m=1 \\ j,m \ne i}}^N \tK_k(x_{jk},x_{mk}) + \sum_{j=1}^N\prod_{s=1}^d h(x_{is},x_{js})-\prod_{s=1}^d h(x_{is},x_{is})\biggr].
+&= \frac{(2N-1)c^d}{N^2} - \frac{2}{N}\biggl[ \frac{1}{N} \sum_{j=1}^N  H(\vx_{j}) + \left(1 - \frac 1N \right) H(\vx_{i})  \biggr] \\
+\label{eq:rowdeletionA}
+& \qquad \qquad + \frac{1}{N^2}\biggl[2 \sum_{j=1}^N K(\vx_{i},\vx_{j})-\prod_{k=1}^d K(\vx_{i},\vx_{i})\biggr]. 
 \end{align}
+The computational cost for $\frakd_p(1), \ldots, \frakd_p(N)$ is then $\Order(dN^2)$, which is the same order as the cost of the discrepancy of a single design.
+
 We use $D(\Xdes)$ as a simplified notation for the discrepancy as the target design is always standard normal distribution and the kernel function is \eqref{eq:OrigKernel}. 

### 2019-05-26 InvPts_verB.tex

@@
 \newcommand{\tOmega}{\widetilde{\Omega}}
+\newcommand{\tvarrho}{\widetilde{\varrho}}
 \newcommand{\Order}{\mathcal{O}}
@@
 
-For kernels of product form, \eqref{eq:prodkernel}, and target distributions with independent marginals, the formula for the squared discrepancy in \eqref{eq:discDef} becomes
+For kernels of product form, \eqref{eq:prodkernel}, and target distributions with independent and identical marginals, the formula for the squared discrepancy in \eqref{eq:discDef} becomes
 \begin{align}
@@
     \intertext{where}
+    c & = \int_{\tOmega \times \tOmega} \tK(t_k,x_k) \, \tvarrho(t) \tvarrho (x) \, \dif t\dif x, \\
+    h(x) & = \int_{\tOmega} \tK_k(t,x)  \, \tvarrho(t) \, \dif t.
     c & = \int_{\Omega_k \times \Omega_k} \tK_k(t_k,x_k) \, \varrho_k(t) \varrho_k (x) \, \dif t\dif x, \\

### 2019-05-26 InvPts_verB.tex
changes offline

@@
 \nonumber
-    D^2(\Xdes,\rho,K)  & = c^d  - \frac 2N \sum_{i=1}^N H(\vx_{i}) + \frac{1}{N^2}  \sum_{i,j=1}^N K(\vx_{i},x_{j}),
+    D^2(\Xdes,\rho,K)  & = (1+c)^d  - \frac 2N \sum_{i=1}^N H(\vx_{i}) + \frac{1}{N^2}  \sum_{i,j=1}^N K(\vx_{i},x_{j}),
     \intertext{where}
-    c & = \int_{\tOmega \times \tOmega} \tK(t_k,x_k) \, \tvarrho(t) \tvarrho (x) \, \dif t\dif x, \\
-    h(x) & = \int_{\tOmega} \tK_k(t,x)  \, \tvarrho(t) \, \dif t.
-    c & = \int_{\Omega_k \times \Omega_k} \tK_k(t_k,x_k) \, \varrho_k(t) \varrho_k (x) \, \dif t\dif x, \\
-    H(\vx) = \prod_{k=1}^d [1+ h(x_{k})]
-    h(x) & = \int_{\Omega_k} \tK_k(t,x)  \, \varrho_k(t) \, \dif t.
+    h(x) & = \int_{\tOmega} \tK_k(t,x)  \, \tvarrho(t) \, \dif t, \\
+    c & = \int_{\tOmega \times \tOmega} \tK(t_k,x_k) \, \tvarrho(t) \tvarrho (x) \, \dif t\dif x = \int_{\tOmega} h(x) \, \tvarrho(x) \, \dif x, \\
+    H(\vx) &= \prod_{k=1}^d [1+ h(x_{k})].
 \end{align}
+We note that an evaluation of $h(x)$ and $\tK(t,x)$ require $\Order(1)$ operations, while an evaluation of $H(\vx)$ and $K(\vt,\vx)$ require $\Order(d)$ operations.
+The computation of $D(\Xdes,\rho,K)$ requires $\Order(dN^2)$ operations because of the double sum.
 For a standard multivariate normal target distribution and the kernel defined in \eqref{eq:OrigKernel}, we have
 \begin{align*}
-c &= 1+\sqrt{\frac{2}{\pi}}, \\
+c &= \sqrt{\frac{2}{\pi}}, \\
 h(x) &= \frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x|-x[\Phi(x)-1/2]-\phi(x),\\
@@
 \frakd_p(i) 
-&= \frac{(2N-1)c^d}{N^2} - \frac{2}{N}\biggl[ \frac{1}{N} \sum_{j=1}^N  H(\vx_{j}) + \left(1 - \frac 1N \right) H(\vx_{i})  \biggr] \\
+&= \frac{(2N-1)(1+c)^d}{N^2} - \frac{2}{N}\biggl[ \frac{1}{N} \sum_{j=1}^N  H(\vx_{j}) + \left(1 - \frac 1N \right) H(\vx_{i})  \biggr] \\
 \label{eq:rowdeletionA}
-& \qquad \qquad + \frac{1}{N^2}\biggl[2 \sum_{j=1}^N K(\vx_{i},\vx_{j})-\prod_{k=1}^d K(\vx_{i},\vx_{i})\biggr]. 
+& \qquad \qquad + \frac{1}{N^2}\biggl[2 \sum_{j=1}^N K(\vx_{i},\vx_{j})- K(\vx_{i},\vx_{i})\biggr]. 
 \end{align}
@@
 
-We use $D(\Xdes)$ as a simplified notation for the discrepancy as the target design is always standard normal distribution and the kernel function is \eqref{eq:OrigKernel}. 
-The notation $\Xdes\backslash \vx_i$ means that the design $\Xdes$ without the $i$-th point $\vx_i$. 
-Here $c(x)$ and $h(x,y)$ are 
-\begin{align*}
-c(x) &= 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x|-x[\Phi_1(x)-1/2]-\phi(x),\\
-h(x,y) &= 1+\frac{1}{2}|x|+\frac{1}{2}|y|-\frac{1}{2}|x-y|.
-\end{align*}
-The definition of $d_r(i)$ represents the change in $D^2(\Xdes)$ when $\vx_i$ is removed from the design. 
-If $d_r(i)\geq 0$, it means that removing $\vx_i$ would lead to a smaller discrepancy. 
-Thus, it is reasonable to assume $\vx_i$ has the potential to be updated and leads to a smaller discrepancy. 
-Among all the design points that $d_r(i)\geq 0$, we should pick the $i_0$ that has largest $d_r(i)$, because removing $\vx_i$ leads to the biggest improvement, so we consider this row has the biggest potential.
-On the other hand, if $d_r(i)< 0$, it means that removing $\vx_i$ would make the discrepancy bigger, and thus make the design worse, so we should keep $\vx_i$ in the design. 
-However, if $d_r(\vx_i)\leq 0$ for $i=1,\ldots, N$, and we must pick a row index, then we should pick the $i_0$ that has the smallest $\abs{d_r(\vx_i)}$ because removing $\vx_{i_0}$ would make the design worse with the least degree compared to other indices.
-Combining both scenarios, we should pick the row index by 
-\[
-i^*=\argmax_{i=1,\ldots,N} d_r(i).
-\]
-Similarly, we define the column deletion function as follows. 
-\begin{eqnarray}\label{eq:coldeletion}
-d_c(j) &=& -\frac{2}{N}\sum_{i=1}^N(c(x_{ij})-1)\prod\limits_{\substack{s=1,\\ s\neq j}}^dc(x_{is})\nonumber\\ 
-&&+\frac{1}{N^2}\sum_{\substack{i=1,\\ r=1}}^N\left(h(x_{ij},x_{rj})-1\right)\prod_{\substack{s=1\\s\neq j}}^d h(x_{is},x_{rs}).
-\end{eqnarray}
-We pick the column index by 
-\[
-j^*=\argmax_{j=1,\ldots,d} d_c(j).
-\]
-Once the $(i^*, j^*)$-th coordinate is identified to be changed, we compute the delta function $\Delta(x_{i^*j^*},x)$, which represents the decrease in $D^2(\Xdes)$, if $x_{i^*j^*}$ is replaced by $x \in \mathbb{R}$.
-The delta function can be computed as follows. 
-\begin{eqnarray}\label{eq:deltafunction}
-&&\Delta(x_{{i^*j^*}}, x)\nonumber\\
-&=& -\frac{2}{N}\left(c(x_{i^*j^*})-c(x)\right)\prod\limits_{\substack{j=1,\\j\neq j^*}}^dc(x_{i^*j})\nonumber\\
-&&+\frac{1}{N^2}\left(2\sum_{\substack{i=1,\\i\neq i^*}}^N(h(x_{i^*j^*},x_{ij^*})-h(x,x_{ij^*}))\prod_{\substack{j=1,\\j\neq j^*}}^dh(x_{i^*j},x_{ij})\right.\nonumber\\
-&&\left.+(|x_{i^*j^*}|-|x|)\prod_{\substack{j=1,\\j\neq j^*}}^d[1+|x_{i^*j}|]\right)
-\end{eqnarray} 
-We summarize the coordinate-exchange algorithm in Algorithm 1. 
-\begin{algorithm}[ht]
-\begin{algorithmic}[1]%\label{alg:coorex}
-\caption{Coordinate exchange method}
-\State Set $k=0$.
-\State Compute the row deletion function $d_r(i)$ ($i=1,...,N$) for $N$ rows of $\mX^{(k)}$ and choose the row $i^*$ with the largest row deletion value, i,e, $i^* = \argmax_{i} d_r(i)$. 
-\State Compute the column deletion function $d_c(j)$ ($j=1,...,d$) for $d$ columns of $\mX^{k}$ and choose the column $j^*$ with the largest column deletion value, i.e., $j^* = \argmax_{j} d_c(j)$. 
-\State Solve the univariate nonlinear optimization problem
-$$\max_{x} \Delta(x_{i^*j^*},x),\,\,\,\,\text{s.t.} x\in \mathbb{R},$$
-and denote the optimal solution as $x^*$.
-\If{$\Delta(x_{i^*j^*},x^*)>0$} 
-\State {replace $x_{i^*j^*}$ with $x^*$ and the define the new design as $\mX^{(k+1)}$.}
-\State {$k=k+1$.}
-\Else 
-\State{terminate the algorithm and conclude the current design is optimal.} 
-\EndIf
-\end{algorithmic}
-\end{algorithm}
+The coordinate deletion function defined in \eqref{eq:coorddeletion} can be be expressed as
+\begin{multline}\label{eq:coldeletionA}
+\frakd_c(k) = (c-1)c^{d-1} -\frac{2}{N}\sum_{i=1}^N \frac{h(x_{ik})H(\vx_i)}{1+h(x_{ik})}  \\
++\frac{1}{N^2}\sum_{i,j=1}^N \frac{\tK(x_{ik},x_{jk}) K(\vx_i,\vx_j)}{1+\tK(x_{ik},x_{jk})}  .
+\end{multline}
+The computational cost for $\frakd_c(1), \ldots, \frakd_p(d)$ is also $\Order(dN^2)$, which is the same order as the cost of the discrepancy of a single design.
 
-It's worth pointing out that although the three functions, $d_r, d_c$ and $\Delta$ need to computed in each iteration for multiple times, most evaluations only involve $c(x_{ij})$ and $h(x_{ij},x_{rs})$, $i,r = 1,...,N, j,s=1,...,d$, which only need to be computed once before the design is updated.
-The maximization of $\Delta$ function is a one-dimension unconstrained optimization and can be easily solved by any unconstrained nonlinear optimization methods.
+Finally, the  function $\Delta$ defined in \eqref{eq:deltafun} is given by
+\begin{align}\label{eq:deltafunction}
+\nonumber
+\Delta(x)
+&= -\frac{2\left[  h(x_{i^*k^*})-h(x)    \right]H(\vx_{i^*})}{N[1 + h(x_{i^*k^*})]}   \\
+\nonumber
+& \qquad \qquad +\frac{1}{N^2}\left(2\sum_{i=1}^N  \frac{[\tK(x_{i^*k^*},x_{ik^*})-\tK(x,x_{ik^*})] K(\vx_{i^*},\vx_i)} {1 + \tK(x_{i^*k^*},x_{ik^*})} \right . \\
+& \qquad \qquad \left . - \frac{[\tK(x_{i^*k^*},x_{i^*k^*})-\tK(x,x)] K(\vx_{i^*},\vx_{i^*})} {1 + \tK(x_{i^*k^*},x_{i^*k^*})} \right )
+\end{align} 
+If we drop the terms that are independent of $x$, then we can maximize the function
+\begin{equation}\label{eq:deltapfunction}
+\Delta'(x) = Ah(x)  - \frac{1}{N}\sum_{i=1}^N B_i \tK(x,x_{ik^*}) + C \tK(x,x)
+\end{equation}
+where
+\begin{equation*}
+A = \frac{2H(\vx_{i^*})}{1 + h(x_{i^*k^*})}, \quad
+B_i  = \frac{2K(\vx_{i^*},\vx_i)} {1 + \tK(x_{i^*k^*},x_{ik^*})}, \quad
+C  = \frac{K(\vx_{i^*},\vx_{i^*})} {N[1 + \tK(x_{i^*k^*},x_{i^*k^*})]}.
+\end{equation*}
+Note that $A, B_1, \ldots, B_N, C$ only need to be computed once for each iteration of the coordinate exchange algorithm.
 

### 2019-06-01 InvPts_verB.tex
Updates from Overleaf

@@
 \usepackage{xspace,subfigure}
-\usepackage{amssymb, xcolor,enumerate,float,mathtools,algorithmicx}
+\usepackage{amssymb, xcolor,enumerate,float,mathtools}
 \usepackage{algpseudocode}
@@
 \algnewcommand\INPUT{\item[\algorithmicinput]}
+\algnewcommand\algorithmicoutput{\textbf{Output:}}
+\algnewcommand\OUTPUT{\item[\algorithmicoutput]}
 %\algnewcommand\STATE{\item}
@@
 \end{equation}
-A number of transformation methods for different distributions can be found in \cite{devroye2006nonuniform}. \FJH{How about Prof. Fang's books?}
+A number of transformation methods for different distributions can be found in \cite{devroye2006nonuniform} and Professor Fang's book \cite{FanWan94}.
 
@@
      \nonumber
-      &= \prod_{j=1}^d\left[1+\frac{1}{2}\left(\left|\Phi^{-1}(t_j)-1/2\right|+ \left|\Phi^{-1}(x_j)- 1/2 \right| \right . \right . \\
-      & \qquad \qquad \left.  \left . -\left|\Phi^{-1}(t_j)-\Phi^{-1}(x_j)\right|\right)\right].
+      &= \prod_{j=1}^d\left[1+\frac{1}{2}\left(\left|\Phi(t_j)-1/2\right|+ \left|\Phi(x_j)- 1/2 \right| \right . \right . \\
+      & \qquad \qquad \left.  \left . -\left|\Phi(t_j)-\Phi(x_j)\right|\right)\right].
 \end{align}
-In one dimension, the distance between two Dirac measures defined using the kernel $K_\unif$ above is $\norm{\delta_{x} - \delta_{t}} = \sqrt{x-t}$, whereas the distance defined using the kernel $K$ above is $\norm{\delta_{x} - \delta_{t}} = \sqrt{\Phi^{-1}(x)-\Phi^{-1}(t)}$.
+In one dimension, the distance between two Dirac measures defined using the kernel $K_\unif$ above is $\norm{\delta_{x} - \delta_{t}} = \sqrt{|x-t|}$, whereas the distance defined using the kernel $K$ above is $\norm{\delta_{x} - \delta_{t}} = \sqrt{|\Phi(x)-\Phi(t)|}$.
 Under kernel $K$, the distance between two Dirac measures can never be greater than one.
@@
 Varying the dimension $d$ from $1$ to $10$, we calculate the sample correlation between $D(\vPsi(\Udes),F_\normal, K)$ and $D(\Udes,F_\unif,K_\unif) = D(\Udes',F_\unif',K)$ for $B=500$ IID designs of size $N=50$.
-Figure \ref{fig:UniVsNormDisc} displays the correlation as a function of $d$.
+Figure \ref{fig:DiscVsd} displays the correlation as a function of $d$.
 Although the correlation is positive, it degrades with increasing $d$.
 
+\begin{figure}[ht]
+\begin{center}
+\includegraphics[width=8cm]{code/dimVsdisc.eps}
+\caption{Correlation between Uniform Discrepancy and Normal Discrepancy with Different Variable Dimensions. \label{fig:DiscVsd}}
+\end{center}
+\end{figure}
+
 \FJH{Fred does not understand this example.}
-A simple example of integral approximation below shows that a naively inverse transformed sequence $\Udes$ could result in ridiculous estimate even if $D(\Udes,F_\unif, \tilde{K})$ is small.
+A simple example of integral approximation below shows that a naively inverse transformed sequence $\Udes$ could result in very misleading estimate even if $D(\Udes,F_\unif, K)$ is small.
 
-\emph{Example}: Consider estimating the integral $\int_{\mathbb{R}^d} e^{|x_1|+\cdots+|x_d|}\dif \Phi(\vx)$ using Monte Carlo method, with $d=10$ and $N=200$ points.
+\emph{Example}: Consider estimating the integral
+\begin{align}\label{eq:badexample}
+\int_{\mathbb{R}^d} \frac{x_1+\cdots+x_d}{1+10^(-8)(x_1^2+\cdots+x_d^2)}\dif \Phi(\vx) & = \Ex(e^{|x_1+\cdots+x_d|}),\,\,\,\vx\sim N({\bf 0}, {\mathsf I}_d)
+\end{align}
+using Monte Carlo method, with $d=10$ and $N=2^{10}$ points.
+We start with two uniform random sequences.
+One is a Sobol sequence that has small uniform discrepancy, denoted as $\Udes_1$.
+Then we move the closest point to origin $0^d$ in $\Udes_1$ to $\left(10^{-15}\right)^d$, and denote the new sequence as $\Udes_2$.
+We compare the integral estimate with samples $\vPsi(\Udes_1)$ and $\vPsi(\Udes_2)$.
+Table \ref{tab:badexample} shows that the uniform discrepancies of $\Udes_1$ and $\Udes_2$ don't differ much, but the normal discrepancy of $\vPsi(\Udes_2)$ is far larger than that of $\vPsi(\Udes_1)$.
+What's more, the integral estimate using $\vPsi(\Udes_2)$ explodes while that of $\vPsi(\Udes_1)$ is reasonable.
 
@@
   \centering
-  \caption{Estimate}
-    \begin{tabular}{rcccc}
+  \caption{Comparison of Integral Estimate}
+    \begin{tabular}{ccccc}
     \hline
-   $\Udes$       & $D(\Udes,F_\unif, \tilde{K})$     & $D(\vPsi(\Udes),F_\normal, K)$     & Estimate \\
+   $\Udes$       & $D(\Udes,F_\unif, K)$     & $D(\vPsi(\Udes),F_\normal, K)$     & Estimate \\
     \hline
-    $x$     &   0.1754    &  18.61     & 198.68 \\
-    $y$     &  0.1800      &  286.35     & $1.54\times 10^{32}$ \\
+    $\Udes_1$     &   0.0286    &  18.57     & 251.33 \\
+    $\Udes_2$     &  0.0294      &  58.82     & $3.01\times 10^{31}$ \\
     \hline
     \end{tabular}%
-  \label{tab:addlabel}%
+  \label{tab:badexample}%
 \end{table}%
 
-\FJH{Fred got to here}
 \section{Improvement by the Coordinate-Exchange Method}\label{sec:CoordEx}
@@
 \begin{algorithm}[ht]
-\caption{Coordinate exchange method\label{alg:coorex}}
+\caption{Coordinate Exchange Algorithm.\label{alg:coorex}}
 \begin{algorithmic}[1]
-\INPUT An initial design $\Xdes$ on the domain $\Omega$, a target distribution, $F$, and a kernel, $K$ of the form \eqref{eq:prodkernel}.
-\State Compute the point deletion function $\frakd_p(1), \ldots, \frakd_p(N)$ for the design $\Xdes$, and choose the row $i^*$ with the largest row deletion value, i.e.
-$i^* = \argmax_{i} \frakd_p(i)$.
-\State Compute the coordinate deletion function $\frakd_c(1), \ldots, \frakd_c(d)$ and choose the column $j^*$ with the largest column deletion value, i.e., $k^* = \argmax_{k} \frakd_c(k)$. 
-\State Choose the replacement value for $x_{i^*k^*}$ by solving the univariate nonlinear optimization problem
+\INPUT An initial design $\Xdes$ on the domain $\Omega$, a target distribution, $F$, and a kernel, $K$ of the form \eqref{eq:prodkernel}, a small value $TOL$ to measure convergence of the algorithm, and the maximum allowed number of iterations, $I_{\max}$.
+\OUTPUT Low discrepancy design $\Xdes$. 
+\State Compute the squared discrepancy $D^2_0$ for the initial design $\Xdes$ and set the iteration index $i=0$.
+\For{$i=1,2,\ldots, I_{\max}$}
+\State Compute the point deletion function $\frakd_p(1), \ldots, \frakd_p(N)$. Choose the $i^*$-th point which has the largest point deletion value, i.e. $i^* = \argmax_{i} \frakd_p(i)$. 
+\State For the $i^*$-th point, Compute the coordinate deletion function $\frakd_c(1), \ldots, \frakd_c(d)$ and choose the $j^*$-th element which has the largest coordinate deletion value, i.e., $k^* = \argmax_{k} \frakd_c(k)$.
+\State Replace the coordinate $x_{i^*k^*}$ by $x^*$ which is the solution of the univariate optimization
 \[
-x^* = \argmax_{x \in \Omega_k} \Delta(x).
+x^* = \argmax_{x \in \tOmega} \Delta(x).
 \]
-\If{$\Delta(x^*>0$} 
+\If{$\Delta(x^*)/D^2_{i-1}>TOL$} 
 \State {Replace $x_{i^*k^*}$ with $x^*$ in the design $\Xdes$, i.e., let  $\Xdes(x^*)$ replace the old $\Xdes$.}
+\State Update the squared discrepancy $D^2_{i}=D^2_{i-1}-\Delta(x^*)$. 
 \Else 
-\State{Terminate the algorithm and the design $\Xdes$.} 
+\State{Terminate the loop and return the design $\Xdes$.} 
 \EndIf
+\EndFor
 \end{algorithmic}
@@
 \nonumber
-    D^2(\Xdes,\rho,K)  & = (1+c)^d  - \frac 2N \sum_{i=1}^N H(\vx_{i}) + \frac{1}{N^2}  \sum_{i,j=1}^N K(\vx_{i},x_{j}),
+    D^2(\Xdes,\rho,K)  & = (1+c)^d  - \frac 2N \sum_{i=1}^N H(\vx_{i}) + \frac{1}{N^2}  \sum_{i,j=1}^N K(\vx_{i},\vx_{j}),
     \intertext{where}
-    h(x) & = \int_{\tOmega} \tK_k(t,x)  \, \tvarrho(t) \, \dif t, \\
+    h(x) & = \int_{\tOmega} \tK(t,x)  \, \tvarrho(t) \, \dif t, \\
     c & = \int_{\tOmega \times \tOmega} \tK(t_k,x_k) \, \tvarrho(t) \tvarrho (x) \, \dif t\dif x = \int_{\tOmega} h(x) \, \tvarrho(x) \, \dif x, \\
@@
 \end{align}
-We note that an evaluation of $h(x)$ and $\tK(t,x)$ require $\Order(1)$ operations, while an evaluation of $H(\vx)$ and $K(\vt,\vx)$ require $\Order(d)$ operations.
+An evaluation of $h(x)$ and $\tK(t,x)$ each require $\Order(1)$ operations, while an evaluation of $H(\vx)$ and $K(\vt,\vx)$ each require $\Order(d)$ operations.
 The computation of $D(\Xdes,\rho,K)$ requires $\Order(dN^2)$ operations because of the double sum.
@@
 \nonumber
-& \qquad \qquad +\frac{1}{N^2}\left(2\sum_{i=1}^N  \frac{[\tK(x_{i^*k^*},x_{ik^*})-\tK(x,x_{ik^*})] K(\vx_{i^*},\vx_i)} {1 + \tK(x_{i^*k^*},x_{ik^*})} \right . \\
-& \qquad \qquad \left . - \frac{[\tK(x_{i^*k^*},x_{i^*k^*})-\tK(x,x)] K(\vx_{i^*},\vx_{i^*})} {1 + \tK(x_{i^*k^*},x_{i^*k^*})} \right )
+& \qquad \qquad +\frac{1}{N^2}\left(2\sum_{\substack{i=1 \\ i \ne i^*}}^N  \frac{[\tK(x_{i^*k^*},x_{ik^*})-\tK(x,x_{ik^*})] K(\vx_{i^*},\vx_i)} {1 + \tK(x_{i^*k^*},x_{ik^*})} \right . \\
+& \qquad \qquad \left . + \frac{[\tK(x_{i^*k^*},x_{i^*k^*})-\tK(x,x)] K(\vx_{i^*},\vx_{i^*})} {1 + \tK(x_{i^*k^*},x_{i^*k^*})} \right )
 \end{align} 
@@
 \begin{equation}\label{eq:deltapfunction}
-\Delta'(x) = Ah(x)  - \frac{1}{N}\sum_{i=1}^N B_i \tK(x,x_{ik^*}) + C \tK(x,x)
+\Delta'(x) = Ah(x)  - \frac{1}{N}\sum_{\substack{i=1 \\ i \ne i^*}}^N B_i \tK(x,x_{ik^*}) - C \tK(x,x)
 \end{equation}
@@
 
+\FJH{Fred got to here}
+
 \section{Simulation}
 
-To demonstrate the performance of the $d$-dim standard normal design proposed in Section \ref{sec:CoordEx}, we compare three algorithms: (1) Randn: embedded normal random number generator `randn' from MATLAB;  (2) NG1: inverse transformed Sobol sequence; (3) NG2: improved NG1 with proposed Algorithm 1.
+To demonstrate the performance of the $d$-dim standard normal design proposed in Section \ref{sec:CoordEx}, we compare three algorithms: (1) RAND: inverse transformed uniform random sequence;  (2) SOBOL: inverse transformed Sobol sequence; (3) E-SOBOL: inversed transformed scrambled Sobol sequence with uni-dimensional projection at $\left\{\frac{2i-1}{2N}\right\}_{i=1}^{2N}$; (4) CE: improved E-SOBOL with proposed Algorithm 1.
 We have tried different combinations of dimension and sample size, and let the sample size become larger as the dimension becomes higher. 
 Using each algorithm we generate 500 designs, and for each design, we compute the discrepancy \eqref{eq:DisNormald>1} and compare the distribution of discrepancies from different algorithms as shown in Figure \ref{fig:comparison}.
+
+Figure \ref{fig:SOBOLVsRAND} contains the boxplots of normal discrepancies corresponding to the four generators with $d=2$ and $N=32$.
+It shows that SOBOL, E-SOBOL and CE all outperform RAND by a great margin.
+To better present the comparison between the generators, in the follow figures, we exclude the boxplot from RAND.
+
+\begin{figure}[ht]
+\begin{center}
+\includegraphics[width=8cm]{code/boxplotall_d2n32.eps}
+\caption{Performance Comparison of Generators. \label{fig:SOBOLVsRAND}}
+\end{center}
+\end{figure}
+
 We summarize the observations as follows. 
@@
 \item
-NG1 and NG2 both outperform Randn by a great margin.
+Overall, E-SOBOL and CE outperform SOBOL. 
 \item 
-When the sample is relatively dense, i.e., $N/d$ ratio is large, NG1 and NG2 have similar performance, but the proposed NG2 is slightly better, as it takes the extra step to improve the relative high discrepancy via Algorithm 1.
+When the sample is relatively dense, i.e., $N/d$ ratio is large, E-SOBOL and CE have similar performance. They both outperform SOBOL by a great margin
 \item
-As the sample becomes more sparse, i.e., $N/d$ ratio is smaller, the proposed NG2 becomes much superior to NG1.
+As the sample becomes more sparse, i.e., $N/d$ ratio is smaller, SOBOL and E-SOBOL have similar performance. The proposed CE becomes much superior to both of them.
 \end{enumerate}
-Therefore, the inverse transformation of low-discrepancy uniform designs, such as Sobol sequences is still preferable when the sample size is large relative to the dimension, and we recommend using the proposed remedy approach to further improve the inverse transformed Sobol sequences when the sample size is small or moderate.
+Therefore, E-SOBOL sequences are preferable when the sample size is large relative to the dimension, and we recommend using the proposed remedy approach to further improve E-SOBOL when the sample size is small or moderate.
 
@@
 \centering
-{\subfigure[$d=2,N=30$] {\includegraphics[width=5.5cm]{code/boxplot_d2n30.eps}}}
+{\subfigure[$d=2,N=32$] {\includegraphics[width=5.5cm]{code/boxplot_d2n32.eps}}}
 \quad
-{\subfigure [$d=3, N=50$]
-{\includegraphics[width=5.5cm]{code/boxplot_d3n50.eps}}}
+{\subfigure [$d=3, N=64$]
+{\includegraphics[width=5.5cm]{code/boxplot_d3n64.eps}}}
 \quad
-{\subfigure[$d=4, N=70$] {\includegraphics[width=5.5cm]{code/boxplot_d4n70.eps}}}
+{\subfigure[$d=4, N=64$] {\includegraphics[width=5.5cm]{code/boxplot_d4n64.eps}}}
 \quad
-{\subfigure[$d=5, N=90$] {\includegraphics[width=5.5cm]{code/boxplot_d5n90.eps}}}
+{\subfigure[$d=6, N=128$] {\includegraphics[width=5.5cm]{code/boxplot_d5n128.eps}}}
 \quad
-{\subfigure[$d=6, N=110$] {\includegraphics[width=5.5cm]{code/boxplot_d6n110.eps}}}
+{\subfigure[$d=8, N=256$] {\includegraphics[width=5.5cm]{code/boxplot_d8n256.eps}}}
 \quad
-{\subfigure[$d=7, N=130$] {\includegraphics[width=5.5cm]{code/boxplot_d7n130.eps}}}
-\caption{Performance Comparison of Three Generators}\label{fig:generatorcomp}
+{\subfigure[$d=10, N=512$] {\includegraphics[width=5.5cm]{code/boxplotall_d10n512.eps}}}
+\caption{Performance Comparison of Generators}
+\end{figure}
+
+We also report the average execution time of the four generators in Table \ref{tab:ExeTime}.
+All codes were run on a MacBook Pro with 2.4 GHz Intel Core i5 processor.
+Although CE requires the longest computational time compared to the other three generators, the execution time to achieve one sample is very reasonable.
+CE is quite computationally efficient and practical especially when the dimension is high and only a small sample is affordable.
+
+% Table generated by Excel2LaTeX from sheet 'Sheet1'
+\begin{table}[htbp]
+  \centering
+  \caption{Execution Time of Generators (in seconds)}
+    \begin{tabular}{ccccccc}
+    \hline
+          & $d=2,$   & $d=3,$   & $d=4,$   & $d=6,$   & $d=8,$   & $d=10,$ \\
+  & $N=32$   & $N=64$   & $N=64$   & $N=128$   & $N=256$   & $N =512$ \\
+    \hline
+    RAND  & $3.22\times 10^{-5}$      &  $5.21\times 10^{-5}$     & $5.27\times 10^{-5}$      &  $9.92\times 10^{-5}$     & $2.48\times 10^{-4}$      & $ 5.32\times 10^{-4}$ \\
+    SOBOL & $8.60\times 10^{-4}$      &  $0.10\times 10^{-2}$     &    $0.11\times 10^{-2}$   &  $0.16\times 10^{-2}$     & $0.21\times 10^{-2}$      &  $0.28\times 10^{-2}$\\
+    E-SOBOL & $8.71\times 10^{-4}$  & $0.11\times 10^{-2}$      &     $0.12\times 10^{-2}$  &  $0.16\times 10^{-2}$     &   $0.23\times 10^{-2}$    & $0.32\times 10^{-2}$  \\
+    CE    & $1.34\times 10^{-2}$      & $2.73\times 10^{-2}$      & $6.12\times 10^{-2}$      &   $0.24$    &   $1.04$    & $3.84$  \\
+    \hline
+    \end{tabular}%
+  \label{tab:ExeTime}%
+\end{table}%
+
+To further evaluate the performance of the normal random sequence generated by the four generators, we consider the integral approximation problem in \eqref{eq:badexample} with $d=10$.
+We use the Monte Carlo estimate with the sample generated by SOBOL of size $n = 2^{17}$ as an accurate estimate of the integral, and summarize the integral estimation error according to the four generators with simulation size $N=512$ in Figure \ref{fig:comparison_integral}.
+Not surprisingly, CE outperforms the other three generators and has no explosive relative error.
+It's interesting to see that SOBOL and E-SOBOL may perform even worse than RAND in several cases, and this aligns with our discussion in Section 4: the inverse transformed low uniform discrepancy sequence may not retain low normal discrepancy.
+When the sample size $N$ is small/moderate relative to dimension $d$, using CE would limit the potential danger of very inaccurate estimate caused by a sample with large normal discrepancy.
+
+\begin{figure}[ht]\label{fig:comparison_integral}
+\centering
+{\subfigure[$d=2,N=32$] {\includegraphics[width=5.5cm]{code/errorboxplot_d2n32.eps}}}
+\quad
+{\subfigure [$d=3, N=64$]
+{\includegraphics[width=5.5cm]{code/errorboxplot_d3n64.eps}}}
+\quad
+{\subfigure[$d=4, N=64$] {\includegraphics[width=5.5cm]{code/errorboxplot_d4n64.eps}}}
+\quad
+{\subfigure[$d=6, N=128$] {\includegraphics[width=5.5cm]{code/errorboxplot_d6n128.eps}}}
+\quad
+{\subfigure[$d=8, N=256$] {\includegraphics[width=5.5cm]{code/errorboxplot_d8n256.eps}}}
+\quad
+{\subfigure[$d=10, N=512$] {\includegraphics[width=5.5cm]{code/errorboxplot_d10n512.eps}}}
+\caption{Integral Approximate Performance Comparison of Generators}
 \end{figure}
@@
 
+\FJH{I should write about coordinate weights}
+
 \section*{Appendix}
-Derivation of \eqref{eq:DisNormald=1} and \eqref{eq:DisNormald>1}. 
+Derivation of \eqref{eq:DisNormald>1}. 
 \begin{proof}

### 2019-06-01 code/CE_Normal.m

@@ -2,13 +2,14 @@
 
 function [low_discNormal,normaldisc] = CE_Normal(x)
 
-delta = 0.01;
-maxrun = 50;
+maxrun = 200;
 count = 0;
-opt_delta=-1;
+flag=1;
+delta = 1;
 
-while opt_delta< -1*10^(-10) && count<maxrun
-    [x,opt_delta] = coordinate_exchange(x);
+
+while delta>10^(-15) && count<200
+    [x,delta] = coordinate_exchange(x);
     count = count+1;
     normaldisc = normal_multidiscrepancy(x);
 end

### 2019-06-01 code/bad_example.m

@@ -1,0 +1,49 @@
+function [error_bad, error] = bad_example
+
+N =512;
+d=10;
+
+%generate 2-d uniform random numbers
+p = sobolset(d);
+p = scramble(p,'MatousekAffineOwen');
+x = net(p,N);
+
+%shift the largest point in x to the right a little bit
+y = x;
+changed = zeros(1,d)+10^(-15);
+
+[~,ind] = min(vecnorm(y'));
+y(ind,:) = changed;
+
+disc_x = uniform_multidiscrepancy(x); %discrepancy of y w.r.t. uniforma measure
+disc_x
+normal_x = norminv(x); % the normal points using shifted low discrepancy sequence y
+disc_normalx = normal_multidiscrepancy(normal_x); %discrepancy of inverse transformed y w.r.t. normal measure
+disc_normalx
+
+disc_y = uniform_multidiscrepancy(y); %discrepancy of y w.r.t. uniforma measure
+disc_y
+normal_y = norminv(y); % the normal points using shifted low discrepancy sequence y
+disc_normaly = normal_multidiscrepancy(normal_y); %discrepancy of inverse transformed y w.r.t. normal measure
+disc_normaly
+
+
+% est_invx = mean(exp(abs(sum(normal_x,2))))
+% est_invy = mean(exp(abs(sum(normal_y,2))))
+
+% est_invx = mean((abs(sum(normal_x,2))).^(0.99))
+% est_invy = mean((abs(sum(normal_y,2))).^(0.99))
+% true = 2^(0.99/2)*gamma(199/200)*d^(0.99/2)/sqrt(pi)
+% error_invx = abs(est_invx-true)/true
+% error_invy = abs(est_invy-true)/true
+
+integrand =@(z) 1./(1+1e-8*sum(z.^2,2));
+
+est_invx = mean(integrand(normal_x))
+est_invy = mean(integrand(normal_y))
+
+
+
+
+
+end

### 2019-06-01 code/compare_generator.m

@@ -1,32 +1,42 @@
 %compare proposed generator with 'randn'
 
 function  compare_generator
+close all
+clearvars
 
 repeat = 500;
 disc_opt = zeros(repeat,1);
 disc_randn = zeros(repeat,1);
 disc_low = zeros(repeat,1);
-d=2;
-n=30;
+disc_center = zeros(repeat,1);
+d=4;
+n=2^6;
 
 for i = 1:repeat 
     %generate normal random numbers using inverse distribution transformation
     p = sobolset(d);
     p = scramble(p,'MatousekAffineOwen');
+    %Sobol sequence
     uniform = net(p,n);
     x = norminv(uniform);
     disc_low(i) = normal_multidiscrepancy(x);
+    %Centered points
+    [~, xwh] = sort(uniform); %sort twice
+    [~, xeven] = sort(xwh); %to order the points in each direction
+    xeven = (2*xeven-1)/(2*n); %this gives you evenness in one direction
+    disc_center(i) = normal_multidiscrepancy(norminv(xeven));
+    %C-E optimized sequence
     [low_discNormal,new_normaldisc] = CE_Normal(x);
-    disc_opt(i) = new_normaldisc;   
+    disc_opt(i) = new_normaldisc; 
+    %random normal in Matlab
     rand_sample = randn(n,d);
     disc_randn(i) = normal_multidiscrepancy(rand_sample);
-    repeat_index=repeat_index+1;
 end
 
 %read data
-disc_opt = disc_d7n130(1:500);
-disc_low = disc_d7n130(501:1000);
-disc_randn = disc_d7n130(1001:1500);
+% disc_opt = disc_d7n130(1:500);
+% disc_low = disc_d7n130(501:1000);
+% disc_randn = disc_d7n130(1001:1500);
 
 
 %plot opt Vs randn
@@ -37,22 +47,24 @@ figure
 subplot(2,1,1);
 boxplot(disc,g)
 %title('Discrepancies of Proposed Generator and Randn Generator')
-ylabel('Normal Discrepancy')
+ylabel('$D(\boldmath{\Psi}(\mathcal{U}), F_\textup{normal}, K)$','Interpreter','Latex','FontSize',18)
 a = get(gca,'XTickLabel');
 set(gca,'XTickLabel',a,'FontName','Times','fontsize',21)
[…]

### 2019-06-01 code/coordinate_exchange.m

@@ -1,55 +1,84 @@
-function [x,opt_delta] = coordinate_exchange(x)
+function [x,delta] = coordinate_exchange(x)
 
 N = size(x,1); %number of points
 d = size(x,2); %dimension
 
 temp_x = x';
 
-c = @(a) 1+1/sqrt(2*pi)+1/2*abs(a)-a*(normcdf(a)-1/2)-normpdf(a);
-h = @(a,b) 1+1/2*abs(a)+1/2*abs(b)-1/2*abs(a-b);
+c = sqrt(2/pi);
+h = @(a) 1/sqrt(2*pi)+1/2*abs(a)-a*(normcdf(a)-1/2)-normpdf(a);
+k = @(a,b) 1/2*(abs(a)+abs(b)-abs(a-b));
 
-c_mat = arrayfun(c,x); %function c evaluated all elements of x;
+h_vec = prod((1+arrayfun(h,x)),2); %vector H in the manuscript
 
-%[(h_mat)_1;(h_mat)_2;...;(h_mat)_N], with (h_mat)_i as a Nxd matrix = [h(x_i1,x_11),...,h(x_id,x_1d);....;h(x_i1,x_N1),...,h(x_id,x_Nd)]
-h_mat = zeros(N^2,d); %function h(x_ij,x_rj) for i,r=1,...,N,j=1,...,d.
+%k_tilde: N^2xd matrix, [k(x_1,x_j);k(x_2,x_j);....;k(x_N,x_j)]
+k_tilde = zeros(N^2,d); %matrix k_tilde in the manuscript
 D = zeros(N,N*d); %distance matrix
 
+%tic()
 for i = 1:N
     D(:,((i-1)*d+1): (i*d)) = abs(bsxfun(@minus, x(i,:), x));
 end
 
-h_mat = (reshape((1+1/2*abs(repmat((temp_x(:))',N,1))+ 1/2*abs(repmat(x,1,N))-1/2*abs(D))',d,N*N))';
+k_tilde = (reshape(1/2*(abs(repmat((temp_x(:))',N,1))+abs(repmat(x,1,N))-abs(D))',d,N*N))';
+%toc()
 
-row_deletion = -2*prod(c_mat,2)+(N-1)*(2*sum(reshape(prod(h_mat,2),N,N)',2)-prod((1+abs(x)),2));
+k_mat = reshape(prod(1+k_tilde,2),N,N); %NxN matrix, each row is prod(1+k_tilde) of x_i with other points
+
[…]

### 2019-06-01 code/bad_example.m
another example.

@@ -1,7 +1,7 @@
 function [error_bad, error] = bad_example
 
-N =512;
-d=10;
+N = 512;
+d = 10;
 
 %generate 2-d uniform random numbers
 p = sobolset(d);
@@ -37,13 +37,43 @@ disc_normaly
 % error_invx = abs(est_invx-true)/true
 % error_invy = abs(est_invy-true)/true
 
-integrand =@(z) 1./(1+1e-8*sum(z.^2,2));
+c = 1e-4;
+integrand1 =@(z) sum(z,2)./(1+c^2*sum(z.^2,2)); trueIntegral1 = 0
+integrand2 =@(z) sum(z.^2,2)./(1+c^2*sum(z.^2,2)); 
+trueIntegral23 = ...
+(2*c^3*(-1 + c^2) + exp(1/(2*c^2))*sqrt(2*pi)*erfc(1/(sqrt(2)*c)))/(2*c^5)
+trueIntegral2 = ...
+   2^(-1-d/2) * c^(-2-d) * d * exp(1/(2*c^2)) * WGamma(-d/2, 1/(2*c^2))
 
-est_invx = mean(integrand(normal_x))
-est_invy = mean(integrand(normal_y))
+
+est_invx1 = mean(integrand1(normal_x))
+est_invy1 = mean(integrand1(normal_y))
+est_invx2 = mean(integrand2(normal_x))
+est_invy2 = mean(integrand2(normal_y))
 
 
 
 
 
 end
+
+function y = WGamma(a,x)
+%Wolfram's definition of Gamma(a,x) = gammainc(x,a,'upper')*gamma(a)
+%Since gamma(x,a) only works for a>0 we need to use the 
+a1 = mod(a,1) + 1;
+a2 = a - a1;
+if a2 >= 0
+   y = gammainc(x,a,'upper')*gamma(a);
+else 
+   y = gammainc(x,a1,'upper')*gamma(a1);
+   for aa = a1-1:-1:a
+      y = (y - x.^aa * exp(-x))/aa;
+   end
+end
+
+
+
+end
+
+
+

### 2019-06-02 InvPts_verB.tex

@@
 \usepackage{xspace,subfigure}
+\usepackage{comment}
 \usepackage{amssymb, xcolor,enumerate,float,mathtools}
@@
 \begin{align}\label{eq:badexample}
-\int_{\mathbb{R}^d} \frac{x_1+\cdots+x_d}{1+10^(-8)(x_1^2+\cdots+x_d^2)}\dif \Phi(\vx) & = \Ex(e^{|x_1+\cdots+x_d|}),\,\,\,\vx\sim N({\bf 0}, {\mathsf I}_d)
+\int_{\mathbb{R}^d} \frac{x_1+\cdots+x_d}{1+10^{-8}(x_1^2+\cdots+x_d^2)}\dif \Phi(\vx) & = \Ex\left[\frac{\sum\limits_{i=1}^d x_i}{1+10^{-8}\|\vx\|_2^2}\right],\,\,\,\vx\sim N({\bf 0}, {\mathsf I}_d)
 \end{align}
 using Monte Carlo method, with $d=10$ and $N=2^{10}$ points.
+Analytically, the integral \eqref{eq:badexample} equals 0 since $\frac{x_1+\cdots+x_d}{1+10^{-8}(x_1^2+\cdots+x_d^2)}$ is an odd function in each dimension and the probability density function of standard normal is an even function.
 We start with two uniform random sequences.
@@
 Table \ref{tab:badexample} shows that the uniform discrepancies of $\Udes_1$ and $\Udes_2$ don't differ much, but the normal discrepancy of $\vPsi(\Udes_2)$ is far larger than that of $\vPsi(\Udes_1)$.
-What's more, the integral estimate using $\vPsi(\Udes_2)$ explodes while that of $\vPsi(\Udes_1)$ is reasonable.
+In return, the estimate error corresponding to $\Udes_2$ is about 60 times larger than that corresponding to $\Udes_1$.
 
@@
     \hline
-    $\Udes_1$     &   0.0286    &  18.57     & 251.33 \\
-    $\Udes_2$     &  0.0294      &  58.82     & $3.01\times 10^{31}$ \\
+    $\Udes_1$     &   0.0285    &  18.57     & 0.0011 \\
+    $\Udes_2$     &  0.0292      &  58.82     & -0.0660 \\
     \hline
@@
 
+\begin{comment}
 To further evaluate the performance of the normal random sequence generated by the four generators, we consider the integral approximation problem in \eqref{eq:badexample} with $d=10$.
@@
 \end{figure}
+\end{comment}
 

### 2019-06-02 InvPts_verB.tex
Updates from Overleaf

@@
 
-\FJH{Fred does not understand this example.}
-A simple example of integral approximation below shows that a naively inverse transformed sequence $\Udes$ could result in very misleading estimate even if $D(\Udes,F_\unif, K)$ is small.
+\FJH{Changing example.}
 
-\emph{Example}: Consider estimating the integral
-\begin{align}\label{eq:badexample}
-\int_{\mathbb{R}^d} \frac{x_1+\cdots+x_d}{1+10^{-8}(x_1^2+\cdots+x_d^2)}\dif \Phi(\vx) & = \Ex\left[\frac{\sum\limits_{i=1}^d x_i}{1+10^{-8}\|\vx\|_2^2}\right],\,\,\,\vx\sim N({\bf 0}, {\mathsf I}_d)
-\end{align}
-using Monte Carlo method, with $d=10$ and $N=2^{10}$ points.
-Analytically, the integral \eqref{eq:badexample} equals 0 since $\frac{x_1+\cdots+x_d}{1+10^{-8}(x_1^2+\cdots+x_d^2)}$ is an odd function in each dimension and the probability density function of standard normal is an even function.
-We start with two uniform random sequences.
-One is a Sobol sequence that has small uniform discrepancy, denoted as $\Udes_1$.
-Then we move the closest point to origin $0^d$ in $\Udes_1$ to $\left(10^{-15}\right)^d$, and denote the new sequence as $\Udes_2$.
-We compare the integral estimate with samples $\vPsi(\Udes_1)$ and $\vPsi(\Udes_2)$.
-Table \ref{tab:badexample} shows that the uniform discrepancies of $\Udes_1$ and $\Udes_2$ don't differ much, but the normal discrepancy of $\vPsi(\Udes_2)$ is far larger than that of $\vPsi(\Udes_1)$.
-In return, the estimate error corresponding to $\Udes_2$ is about 60 times larger than that corresponding to $\Udes_1$.
+\begin{example} A simple cubature example illustrates that a naively inverse transformed low discrepancy design, $\Udes$, may yield a large $D(\vPsi(\Udes),F_\normal, K)$ and also a large cubature error.
+Consider the integration problem in \eqref{eq:integration} with
+\begin{subequations} \label{eq:badexample}
+\begin{gather}
+\vX \sim  N(\vzero, {\mathsf I}_d), \qquad f(\vx) = \frac{x_1^2+\cdots+x^2_d}{1+10^{-8}(x_1^2+\cdots+x_d^2)}, \qquad Y = f(\vX),\\
+\mu = \Ex(Y) = \int_{\reals^d} \frac{x_1^2+\cdots+x^2_d}{1+10^{-8}(x_1^2+\cdots+x_d^2)} \phi(\vx) \, \dif \vx
+\end{gather}
+\end{subequations}
+where $\phi$ is the probability density function for the standard multivariate normal distribution.
+Since the integrand above is a function of $x_1^2 + \cdots + x_d^2$, $\mu$ can be written as a one dimensional integral.  For $d=10$, $\mu = 10$ to at least $15$ significant digits using quadrature.
+
+We can also approximate the integral in \eqref{eq:badexample} using a $d=10$, $N=512$ cubature \eqref{eq:cubature}.
+We compare cubatures using two designs.
+The design $\Xdes_1$ is the inverse normal transformation of a scrambled Sobol' sequence, $\Udes_1$, which has low discrepancy with respect to the uniform distribution on the $d$-dimensional unit cube.
+The design $\Udes_2$ takes the point in $\Udes_1$ that is closet to $\vzero$ and moves it to $\left(10^{-15}, \ldots, 10^{-15}\right)$, which is very close to $\vzero$.
+As seen in Table \ref{tab:badexample}, the two uniform designs have quite similar, small discrepancies.
+However, the transformed designs, $\Xdes_j = \vPsi(\Udes_j)$ for $j=1,2$, have much different discrepancies with respect to the normal distribution.
+This is due to the point in $\Xdes_2$ that has large negative coordinates.
+Furthermore, the cubatures, $\hat{\mu}$, based on these two designs have significantly different errors.
+The first design has both a smaller discrepancy and a smaller error than the second.
+This could not have been induced by looking at the discrepancies of the original uniform designs.
 
@@
     \begin{tabular}{ccccc}
-    \hline
-   $\Udes$       & $D(\Udes,F_\unif, K)$     & $D(\vPsi(\Udes),F_\normal, K)$     & Estimate \\
-    \hline
-    $\Udes_1$     &   0.0285    &  18.57     & 0.0011 \\
-    $\Udes_2$     &  0.0292      &  58.82     & -0.0660 \\
-    \hline
+   $\Udes$       & $D(\Udes,F_\unif, K)$     & $D(\vPsi(\Udes),F_\normal, K)$     & $\hat{\mu}$  & Relative Error\\
+    \toprule
+    $\Udes_1$     &   0.0285    &  18.57     & 10.0182 & 0.0018\\
+    $\Udes_2$     &  0.0292      &  58.82     & 11.2238 & 0.1224
     \end{tabular}%
@@
 \end{table}%
+
+% % Table generated by Excel2LaTeX from sheet 'Sheet1'
+% \begin{table}[htbp]
+%   \centering
+%   \caption{Comparison of Integral Estimate}
+%     \begin{tabular}{ccccc}
+%     \hline
+%   $\Udes$       & $D(\Udes,F_\unif, K)$     & $D(\vPsi(\Udes),F_\normal, K)$     & Estimate \\
+%     \hline
+%     $\Udes_1$     &   0.0285    &  18.57     & 0.0011 \\
+%     $\Udes_2$     &  0.0292      &  58.82     & -0.0660 \\
+%     \hline
+%     \end{tabular}%
+%   \label{tab:badexample}%
+% \end{table}%
+
+\end{example}
 

### 2019-06-03 code/bad_example.m
updated one

@@ -1,5 +1,6 @@
 function [error_bad, error] = bad_example
 
+rng(29)
 N = 512;
 d = 10;
 
@@ -40,16 +41,21 @@ disc_normaly
 c = 1e-4;
 integrand1 =@(z) sum(z,2)./(1+c^2*sum(z.^2,2)); trueIntegral1 = 0
 integrand2 =@(z) sum(z.^2,2)./(1+c^2*sum(z.^2,2)); 
-trueIntegral23 = ...
-(2*c^3*(-1 + c^2) + exp(1/(2*c^2))*sqrt(2*pi)*erfc(1/(sqrt(2)*c)))/(2*c^5)
-trueIntegral2 = ...
-   2^(-1-d/2) * c^(-2-d) * d * exp(1/(2*c^2)) * WGamma(-d/2, 1/(2*c^2))
-
+trueIntegral2 = d
 
 est_invx1 = mean(integrand1(normal_x))
 est_invy1 = mean(integrand1(normal_y))
 est_invx2 = mean(integrand2(normal_x))
 est_invy2 = mean(integrand2(normal_y))
+
+
+abs_err_invx1 = abs(trueIntegral1 - est_invx1)
+abs_err_invy1 = abs(trueIntegral1 - est_invy1)
+abs_err_invx2 = abs(trueIntegral2 - est_invx2)
+abs_err_invy2 = abs(trueIntegral2 - est_invy2)
+
+rel_err_invx2 = abs_err_invx2/abs(trueIntegral2)
+rel_err_invy2 = abs_err_invy2/abs(trueIntegral2)
 
 
 

### 2019-06-03 code/bad_example.m
fixed badexample.m

@@ -58,28 +58,9 @@ rel_err_invx2 = abs_err_invx2/abs(trueIntegral2)
 rel_err_invy2 = abs_err_invy2/abs(trueIntegral2)
 
 
-
-
-
-end
-
-function y = WGamma(a,x)
-%Wolfram's definition of Gamma(a,x) = gammainc(x,a,'upper')*gamma(a)
-%Since gamma(x,a) only works for a>0 we need to use the 
-a1 = mod(a,1) + 1;
-a2 = a - a1;
-if a2 >= 0
-   y = gammainc(x,a,'upper')*gamma(a);
-else 
-   y = gammainc(x,a1,'upper')*gamma(a1);
-   for aa = a1-1:-1:a
-      y = (y - x.^aa * exp(-x))/aa;
-   end
 end
 
 
-
-end
 
 
 

### 2019-06-03 code/bad_example.m
fixed true integral

@@ -41,7 +41,8 @@ disc_normaly
 c = 1e-4;
 integrand1 =@(z) sum(z,2)./(1+c^2*sum(z.^2,2)); trueIntegral1 = 0
 integrand2 =@(z) sum(z.^2,2)./(1+c^2*sum(z.^2,2)); 
-trueIntegral2 = d
+trueIntegral2 = (2*pi^(d/2) / gamma(d/2)) * (2*pi)^(-d/2) ...
+   * integral(@(r) (r.^2./(1 + c.^2 * r.^2)) .* exp(-r.^2/2) .* r.^(d - 1), 0, Inf)
 
 est_invx1 = mean(integrand1(normal_x))
 est_invy1 = mean(integrand1(normal_y))

### 2019-06-03 InvPts_verB.tex
revising

@@
 
-\abstract{Write me later}
+\abstract{\FJH{Lulu or Yiou, please draft me.}}
 
@@
 
-Professor Kai-Tai Fang and his collaborators have demonstrated the effectiveness of low discrepancy points as space filling designs \cite{FanWan94, FanLiSud06, FangHic07a}.  
-They promoted discrepancy as a quality measure for statistical experimental designs to the statistics, science, and engineering communities \cite{FanMaWin02, FanMuk00, FanMa01a, FanMa01b}.
+Professor Kai-Tai Fang and his collaborators have demonstrated the effectiveness of low discrepancy points as space filling designs \cite{FangHic07a, FangEtal19a, FanLiSud06, FanWan94}.  
+They have promoted discrepancy as a quality measure for statistical experimental designs to the statistics, science, and engineering communities \cite{FanMa01b, FanMaWin02, FanMuk00, FanMa01a}.
 
 Low discrepancy designs, $\Udes = \{\vu_i\}_{i=1}^N$, are typically constructed so that their empirical distribution, $F_\Udes$, approximates $F_\unif$, the uniform distribution on the unit cube, \cube.
-The discrepancy measures how large $F_\unif-F_\Udes$ is.
+The discrepancy measures the magnitude of $F_\unif-F_\Udes$.
 
@@
 \end{equation}
-A number of transformation methods for different distributions can be found in \cite{devroye2006nonuniform} and Professor Fang's book \cite{FanWan94}.
+A number of transformation methods for different distributions can be found in \cite{devroye2006nonuniform} and  \cite[Chap.\ 1]{FanWan94}.
 
@@
 In other words, 
-\begin{equation} \label{BigQ} \tag{Q}
+\begin{equation} \label{eq:BigQ} \tag{Q}
 \text{\emph{does small $F_\unif - F_\Udes$ imply small $\Ftar - F_\Xdes$?}}
 \end{equation}
-We demonstrate that the answer may be yes or no, depending on how the question is posed.  
+We demonstrate that the answer may be yes or no, depending on how the question is understood.  
 We discuss both cases.  
@@
 
-In the rest of this chapter, we first explain the discrepancy that measures how large $\Ftar - F_\Xdes$ is and motivate it from three different perspectives.
-Next, we show how the inverse transformation can lead to does not always preserve the low discrepancy of a design.
-We also propose a remedy method to improve the design in terms of the discrepancy between $\Ftar$ and $F_\Xdes$. 
-Numerical examples are used to show the performance of the method.
+In the next section of this chapter, we first explain the discrepancy that measures how large $\Ftar - F_\Xdes$ is and motivate it from three different perspectives.
+In Section \ref{sec:WhenYes} we give simple condition under which the answer to \eqref{eq:BigQ} is yes.
+But, if Section \ref{sec:DoTransformedPts} we show that under give a more practical condition the answer to \eqref{eq:BigQ} is no.
+An example illustrates what can go wrong.
+Section \ref{sec:CoordEx} provides a coordinate exchange algorithm that improves the discrepancy of an initial candidate design.
+Simulation results illustrate the value of this algorithm.
+We conclude with a brief discussion.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Discrepancy}
+\section{The Discrepancy} \label{sec:discrepancy}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 If $\nu$ is a probability measure, the associated probability distribution is given by $F(\vx) = \nu((-\vinfty,\vx])$.
-The Dirac measure, $\delta_{\vx}$ is the probability measure assigning unit measure to the point $\vx$.
-A design, $\Xdes = \{\vx_i\}_{i=1}^N$, is a finite set of points that has an associated empirical distribution, $F_{\Xdes}  = N^{-1} \sum_{i=1}^N \bbone_{(-\vinfty,\vx_i]}$ as well as an associated empirical measure, $\nu_{\Xdes}  = N^{-1} \sum_{i=1}^N \delta_{\vx_i}$.
+The Dirac measure, $\delta_{\vx}$ is the probability measure that assigns unit measure to the set $\{\vx\}$ and zero measure to sets not containing $\vx$.
+A design, $\Xdes = \{\vx_i\}_{i=1}^N$, is a finite set of points that has an associated empirical distribution, $F_{\Xdes}  = N^{-1} \sum_{i=1}^N \bbone_{(-\vinfty,\vx_i]}$, as well as an associated empirical measure, $\nu_{\Xdes}  = N^{-1} \sum_{i=1}^N \delta_{\vx_i}$.
 
@@
 In the remainder of this section we provide three interpretations of the discrepancy, summarized in Table \ref{tab:ThreeInterpTable}.
-These results are derived previously in various places, including \cite{Hic99a}.
-One interpretation is the norm of $\nu - \nu_{\Xdes}$.
+These results are presented in various places, including \cite{Hic99a,Hic17a}.
+One interpretation of discrepancy is the norm of $\nu - \nu_{\Xdes}$.
 The second and third interpretations consider the problem of evaluating the mean of a random variable $Y=f(\vX)$, or equivalently a multidimensional integral
@@
 where $\vX$ is a random vector with density $\varrho$. The second
-interpretation is worst-case cubature error for integrands, $f$, in the unit ball of a Hilbert space.
-The third interpretation is the root mean squared cubature error for integrands, $f$ which are realizations of a stochastic processes.
+interpretation of the discrepancy is worst-case cubature error for integrands, $f$, in the unit ball of a Hilbert space.
+The third interpretation is the root mean squared cubature error for integrands, $f$, which are realizations of a stochastic processes.
 
@@
 Assume that $\cm$ includes all Dirac measures.
-Define the function $K:\Omega \times \Omega \to \reals$ in terms of inner products of Dirac measures:
+Define the kernel function $K:\Omega \times \Omega \to \reals$ in terms of inner products of Dirac measures:
 \begin{equation} \label{kerDeltaDef}
@@
 
-The formulas for the discrepancy in \eqref{eq:discDef} depend inherently on the choice of $K$.  That is key to answering our question \eqref{BigQ}.  An often used kernel is 
+Typically the computational cost of evaluating $K(\vt,\vx)$ for any $(\vt,\vx) \in \Omega^2$ is $\Order(d)$, where $t$ is a $d$-vector.
+Thus, assuming that the integrals above can be evaluated at a cost of $\Order(d)$, the computational cost of evaluating $D(\Xdes,\nu,K)$ is $\Order(dN^2)$.
+
+The formulas for the discrepancy in \eqref{eq:discDef} depend inherently on the choice of the kernel $K$.  That choice is key to answering our question \eqref{eq:BigQ}.  An often used kernel is 
 \begin{equation} \label{eq:OrigKernel}
@@
 
-The discrepancy for the uniform distribution on the unit cube defined in terms of the above kernel is commonly called the $L^2$ discrepancy and is expressed as
+The discrepancy for the uniform distribution on the unit cube defined in terms of the above kernel is expressed as
 \begin{align} 
@@
      - \frac 2N \sum_{i=1}^N \prod_{j=1}^d \left[1 + u_{ij} - \frac{u_{ij}^2}{2} \right] \\
-     & \qquad \qquad + \frac 1{N^2} \sum_{i,k=1}^N \prod_{j=1}^d \left[1+ \min(u_{ij},u_{ik})\right]
+     & \qquad \qquad + \frac 1{N^2} \sum_{i,k=1}^N \prod_{j=1}^d \left[1+ \min(u_{ij},u_{ik})\right].
 \end{align}
@@
 \end{equation}
-The quality of this approximation to the integral, or cubature, depends in part on how well the empirical distribution of the design, $\Xdes = \{\vx_i\}_{i=1}^N$, matches the target distribution $F$ associated with the density function $\varrho$.
+The quality of this approximation to the integral, i.e., this cubature, depends in part on how well the empirical distribution of the design, $\Xdes = \{\vx_i\}_{i=1}^N$, matches the target distribution $F$ associated with the density function $\varrho$.
 
@@
 \begin{align*}
-\norm[\ch]{\xi}^2& =\ip[\ch]{\xi}{\xi}=\err(\xi,\Xdes) \quad \text{since $\err(\cdot,\Xdes)$ represents the error functional}\\
+\norm[\ch]{\xi}^2& =\ip[\ch]{\xi}{\xi}=\err(\xi,\Xdes) \quad \text{since $\xi$ represents the error functional}\\
 & = \err(\err(K(\cdot,\cdot \cdot),\Xdes),\Xdes) \quad \text{since } \xi(\vx)=\err(K(\cdot,\vx),\Xdes)\\
@@
 \]
-It is straightforward to see that the kernel function is symmetric and positive definite.
+It is straightforward to show that the kernel function is symmetric and positive definite.
 
@@
 \section{When Transformed Low Discrepancy Points Also Have Low Discrepancy}
+\label{sec:WhenYes}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Having motivated the definition of discrepancy in \eqref{eq:discDef} from three perspectives, we now turn our attention to the question posed in \eqref{BigQ}, namely, does a transformation of low discrepancy points with respect to the uniform distribution yield low discrepancy points with respect to the new target distribution.
+Having motivated the definition of discrepancy in \eqref{eq:discDef} from three perspectives, we now turn our attention to question \eqref{eq:BigQ}, namely, does a transformation of low discrepancy points with respect to the uniform distribution yield low discrepancy points with respect to the new target distribution.
 In this section, we show a positive result, yet recognize some qualifications.
@@
 \begin{equation} \label{eq:BigQYesa}
-    K(\vt,\vx) = K_{\unif}(\vPsi^{-1}(\vt),\vPsi^{-1}(\vx))
+    K(\vt,\vx) = K_{\unif}(\vPsi^{-1}(\vt),\vPsi^{-1}(\vx)),
 \end{equation}
@@
 \begin{equation} \label{eq:BigQYesb}
-    \varrho(\vx) = \abs{\frac{\partial \vPsi^{-1}(\vx)}{\partial \vx}}
+    \varrho(\vx) = \abs{\frac{\partial \vPsi^{-1}(\vx)}{\partial \vx}}.
 \end{equation}
@@
 That is,
-\begin{equation}
-     D(\Xdes,F,K) = D(\Udes,F_{\unif},K_\unif)
-\end{equation}
-As a consequence, under conditions \eqref{eq:BigQYes}, question \eqref{BigQ} has a positive answer.
+\begin{equation*}
+     D(\Xdes,F,K) = D(\Udes,F_{\unif},K_\unif).
+\end{equation*}
+As a consequence, under conditions \eqref{eq:BigQYes}, question \eqref{eq:BigQ} has a positive answer.
 \end{theorem}
 
-Condition \eqref{eq:BigQYesb} may be easy to satisfy.
+Condition \eqref{eq:BigQYesb} may be easily satisfied.
 For example, it is automatically satisfied by the inverse cumulative distribution transform \eqref{eq:inverse}.
 Condition \eqref{eq:BigQYesa} is simply a matter of definition of the kernel, $K$, but it is definition with consequences.
-From the perspective of Section \ref{sec:HilbertMeasures}, changing the kernel means changing the definition of the distance between two Dirac measures.
-From the perspective of Section \ref{sec:DetermBound}, changing the kernel means changing the definition of the Hilbert space of integrands, $f$, in \eqref{eq:integration}.
-From the perspective of Section \ref{sec:RandomBound}, changing the kernel means changing the definition of the covariance kernel for the integrands, $f$, in \eqref{eq:integration}.
+From the perspective of Section \ref{sec:HilbertMeasures}, changing the kernel from $K_\unif$ to $K$ means changing the definition of the distance between two Dirac measures.
+From the perspective of Section \ref{sec:DetermBound}, changing the kernel from $K_\unif$ to $K$ means changing the definition of the Hilbert space of integrands, $f$, in \eqref{eq:integration}.
+From the perspective of Section \ref{sec:RandomBound}, changing the kernel from $K_\unif$ to $K$ means changing the definition of the covariance kernel for the integrands, $f$, in \eqref{eq:integration}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Do Transformed Low Discrepancy Points Have Low Discrepancy More Generally}
+\section{Do Transformed Low Discrepancy Points Have Low Discrepancy More Generally} \label{sec:DoTransformedPts}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-From the discussion above indicates that condition \eqref{eq:BigQYesa} can be too restrictive.
+The discussion above indicates that condition \eqref{eq:BigQYesa} can be too restrictive.
 We would like to compare the discrepancies of designs under kernels that do not satisfy that restriction.
@@
 where $K$ is the kernel defined above in \eqref{eq:OrigKernel}.
-Recall that the origin is a special point in the definition of the inner product corresponding to this $K$ as a reproducing kernel in \eqref{eq:inner}.
 
-Therefore, this $K$ from \eqref{eq:OrigKernel} is an appropriate kernel to use to define the the discrepancy for designs defined with respect to the standard normal distribution, which is also centered at the origin.
+Recall that the origin is a special point in the definition of the inner product for the Hilbert space with $K$ as its reproducing kernel in \eqref{eq:inner}.
+Therefore, this $K$ from \eqref{eq:OrigKernel} is appropriate for defining the discrepancy for target distributions centered at the origin, such as the standard normal distribution, $F_\normal$.
 Such a discrepancy is
@@
 
-%\section{Inconsistency in Discrepancy}\label{sec:inconsistency}
-Now we numerically compare the discrepancy of a uniform design, $\Udes'$ given by \eqref{eq:Updef} and the discrepancy of a design constructed by the inverse normal transformation, i.e.,  $\Xdes = \vPsi(\Udes)$ for $\vPsi$ in \eqref{eq:invNormTrans}, where the $\Udes$ leading to both is identical.
+We numerically compare the discrepancy of a uniform design, $\Udes'$ given by \eqref{eq:Updef} and the discrepancy of a design constructed by the inverse normal transformation, i.e.,  $\Xdes = \vPsi(\Udes)$ for $\vPsi$ in \eqref{eq:invNormTrans}, where the $\Udes$ leading to both $\Udes'$ and $\Xdes$ is identical.
 We do not expect the magnitudes of the discrepancies to be the same, but we ask
 \begin{multline} \tag{Q'} \label{eq:BigQPrime}
-    \text{does } D(\Udes'_1,F'_\unif, K)\leq D(\Udes_2',F_\unif', K) \\
+    \text{Does } D(\Udes'_1,F'_\unif, K)\leq D(\Udes_2',F_\unif', K) \\
     \text{imply }
@@
 
-\FJH{Changing example.}
-
 \begin{example} A simple cubature example illustrates that a naively inverse transformed low discrepancy design, $\Udes$, may yield a large $D(\vPsi(\Udes),F_\normal, K)$ and also a large cubature error.
@@
 \vX \sim  N(\vzero, {\mathsf I}_d), \qquad f(\vx) = \frac{x_1^2+\cdots+x^2_d}{1+10^{-8}(x_1^2+\cdots+x_d^2)}, \qquad Y = f(\vX),\\
-\mu = \Ex(Y) = \int_{\reals^d} \frac{x_1^2+\cdots+x^2_d}{1+10^{-8}(x_1^2+\cdots+x_d^2)} \phi(\vx) \, \dif \vx
+\label{eq:badexampleb}
+\mu = \Ex(Y) = \int_{\reals^d} \frac{x_1^2+\cdots+x^2_d}{1+10^{-8}(x_1^2+\cdots+x_d^2)} \phi(\vx) \, \dif \vx,
 \end{gather}
@@
 where $\phi$ is the probability density function for the standard multivariate normal distribution.
-Since the integrand above is a function of $x_1^2 + \cdots + x_d^2$, $\mu$ can be written as a one dimensional integral.  For $d=10$, $\mu = 10$ to at least $15$ significant digits using quadrature.
+The function $f:\reals^d \to \reals$ is constructed to asymptote to a constant as $\norm[2]{\vx}$ tends to infinity to ensure that $f$ lies inside the Hilbert space corresponding to the kernel $K$ defined in \eqref{eq:OrigKernel}.
+Since the integrand in \eqref{eq:badexampleb} is a function of $\norm[2]{\vx}$, $\mu$ can be written as a one dimensional integral.
+For $d=10$, $\mu = 10$ to at least $15$ significant digits using quadrature.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Improvement by the Coordinate-Exchange Method}\label{sec:CoordEx}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\section{Simulation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Simulation} \label{sec:Simulation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 Not surprisingly, CE outperforms the other three generators and has no explosive relative error.
-It's interesting to see that SOBOL and E-SOBOL may perform even worse than RAND in several cases, and this aligns with our discussion in Section 4: the inverse transformed low uniform discrepancy sequence may not retain low normal discrepancy.
+It's interesting to observe that SOBOL and E-SOBOL may perform even worse than RAND in several cases, and this aligns with our discussion in Section 4: the inverse transformed low uniform discrepancy sequence may not retain low normal discrepancy.
 When the sample size $N$ is small/moderate relative to dimension $d$, using CE would limit the potential danger of very inaccurate estimate caused by a sample with large normal discrepancy.
@@
 
-\section{Discussion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion} \label{sec:discussion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 In this chapter, we summarize the three interpretations of the discrepancy. 
@@
 
+\FJH{Lulu, could you please make the references consistent, i.e., all initials and not first names.  Also please use AMS standard abbreviations for the journals.}
 \bibliographystyle{amsplain}

### 2019-06-14 InvPts_verB.tex
Updates from Overleaf

@@
                             % not available on your system
-%
+
 \usepackage{makeidx}         % allows index generation
@@
 \usepackage{algorithm, algorithmicx}
-\usepackage[numbers]{natbib}
 \usepackage{enumerate,multirow,booktabs}
 \usepackage{url}
-\usepackage{natbib}
-\usepackage{showlabels}
+%\usepackage{showlabels}
+\usepackage{amsrefs}
 
@@
 \newcommand{\Order}{\mathcal{O}}
+\newcommand{\TOL}{\text{TOL}}
+\newcommand{\vT}{\boldsymbol{T}}
+\newcommand{\vone}{\boldsymbol{1}}
+\newcommand{\vgamma}{\boldsymbol{\gamma}}
 
@@
 
-\title*{Are Transformed Low Discrepancy Points Also Low Discrepancy?}
+\title*{Is a Transformed Low Discrepancy Design Also Low Discrepancy?}
 % Use \titlerunning{Short Title} for an abbreviated version of
 % your contribution title if the original one is too long
-\author{Yiou Li, Lulu Kang, and Fred Hickernell}
+\author{Yiou Li, Lulu Kang, and Fred J. Hickernell}
 % Use \authorrunning{Short Title} for an abbreviated version of
@@
 \institute{Yiou Li \at DePaul University, 2320 N. Kenmore Avenue, Chicago, IL 60614 \email{yli139@depaul.edu}
-\and Lulu Kang \at Illinois Institute of Technology, 10 W 32nd Street, Chicago, IL 60616 \email{lkang2@iit.edu} 
+\and Lulu Kang \at Illinois Institute of Technology, 10 W. 32nd Street, Chicago, IL 60616 \email{lkang2@iit.edu} 
 \and 
-Fred Hickernell \at Illinois Institute of Technology, 10 W 32nd Street, Chicago, IL 60616 \email{hickernell@iit.edu}}
+Fred J. Hickernell \at Illinois Institute of Technology, 10 W. 32nd Street, Chicago, IL 60616 \email{hickernell@iit.edu}}
 %
@@
 
-\abstract{\FJH{Lulu or Yiou, please draft me.}}
+\abstract{Experimental designs intended to match arbitrary target distributions are typically constructed via a variable transformation of a uniform experimental design.
+The inverse distribution function is one such transformation. The discrepancy is a measure of how well the empirical distribution of any design matches its target distribution.
+This chapter addresses the question of whether a variable transformation of a low discrepancy uniform design yields a low discrepancy design for the desired target distribution.
+The answer depends on the two kernel functions used to define the respective discrepancies.
+If these kernels satisfy certain conditions, then the answer is yes.
+However, these conditions may be undesirable for practical reasons.
+In such a case, the transformation of a low discrepancy uniform design may yield a design with a large discrepancy.
+We illustrate how this may occur.
+We also suggest some remedies.
+One remedy is to ensure that the original uniform design has optimal one-dimensional projection.
+Another remedy is to use the transformed design as the input to a coordinate-exchange algorithm that optimizes the desired discrepancy.
+The effectiveness of these two remedies is illustrated via simulation.}
 
@@
 
-Professor Kai-Tai Fang and his collaborators have demonstrated the effectiveness of low discrepancy points as space filling designs \cite{FangHic07a, FangEtal19a, FanLiSud06, FanWan94}.  
-They have promoted discrepancy as a quality measure for statistical experimental designs to the statistics, science, and engineering communities \cite{FanMa01b, FanMaWin02, FanMuk00, FanMa01a}.
+Professor Kai-Tai Fang and his collaborators have demonstrated the effectiveness of low discrepancy points as space filling designs \cites{FangHic07a, FangEtal19a, FanLiSud06, FanWan94}. 
+They have promoted discrepancy as a quality measure for statistical experimental designs to the statistics, science, and engineering communities \cites{FanMa01b, FanMaWin02, FanMuk00, FanMa01a}.
 
-Low discrepancy designs, $\Udes = \{\vu_i\}_{i=1}^N$, are typically constructed so that their empirical distribution, $F_\Udes$, approximates $F_\unif$, the uniform distribution on the unit cube, \cube.
+Low discrepancy designs, $\Udes = \{\vu_i\}_{i=1}^N$, are typically constructed so that their empirical distributions, $F_\Udes$, approximate $F_\unif$, the uniform distribution on the unit cube, \cube.
 The discrepancy measures the magnitude of $F_\unif-F_\Udes$. 
+The uniform design a commonly used space filling design for computer experiments \cite{FanLiSud06} and can be constructed using  JMP\textsuperscript{\textregistered} \cite{sall2012jmp}.
 
-When the target distribution for the design, $\Ftar$, defined over the experimental domain $\Omega$, is \emph{not} the uniform distribution on the unit cube, then one typically constructs the desired design, $\Xdes$, by transforming a low discrepancy uniform design, i.e.,
+When the target probability distribution for the design, $\Ftar$, defined over the experimental domain $\Omega$, is \emph{not} the uniform distribution on the unit cube, then the desired design, $\Xdes$, is typically constructed by transforming a low discrepancy uniform design, i.e.,
 \begin{equation} \label{eq:transPts}
@@
 Note that $\Ftar$ may differ from $F_\unif$ because $\Omega \ne \cube$ and/or $\Ftar$ is non-uniform.  
-A natural transformation, $\vPsi(\vu)=[\Psi_1(u_1),\ldots,\Psi_d(u_d)]$, when $\Ftar$ has independent marginals, is the inverse distribution transformation:
+A natural transformation, $\vPsi(\vu)=\bigl(\Psi_1(u_1),\ldots,\Psi_d(u_d) \bigr)$, when $\Ftar$ has independent marginals, is the inverse distribution transformation:
 \begin{equation}\label{eq:inverse}
@@
 \end{equation}
-A number of transformation methods for different distributions can be found in \cite{devroye2006nonuniform} and  \cite[Chap.\ 1]{FanWan94}.
+A number of transformation methods for different distributions can be found in \cite{DEVROYE200683} and \cite{FanWan94}*{Chapter 1}.
 
-The question addressed in this chapter is whether the design $\Xdes$ resulting from transformation \eqref{eq:transPts} of a low discrepancy design, $\Udes$, is itself low discrepancy with respect to the target distribution $\Ftar$.
+This chapter addresses the question of whether the design $\Xdes$ resulting from transformation \eqref{eq:transPts} of a low discrepancy design, $\Udes$, is itself low discrepancy with respect to the target distribution $\Ftar$.
 In other words, 
@@
 \end{equation}
-We demonstrate that the answer may be yes or no, depending on how the question is understood.  
+We show that the answer may be yes or no, depending on how the question is understood.  
 We discuss both cases.  
-For illustrative purposes, we consider the case where $\Ftar$ is the multivariate standard normal distribution.
+For illustrative purposes, we consider the situation where $\Ftar$ is the standard multivariate normal distribution, $F_\normal$.
 
-In the next section of this chapter, we first explain the discrepancy that measures how large $\Ftar - F_\Xdes$ is and motivate it from three different perspectives.
-In Section \ref{sec:WhenYes} we give simple condition under which the answer to \eqref{eq:BigQ} is yes.
-But, if Section \ref{sec:DoTransformedPts} we show that under give a more practical condition the answer to \eqref{eq:BigQ} is no.
+In the next section, we define the discrepancy and motivate it from three perspectives.
+In Section \ref{sec:WhenYes} we give a simple condition under which the answer to \eqref{eq:BigQ} is yes.
+But, in Section \ref{sec:DoTransformedPts} we show that under more practical assumptions the answer to \eqref{eq:BigQ} is no.
 An example illustrates what can go wrong.
-Section \ref{sec:CoordEx} provides a coordinate exchange algorithm that improves the discrepancy of an initial candidate design.
-Simulation results illustrate the value of this algorithm.
+Section \ref{sec:CoordEx} provides a coordinate exchange algorithm that improves the discrepancy of a candidate design.
+Simulation results illustrate the performance of this algorithm.
 We conclude with a brief discussion.
@@
 It is convenient to also work with measures, $\nu$, defined on $\Omega$.
-If $\nu$ is a probability measure, the associated probability distribution is given by $F(\vx) = \nu((-\vinfty,\vx])$.
-The Dirac measure, $\delta_{\vx}$ is the probability measure that assigns unit measure to the set $\{\vx\}$ and zero measure to sets not containing $\vx$.
-A design, $\Xdes = \{\vx_i\}_{i=1}^N$, is a finite set of points that has an associated empirical distribution, $F_{\Xdes}  = N^{-1} \sum_{i=1}^N \bbone_{(-\vinfty,\vx_i]}$, as well as an associated empirical measure, $\nu_{\Xdes}  = N^{-1} \sum_{i=1}^N \delta_{\vx_i}$.
+If $\nu$ is a probability measure, then the associated probability distribution is given by $F(\vx) = \nu((-\vinfty,\vx])$.
+The Dirac measure, $\delta_{\vx}$ assigns unit measure to the set $\{\vx\}$ and zero measure to sets not containing $\vx$.
+A design, $\Xdes = \{\vx_i\}_{i=1}^N$, is a finite set of points with empirical distribution $F_{\Xdes}  = N^{-1} \sum_{i=1}^N \bbone_{(-\vinfty,\vx_i]}$ and empirical measure $\nu_{\Xdes}  = N^{-1} \sum_{i=1}^N \delta_{\vx_i}$.
 
@@
 
-In the remainder of this section we provide three interpretations of the discrepancy, summarized in Table \ref{tab:ThreeInterpTable}.
-These results are presented in various places, including \cite{Hic99a,Hic17a}.
-One interpretation of discrepancy is the norm of $\nu - \nu_{\Xdes}$.
-The second and third interpretations consider the problem of evaluating the mean of a random variable $Y=f(\vX)$, or equivalently a multidimensional integral
-\begin{equation}\label{eq:integration}
-\mu = \Ex(Y) = \Ex[f(\vX)] = \int_{\Omega} f(\vx) \, \varrho(\vx) \, \dif \vx,
-\end{equation}
-where $\vX$ is a random vector with density $\varrho$. The second
-interpretation of the discrepancy is worst-case cubature error for integrands, $f$, in the unit ball of a Hilbert space.
-The third interpretation is the root mean squared cubature error for integrands, $f$, which are realizations of a stochastic processes.
-
 \begin{table}
 \centering
-\caption{Three interpretations of the discrepancy}
+\caption{Three interpretations of the discrepancy.}
 \vspace{-3ex}
@@
 \end{table}
+
+In the remainder of this section we provide three interpretations of the discrepancy, summarized in Table \ref{tab:ThreeInterpTable}.
+These results are presented in various places, including \cites{Hic99a,Hic17a}.
+One interpretation of discrepancy is the norm of $\nu - \nu_{\Xdes}$.
+The second and third interpretations consider the problem of evaluating the mean of a random variable $Y=f(\vX)$, or equivalently a multidimensional integral
+\begin{equation}\label{eq:integration}
+\mu = \Ex(Y) = \Ex[f(\vX)] = \int_{\Omega} f(\vx) \, \varrho(\vx) \, \dif \vx,
+\end{equation}
+where $\vX$ is a random vector with density $\varrho$. The second
+interpretation of the discrepancy is worst-case cubature error for integrands, $f$, in the unit ball of a Hilbert space.
+The third interpretation is the root mean squared cubature error for integrands, $f$, which are realizations of a stochastic processes.
 
@@
 
-Typically the computational cost of evaluating $K(\vt,\vx)$ for any $(\vt,\vx) \in \Omega^2$ is $\Order(d)$, where $t$ is a $d$-vector.
-Thus, assuming that the integrals above can be evaluated at a cost of $\Order(d)$, the computational cost of evaluating $D(\Xdes,\nu,K)$ is $\Order(dN^2)$.
+Typically the computational cost of evaluating $K(\vt,\vx)$ for any $(\vt,\vx) \in \Omega^2$ is $\Order(d)$, where $\vt$ is a $d$-vector.
+Assuming that the integrals above can be evaluated at a cost of $\Order(d)$, the computational cost of evaluating $D(\Xdes,\nu,K)$ is $\Order(dN^2)$.
 
-The formulas for the discrepancy in \eqref{eq:discDef} depend inherently on the choice of the kernel $K$.  That choice is key to answering our question \eqref{eq:BigQ}.  An often used kernel is 
+The formulas for the discrepancy in \eqref{eq:discDef} depend inherently on the choice of the kernel $K$.  That choice is key to answering question \eqref{eq:BigQ}.  An often used kernel is 
 \begin{equation} \label{eq:OrigKernel}
@@
 \end{equation}
-This kernel is plotted in Figure \ref{fig:kernelpict} for $d=1$.  Note that for this kernel in one dimension the distance between two Dirac measures by \eqref{distDelta} is 
+This kernel is plotted in Figure \ref{fig:kernelpict} for $d=1$. The distance between two Dirac measures by \eqref{distDelta} for this kernel in one dimension is 
 \begin{equation*}
@@
 
-The integral $\mu = \int_{\Omega} f(\vx) \, \varrho(\vx) \, \dif \vx$, which was identified as $\Ex[f(\vX)]$ in \eqref{eq:integration}, can be approximated by a sample mean, 
+The integral $\mu = \int_{\Omega} f(\vx) \, \varrho(\vx) \, \dif \vx$, which was identified as $\Ex[f(\vX)]$ in \eqref{eq:integration}, can be approximated by a sample mean:
 \begin{equation}\label{eq:cubature}
@@
 \end{align}
-Under modest assumptions on the reproducing kernel,  $\err(\cdot, \Xdes)$ is a bounded, linear functional, so. 
-by the Riesz representation theorem, there exists a unique representer, $\xi \in \ch$, such that 
+Under modest assumptions on the reproducing kernel,  $\err(\cdot, \Xdes)$ is a bounded, linear functional. 
+By the Riesz representation theorem, there exists a unique representer, $\xi \in \ch$, such that 
 \[
-\err(f, \Xdes)=\ip[\ch]{f}{\xi}, \quad \forall f\in \ch.
+\err(f, \Xdes)=\ip[\ch]{\xi}{f}, \quad \forall f\in \ch.
 \]
-The reproducing kernel allows us to write down an explicit formula for that representer, namely, $\xi(\vx)=\ip[\ch]{K(\cdot,\vx)}{\xi}=\err(K(\cdot,\vx),\Xdes)$.
+The reproducing kernel allows us to write down an explicit formula for that representer, namely, $\xi(\vx)=\ip[\ch]{K(\cdot,\vx)}{\xi}=\ip[\ch]{\xi}{K(\cdot,\vx)}=\err(K(\cdot,\vx),\Xdes)$.
 By the Cauchy-Schwarz inequality, there is a tight bound on the squared cubature error, namely
 \begin{equation}\label{eq:wcErrA}
-\abs{\err(f,\Xdes)}^2=\ip[\ch]{f}{\xi}^2\leq \norm[\ch]{f}^2 \norm[\ch]{\xi}^2.
+\abs{\err(f,\Xdes)}^2=\ip[\ch]{\xi}{f}^2\leq \norm[\ch]{\xi}^2 \norm[\ch]{f}^2 .
 \end{equation}
-The first term on the right describes the contribution to the cubature error made by the nature of the integrand, while the second term describes the contribution made by the quality of the cubature rule.
+The first term on the right describes the contribution made by the quality of the cubature rule, while the second term describes the contribution to the cubature error made by the nature of the integrand.
 
@@
 & = \err(\err(K(\cdot,\cdot \cdot),\Xdes),\Xdes) \quad \text{since } \xi(\vx)=\err(K(\cdot,\vx),\Xdes)\\
-& =\int_{\Omega\times \Omega} K(\vt,\vx)\dif[F(\vx)-F_{\Xdes}(\vx)] \, \dif[F(\vt)-F_{\Xdes}(\vt)].
+& =\int_{\Omega\times \Omega} K(\vt,\vx)\, \dif[F(\vt)-F_{\Xdes}(\vt)] \dif[F(\vx)-F_{\Xdes}(\vx)] .
 \end{align*}
@@
 \begin{align*}
-&\Ex_{f\in\mathcal{A}}[(\err(f,\Xdes)]^2= \Ex_{f\in\mathcal{A}} \left\{\int_{\Omega}f(\vx)\dif F(\vx)-\frac{1}{N}\sum_{i=1}^N f(\vx_i) \right\}^2\\
-=&\Ex_{f\in\mathcal{A}}\left\{\int_{\Omega}(f(\vx)-m)\dif F(\vx)-\frac{1}{N}\sum_{i=1}^N (f(\vx_i)-m) \right\}^2\\
+&\Ex_{f\in\mathcal{A}}[(\err(f,\Xdes)]^2= \Ex_{f\in\mathcal{A}} \left\{\int_{\Omega}f(\vx) \,\dif F(\vx)-\frac{1}{N}\sum_{i=1}^N f(\vx_i) \right\}^2\\
+=&\Ex_{f\in\mathcal{A}}\left\{\int_{\Omega}(f(\vx)-m) \, \dif F(\vx)-\frac{1}{N}\sum_{i=1}^N (f(\vx_i)-m) \right\}^2\\
 =&\int_{\Omega^2}\Ex_{f\in \mathcal{A}}[ (f(\vt)-m)(f(\vx)-m)] \, \dif F(\vt)\dif F(\vx)\\
@@
 &+\frac{1}{N^2}\sum_{i,k=1}^N\Ex_{f\in\mathcal{A}}[(f(\vx_i)-m)(f(\vx_k)-m)]\\
-=&\int_{\Omega^2}K(\vt,\vx) \, \dif F(\vt)\dif F(\vx)-\frac{2}{N}\sum_{i=1}^N \int_{\Omega} K(\vx, \vx_i)\dif F(\vx)+\frac{1}{N^2} \sum_{i,k=1}^N K(\vx_i,\vx_k). 
+=&\int_{\Omega^2}K(\vt,\vx) \, \dif F(\vt)\dif F(\vx)-\frac{2}{N}\sum_{i=1}^N \int_{\Omega} K(\vx, \vx_i)\, \dif F(\vx)+\frac{1}{N^2} \sum_{i,k=1}^N K(\vx_i,\vx_k). 
 \end{align*}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{When Transformed Low Discrepancy Points Also Have Low Discrepancy}
+\section{When Transformed Low Discrepancy Design Also Has Low Discrepancy}
 \label{sec:WhenYes}
@@
 For example, it is automatically satisfied by the inverse cumulative distribution transform \eqref{eq:inverse}.
-Condition \eqref{eq:BigQYesa} is simply a matter of definition of the kernel, $K$, but it is definition with consequences.
+Condition \eqref{eq:BigQYesa} is simply a matter of definition of the kernel, $K$, but this definition has consequences.
 From the perspective of Section \ref{sec:HilbertMeasures}, changing the kernel from $K_\unif$ to $K$ means changing the definition of the distance between two Dirac measures.
@@
 In one dimension, the distance between two Dirac measures defined using the kernel $K_\unif$ above is $\norm{\delta_{x} - \delta_{t}} = \sqrt{|x-t|}$, whereas the distance defined using the kernel $K$ above is $\norm{\delta_{x} - \delta_{t}} = \sqrt{|\Phi(x)-\Phi(t)|}$.
-Under kernel $K$, the distance between two Dirac measures can never be greater than one.
+Under kernel $K$, the distance between two Dirac measures is bounded, even though the domain of the distribution is unbounded.
 Such an assumption may be unpalatable.
@@
 \end{equation}
-where $K$ is the kernel defined above in \eqref{eq:OrigKernel}.
+where $K$ is the kernel defined in \eqref{eq:OrigKernel}.
 
@@
 Figure \ref{fig:UniVsNormDisc} plots the discrepancies for normal designs, $D(\vPsi(\Udes),F_\normal, K)$,  against the discrepancies for the uniform designs, $D(\Udes,F_\unif,K_\unif) = D(\Udes',F_\unif',K)$ for each of the $B=20$ designs.
-Question \eqref{eq:BigQPrime} has a positive answer if and only if the lines passing through any two points on this plot should all have non-negative slope.
+Question \eqref{eq:BigQPrime} has a positive answer if and only if the lines passing through any two points on this plot all have non-negative slopes.
 However, that is not the case.
-Thus \eqref{eq:BigQPrime} is false.
+Thus \eqref{eq:BigQPrime} has a negative answer.
 
@@
 \includegraphics[width=8cm]{code/d5n50.eps}
-\caption{Uniform Discrepancy Vs. Normal Discrepancy. \label{fig:UniVsNormDisc}}
+\caption{Normal discrepancy versus uniform discrepancy for transformed designs. \label{fig:UniVsNormDisc}}
 \end{center}
@@
 \includegraphics[width=8cm]{code/dimVsdisc.eps}
-\caption{Correlation between Uniform Discrepancy and Normal Discrepancy with Different Variable Dimensions. \label{fig:DiscVsd}}
+\caption{Correlation between the uniform and normal discrepancies for different dimensions. \label{fig:DiscVsd}}
 \end{center}
@@
 
-\begin{example} A simple cubature example illustrates that a naively inverse transformed low discrepancy design, $\Udes$, may yield a large $D(\vPsi(\Udes),F_\normal, K)$ and also a large cubature error.
+\begin{example} A simple cubature example illustrates that an inverse transformed low discrepancy design, $\Udes$, may yield a large $D(\vPsi(\Udes),F_\normal, K)$ and also a large cubature error.
 Consider the integration problem in \eqref{eq:integration} with
@@
 We compare cubatures using two designs.
-The design $\Xdes_1$ is the inverse normal transformation of a scrambled Sobol' sequence, $\Udes_1$, which has low discrepancy with respect to the uniform distribution on the $d$-dimensional unit cube.
+The design $\Xdes_1$ is the inverse normal transformation of a scrambled Sobol' sequence, $\Udes_1$, which has a low discrepancy with respect to the uniform distribution on the $d$-dimensional unit cube.
 The design $\Udes_2$ takes the point in $\Udes_1$ that is closet to $\vzero$ and moves it to $\left(10^{-15}, \ldots, 10^{-15}\right)$, which is very close to $\vzero$.
@@
 Furthermore, the cubatures, $\hat{\mu}$, based on these two designs have significantly different errors.
-The first design has both a smaller discrepancy and a smaller error than the second.
-This could not have been induced by looking at the discrepancies of the original uniform designs.
+The first design has both a smaller discrepancy and a smaller cubature error than the second.
+This could not have been inferred by looking at the discrepancies of the original uniform designs.
 
@@
 
-In this section, we propose an efficient algorithm that improves the design's quality in terms of the discrepancy for the target standard normal distribution. 
-We start with a low-discrepancy uniform design, such as a Sobol sequence, and apply the inverse transformation to the design so that the transformed design approximates the target distribution, which is the standard normal distribution in this work.
-Following the optimal design approach, we consider the discrepancy of the normal design as the design criterion and apply a certain optimization algorithm to further improve the design, until the discrepancy reaches the minimum.
+In this section, we propose an efficient algorithm that improves a design's quality in terms of the discrepancy for the target distribution. 
+We start with a low discrepancy uniform design, such as a Sobol' sequence, and transform it into a design that approximates the target distribution. 
+Following the optimal design approach, we then apply a coordinate-exchange algorithm to further improve the discrepancy of the design.
 
-The optimization algorithm we choose is the coordinate-exchange algorithm, which was firstly introduced in \cite{meyer1995coordinate}, and then applied widely to construct various kinds of optimal design \cite{sambo2014coordinate,overstall2017bayesian,kang2018stochastic}.
-The coordinate-exchange algorithm is an iterative optimization method.
-It finds the ``worst" coordinate $x_{ij}$ of the current design and replace it with a better coordinate that decreases the discrepancy. 
+The coordinate-exchange algorithm was introduced in \cite{meyer1995coordinate}, and then applied widely to construct various kinds of optimal designs \cites{sambo2014coordinate,overstall2017bayesian,kang2018stochastic}.
+The coordinate-exchange algorithm is an iterative method.
+It finds the ``worst" coordinate $x_{ij}$ of the current design and replaces it to decrease loss function, in this case, the discrepancy. 
 The most appealing advantage of the coordinate-exchange algorithm is that at each step one need only solve a univariate optimization problem.
@@
 \begin{equation}\label{eq:coorddeletion}
-\frakd_c(k) = D^2(\Xdes)-D^2(\Xdes_{-k}).
+\frakd_c(j) = D^2(\Xdes)-D^2(\Xdes_{-j}).
 \end{equation}
-Here, the design $\Xdes_{-k}$ still has $N$ points but now only $d$ dimensions, the $k^{\text{th}}$ coordinate having been removed.
-For this calculation to be feasible, we need the target distribution to independent marginals defined on the domain.
+Here, the design $\Xdes_{-j}$ still has $N$ points but now only $d$ dimensions, the $j^{\text{th}}$ coordinate having been removed.
+For this calculation to be feasible, the target distribution must have independent marginals.
 Also, the kernel to be of product form.
-To simplify the notation, we assume a somewhat stronger condition, namely that each term in the product defining the kernel is the same for every coordinate:
+To simplify the derivation, we assume a somewhat stronger condition, namely that the marginals are identical and that each term in the product defining the kernel is the same for every coordinate:
 \begin{equation}
     \label{eq:prodkernel}
-    \Omega = \tOmega \times \cdots \times \tOmega, \qquad K(\vt,\vx) = \prod_{k=1}^d [1+ \tK(t_k,x_k)], \qquad \tK:\tOmega \times \tOmega \to \reals.
+    \Omega = \tOmega \times \cdots \times \tOmega, \qquad K(\vt,\vx) = \prod_{j=1}^d [1+ \tK(t_j,x_j)], \qquad \tK:\tOmega \times \tOmega \to \reals.
 \end{equation}
-where the term in the product is 
 We then choose 
-\begin{equation} \label{eq:rowchoice}
-    k^*=\argmax_{k=1, \ldots, d} \frakd_c(k).
+\begin{equation} \label{eq:columnchoice}
+    j^*=\argmax_{j=1, \ldots, d} \frakd_c(j).
 \end{equation}
-For reasons analogous to those given above, the $k^{*\text{th}}$ coordinate seems the best candidate for change.
+For reasons analogous to those given above, the $j^{*\text{th}}$ coordinate seems to be the best candidate for change.
 
-Let $\Xdes^*(x)$ denote the design that results from replacing $x_{i^*k^*}$ by $x$.
+Let $\Xdes^*(x)$ denote the design that results from replacing $x_{i^*j^*}$ by $x$. 
 We now define $\Delta(x)$ as improvement in the squared discrepancy resulting from replacing $\Xdes$ by $\Xdes^*(x)$:
@@
 \end{equation}
-If we can find an $x$ for which $\Delta(x)$ is positive, then we can reduce the discrepancy.  This is the rationale for the coordinate-exchange algorithm given in  Algorithm \ref{alg:coorex}.
+We can reduce the discrepancy by find an $x$ such that $\Delta(x)$ is positive. 
+The coordinate-exchange algorithm outlined in Algorithm \ref{alg:coorex} improves the design by maximizing $\Delta(x)$ for one chosen coordinate in one iteration. 
+The algorithm terminates when it exhausts the maximum allowed number of iterations or the optimal improvement $\Delta(x^*)$ is so small that it becomes negligible ($\Delta(x^*)\leq \textrm{TOL}$). 
+Algorithm \ref{alg:coorex} is a greedy algorithm, and thus it can stop at a local optimal design. 
+We recommend multiple runs of the algorithm with different initial designs to obtain a design with the lowest discrepancy possible. 
+Alternatively, users can include stochastic scheme in choosing the coordinate that is to be exchanged, similarly as in \cite{kang2018stochastic}.
 
@@
 \begin{algorithmic}[1]
-\INPUT An initial design $\Xdes$ on the domain $\Omega$, a target distribution, $F$, and a kernel, $K$ of the form \eqref{eq:prodkernel}, a small value $TOL$ to measure convergence of the algorithm, and the maximum allowed number of iterations, $I_{\max}$.
+\INPUT An initial design $\Xdes$ on the domain $\Omega$, a target distribution, $F$, a kernel, $K$ of the form \eqref{eq:prodkernel}, a small value $\TOL$ to determine the convergence of the algorithm, and the maximum allowed number of iterations, $M_{\max}$.
 \OUTPUT Low discrepancy design $\Xdes$. 
-\State Compute the squared discrepancy $D^2_0$ for the initial design $\Xdes$ and set the iteration index $i=0$.
-\For{$i=1,2,\ldots, I_{\max}$}
+%\State Set the iteration index: $m=0$.
+\For{$m=1,2,\ldots, M_{\max}$}
 \State Compute the point deletion function $\frakd_p(1), \ldots, \frakd_p(N)$. Choose the $i^*$-th point which has the largest point deletion value, i.e. $i^* = \argmax_{i} \frakd_p(i)$. 
-\State For the $i^*$-th point, Compute the coordinate deletion function $\frakd_c(1), \ldots, \frakd_c(d)$ and choose the $j^*$-th element which has the largest coordinate deletion value, i.e., $k^* = \argmax_{k} \frakd_c(k)$.
-\State Replace the coordinate $x_{i^*k^*}$ by $x^*$ which is the solution of the univariate optimization
+\State Compute the coordinate deletion function $\frakd_c(1), \ldots, \frakd_c(d)$ and choose the $j^*$-th coordinate which has the largest coordinate deletion value, i.e., $j^* = \argmax_{j} \frakd_c(j)$.
+\State Replace the coordinate $x_{i^*j^*}$ by $x^*$ which is defined by the univariate optimization problem
 \[
@@
 \]
-\If{$\Delta(x^*)/D^2_{i-1}>TOL$} 
-\State {Replace $x_{i^*k^*}$ with $x^*$ in the design $\Xdes$, i.e., let  $\Xdes(x^*)$ replace the old $\Xdes$.}
-\State Update the squared discrepancy $D^2_{i}=D^2_{i-1}-\Delta(x^*)$. 
+\If{$\Delta(x^*)>\TOL$} 
+\State Replace $x_{i^*j^*}$ with $x^*$ in the design $\Xdes$, i.e., let  $\Xdes(x^*)$ replace the old $\Xdes$.
 \Else 
-\State{Terminate the loop and return the design $\Xdes$.} 
+\State Terminate the loop.
+
 \EndIf
 \EndFor
+\State Return the design, $\Xdes$, and the discrepancy, $D(\Xdes,F,K)$.
 \end{algorithmic}
@@
 For kernels of product form, \eqref{eq:prodkernel}, and target distributions with independent and identical marginals, the formula for the squared discrepancy in \eqref{eq:discDef} becomes
+\begin{subequations}
+\label{eq:chHdef}
 \begin{align}
 \nonumber
-    D^2(\Xdes,\rho,K)  & = (1+c)^d  - \frac 2N \sum_{i=1}^N H(\vx_{i}) + \frac{1}{N^2}  \sum_{i,j=1}^N K(\vx_{i},\vx_{j}),
+    D^2(\Xdes,\rho,K)  & = (1+c)^d  - \frac 2N \sum_{i=1}^N H(\vx_{i}) + \frac{1}{N^2}  \sum_{i,k=1}^N K(\vx_{i},\vx_{k}),
     \intertext{where}
@@
     c & = \int_{\tOmega \times \tOmega} \tK(t_k,x_k) \, \tvarrho(t) \tvarrho (x) \, \dif t\dif x = \int_{\tOmega} h(x) \, \tvarrho(x) \, \dif x, \\
-    H(\vx) &= \prod_{k=1}^d [1+ h(x_{k})].
+    H(\vx) &= \prod_{j=1}^d [1+ h(x_{j})].
 \end{align}
+\end{subequations}
 An evaluation of $h(x)$ and $\tK(t,x)$ each require $\Order(1)$ operations, while an evaluation of $H(\vx)$ and $K(\vt,\vx)$ each require $\Order(d)$ operations.
@@
 \frakd_p(i) 
-&= \frac{(2N-1)(1+c)^d}{N^2} - \frac{2}{N}\biggl[ \frac{1}{N} \sum_{j=1}^N  H(\vx_{j}) + \left(1 - \frac 1N \right) H(\vx_{i})  \biggr] \\
+&= \frac{(2N-1)(1+c)^d}{N^2} - \frac{2}{N}\biggl[ \frac{1}{N} \sum_{k=1}^N  H(\vx_{k}) + \left(1 - \frac 1N \right) H(\vx_{i})  \biggr] \\
 \label{eq:rowdeletionA}
-& \qquad \qquad + \frac{1}{N^2}\biggl[2 \sum_{j=1}^N K(\vx_{i},\vx_{j})- K(\vx_{i},\vx_{i})\biggr]. 
+& \qquad \qquad + \frac{1}{N^2}\biggl[2 \sum_{k=1}^N K(\vx_{i},\vx_{j})- K(\vx_{i},\vx_{i})\biggr]. 
 \end{align}
@@
 \begin{multline}\label{eq:coldeletionA}
-\frakd_c(k) = (c-1)c^{d-1} -\frac{2}{N}\sum_{i=1}^N \frac{h(x_{ik})H(\vx_i)}{1+h(x_{ik})}  \\
-+\frac{1}{N^2}\sum_{i,j=1}^N \frac{\tK(x_{ik},x_{jk}) K(\vx_i,\vx_j)}{1+\tK(x_{ik},x_{jk})}  .
+\frakd_c(j) = (c-1)c^{d-1} -\frac{2}{N}\sum_{i=1}^N \frac{h(x_{ij})H(\vx_i)}{1+h(x_{ij})}  \\
++\frac{1}{N^2}\sum_{i,k=1}^N \frac{\tK(x_{ij},x_{kj}) K(\vx_i,\vx_j)}{1+\tK(x_{ij},x_{kj})}  .
 \end{multline}
@@
 \Delta(x)
-&= -\frac{2\left[  h(x_{i^*k^*})-h(x)    \right]H(\vx_{i^*})}{N[1 + h(x_{i^*k^*})]}   \\
+&= -\frac{2\left[  h(x_{i^*j^*})-h(x)    \right]H(\vx_{i^*})}{N[1 + h(x_{i^*j^*})]}   \\
 \nonumber
-& \qquad \qquad +\frac{1}{N^2}\left(2\sum_{\substack{i=1 \\ i \ne i^*}}^N  \frac{[\tK(x_{i^*k^*},x_{ik^*})-\tK(x,x_{ik^*})] K(\vx_{i^*},\vx_i)} {1 + \tK(x_{i^*k^*},x_{ik^*})} \right . \\
-& \qquad \qquad \left . + \frac{[\tK(x_{i^*k^*},x_{i^*k^*})-\tK(x,x)] K(\vx_{i^*},\vx_{i^*})} {1 + \tK(x_{i^*k^*},x_{i^*k^*})} \right )
+& \qquad \qquad +\frac{1}{N^2}\left(2\sum_{\substack{i=1 \\ i \ne i^*}}^N  \frac{[\tK(x_{i^*j^*},x_{ij^*})-\tK(x,x_{ij^*})] K(\vx_{i^*},\vx_i)} {1 + \tK(x_{i^*j^*},x_{ij^*})} \right . \\
+& \qquad \qquad \left . + \frac{[\tK(x_{i^*j^*},x_{i^*j^*})-\tK(x,x)] K(\vx_{i^*},\vx_{i^*})} {1 + \tK(x_{i^*j^*},x_{i^*j^*})} \right )
 \end{align} 
@@
 \begin{equation}\label{eq:deltapfunction}
-\Delta'(x) = Ah(x)  - \frac{1}{N}\sum_{\substack{i=1 \\ i \ne i^*}}^N B_i \tK(x,x_{ik^*}) - C \tK(x,x)
+\Delta'(x) = Ah(x)  - \frac{1}{N}\sum_{\substack{i=1 \\ i \ne i^*}}^N B_i \tK(x,x_{ij^*}) - C \tK(x,x)
 \end{equation}
@@
 \begin{equation*}
-A = \frac{2H(\vx_{i^*})}{1 + h(x_{i^*k^*})}, \quad
-B_i  = \frac{2K(\vx_{i^*},\vx_i)} {1 + \tK(x_{i^*k^*},x_{ik^*})}, \quad
-C  = \frac{K(\vx_{i^*},\vx_{i^*})} {N[1 + \tK(x_{i^*k^*},x_{i^*k^*})]}.
+A = \frac{2H(\vx_{i^*})}{1 + h(x_{i^*j^*})}, \quad
+B_i  = \frac{2K(\vx_{i^*},\vx_i)} {1 + \tK(x_{i^*j^*},x_{ij^*})}, \quad
+C  = \frac{K(\vx_{i^*},\vx_{i^*})} {N[1 + \tK(x_{i^*j^*},x_{i^*j^*})]}.
 \end{equation*}
 Note that $A, B_1, \ldots, B_N, C$ only need to be computed once for each iteration of the coordinate exchange algorithm.
-
-\FJH{Fred got to here}
 
@@
 
-To demonstrate the performance of the $d$-dim standard normal design proposed in Section \ref{sec:CoordEx}, we compare three algorithms: (1) RAND: inverse transformed uniform random sequence;  (2) SOBOL: inverse transformed Sobol sequence; (3) E-SOBOL: inversed transformed scrambled Sobol sequence with uni-dimensional projection at $\left\{\frac{2i-1}{2N}\right\}_{i=1}^{2N}$; (4) CE: improved E-SOBOL with proposed Algorithm 1.
-We have tried different combinations of dimension and sample size, and let the sample size become larger as the dimension becomes higher. 
-Using each algorithm we generate 500 designs, and for each design, we compute the discrepancy \eqref{eq:DisNormald>1} and compare the distribution of discrepancies from different algorithms as shown in Figure \ref{fig:comparison}.
+To demonstrate the performance of the $d$-dim standard normal design proposed in Section \ref{sec:CoordEx}, we compare three families of designs: (1) RAND: inverse transformed IID uniform random numbers;  (2) SOBOL: inverse transformed Sobol' set; (3) E-SOBOL: inverse transformed scrambled Sobol' set where the one dimensional projections of the Sobol' set have been adjusted to be  $\left\{1/(2N), 3/(2N), \ldots, (2N-1)/(2N) \right\}$; (4) CE: improved E-SOBOL via Algorithm \ref{alg:coorex}.
+We have tried different combinations of dimension, $d$, and sample size, $N$. 
+For each $(d,N)$ and each algorithm we generate $500$ designs and compute their discrepancies \eqref{eq:DisNormald>1}.
 
 Figure \ref{fig:SOBOLVsRAND} contains the boxplots of normal discrepancies corresponding to the four generators with $d=2$ and $N=32$.
-It shows that SOBOL, E-SOBOL and CE all outperform RAND by a great margin.
-To better present the comparison between the generators, in the follow figures, we exclude the boxplot from RAND.
+It shows that SOBOL, E-SOBOL, and CE all outperform RAND by a great margin.
+To better present the comparison between the better generators, in Figure \ref{fig:comparison} we mostly exclude RAND.
+
+We also report the average execution times for the four generators in Table \ref{tab:ExeTime}.
+All codes were run on a MacBook Pro with 2.4 GHz Intel Core i5 processor.
+The maximum iteration allowed is set to be $M_{\max} = 200$, and the Algorithm \ref{alg:coorex} converges within 20 iterations in all simulation examples.
 
@@
 \includegraphics[width=8cm]{code/boxplotall_d2n32.eps}
-\caption{Performance Comparison of Generators. \label{fig:SOBOLVsRAND}}
+\caption{Performance comparison of designs. \label{fig:SOBOLVsRAND}}
 \end{center}
@@
 
-We summarize the observations as follows. 
+ We summarize the results of our simulation as follows. 
 \begin{enumerate}
 \item
-Overall, E-SOBOL and CE outperform SOBOL. 
+Overall, CE produces the smallest discrepancy.
 \item 
-When the sample is relatively dense, i.e., $N/d$ ratio is large, E-SOBOL and CE have similar performance. They both outperform SOBOL by a great margin
+When the design is relatively dense, i.e., $N/d$ is large, E-SOBOL and CE have similar performance.
 \item
-As the sample becomes more sparse, i.e., $N/d$ ratio is smaller, SOBOL and E-SOBOL have similar performance. The proposed CE becomes much superior to both of them.
+When the design is more sparse, i.e., $N/d$ is smaller, SOBOL and E-SOBOL have similar performance, but CE is superior to both of them in terms of the discrepancy.
+not only in terms of the mean but also in terms of the \emph{range} for the $500$ designs generated.
+
+\item CE requires the longest computational time to construct a design, but this is moderate.
+When the cost of obtaining function values is substantial, then the cost of constructing the design may be insignificant.
 \end{enumerate}
-Therefore, E-SOBOL sequences are preferable when the sample size is large relative to the dimension, and we recommend using the proposed remedy approach to further improve E-SOBOL when the sample size is small or moderate.
 
-\begin{figure}[ht]\label{fig:comparison}
+\begin{figure}[ht]
 \centering
@@
 {\subfigure[$d=10, N=512$] {\includegraphics[width=5.5cm]{code/boxplotall_d10n512.eps}}}
-\caption{Performance Comparison of Generators}
+\caption{Performance comparison of designs \label{fig:comparison}}
 \end{figure}
 
-We also report the average execution time of the four generators in Table \ref{tab:ExeTime}.
-All codes were run on a MacBook Pro with 2.4 GHz Intel Core i5 processor.
-Although CE requires the longest computational time compared to the other three generators, the execution time to achieve one sample is very reasonable.
-CE is quite computationally efficient and practical especially when the dimension is high and only a small sample is affordable.
+% Table generated by Excel2LaTeX from sheet 'Sheet1'
+\begin{table}[htbp]
+  \centering
+  \caption{Execution Time of Generators (in seconds)}
+    \begin{tabular}{r*6{@{\ \ }c}}
+    \toprule
+         $d$ & $2$   & $3$   & $4$   & $6$   & $8$   & $10$ \\
+  $N$ & $32$   & $64$   & $64$   & $128$   & $256$   & $512$ \\
+    \hline
+    RAND  & $3.22\text{E}{-5}$      &  $5.21\text{E}{-5}$     & $5.27\text{E}{-5}$      &  $9.92\text{E}{-5}$     & $2.48\text{E}{-4}$      & $ 5.32\text{E}{-4}$ \\
+    SOBOL & $8.60\text{E}{-4}$      &  $0.10\text{E}{-2}$     &    $0.11\text{E}{-2}$   &  $0.16\text{E}{-2}$     & $0.21\text{E}{-2}$      &  $0.28\text{E}{-2}$\\
+    E-SOBOL & $8.71\text{E}{-4}$  & $0.11\text{E}{-2}$      &     $0.12\text{E}{-2}$  &  $0.16\text{E}{-2}$     &   $0.23\text{E}{-2}$    & $0.32\text{E}{-2}$  \\
+    CE    & $1.34\text{E}{-2}$      & $2.73\text{E}{-2}$      & $6.12\text{E}{-2}$      &   $0.24$    &   $1.04$    & $3.84$  \\
+    \hline
+    \end{tabular}%
+  \label{tab:ExeTime}%
+\end{table}%
 
-% Table generated by Excel2LaTeX from sheet 'Sheet1'
+\begin{comment}
 \begin{table}[htbp]
@@
 \end{table}%
+\end{comment}
 
@@
 It's interesting to observe that SOBOL and E-SOBOL may perform even worse than RAND in several cases, and this aligns with our discussion in Section 4: the inverse transformed low uniform discrepancy sequence may not retain low normal discrepancy.
-When the sample size $N$ is small/moderate relative to dimension $d$, using CE would limit the potential danger of very inaccurate estimate caused by a sample with large normal discrepancy.
+When the sample size $N$ is small/moderate relative to dimension $d$, using CE would limit the potential danger of very inaccurate estimate caused by a sample with a large normal discrepancy.
 
-\begin{figure}[ht]\label{fig:comparison_integral}
+\begin{figure}[ht]
 \centering
@@
 
-In this chapter, we summarize the three interpretations of the discrepancy. 
-It is a measure on how well the empirical distribution of a design approximates the target distribution or a tight upper bound of some quadrature of an integral approximation, or the root mean squared cubature error of an integral approximation when the integrand is a stochastic process.
-Then, we point out a flaw of the inverse transformation method, which is used to generate random samples (or designs) following any non-uniform distribution. 
-The flaw is that any low-discrepancy uniform designs do not necessarily lead to low-discrepancy for the inverse transformed designs. 
-To explain this issue, we choose the standard normal distribution as an example for non-uniform distributions. 
-We show that the low-discrepancy uniform design may not preserve the low-discrepancy after inverse distribution transformation into a standard normal distribution. 
-As a remedy approach, we propose a coordinate-exchange algorithm to further minimize the $L_2$-discrepancy of the design from the inverse transformation of the low-discrepancy uniform design.
+This chapter summarizes the three interpretations of the discrepancy.
+We show that for kernels and variable transformations satisfying conditions \eqref{eq:BigQYes}, variable transformations of low discrepancy uniform designs yield low discrepancy designs with respect to the target distribution.
+However, for more practical choices of kernels, this correspondence may not hold.
+The coordinate-exchange algorithm can improve the discrepancies of candidate designs that may be constructed by variable transformations.
 
-It's worth pointing out that the discrepancy defined in \eqref{eq:discDef} can be generalized to any $d$-dim distribution $\varrho$ with mean $\boldsymbol{\mu} = (\mu_1,\cdots,\mu_d)$.
-The centered reproducing kernel in \eqref{eq:OrigKernel} should be
-\begin{equation} \label{ExtKernel}
-     K(\vt,\vx)  = \prod\limits_{j=1}^d\left[1+ \frac 12 \left(|t_j-\mu_j|+ |x_j-\mu_j|- |x_j-t_j| \right)\right].
+While discrepancies can be defined for arbitrary kernels, we believe that the choice of kernel can be important, especially for small sample sizes.
+If the distribution has a symmetry, e.g.
+$\varrho(\vT(\vx)) = \varrho(\vx)$ for some probability preserving bijection $\vT:\Omega \to \Omega$, then we would like our discrepancy to remain unchanged under such a bijection, i.e., $D(\vT(\Xdes),\varrho,K) = D(\Xdes,\varrho,K)$.
+This can typically be ensured by choosing kernels satisfying $K(\vT(\vt),\vT(\vx)) = K(\vt,\vx)$.
+The kernel $K_\unif$ defined in \eqref{eq:L2kernel} satisfies this assumption for the standard uniform distribution and the transformation $\vT(\vx) = \vone - \vx$.
+The kernel $K$ defined in \eqref{eq:OrigKernel} satisfies this assumption for the standard normal distribution and the transformation $\vT(\vx) = -\vx$.
+
+For target distributions with independent marginals and kernels of product form as in \eqref{eq:prodkernel}, \emph{coordinate weights} \cite{DicEtal14a}*{Section 4} are used to determine which projections of the design, denoted by $\fraku \subseteq \{1, \ldots, d\}$, are more important.
+The product form of the kernel given in \eqref{eq:prodkernel} can be generalized as
+\begin{equation} \label{eq:prodKernelWts}
+     K_{\vgamma}(\vt,\vx)  = \prod_{j=1}^d\left[1+ \gamma_j \tK(t_j,x_j) \right].
 \end{equation}
-Then the discrepancy $D(\Xdes,\Ftar,K)$ can be computed using \eqref{eq:discDef}, and the two integrals in \eqref{eq:discDef} may require numerical approximations for some target distribution. 
-If the analytic formula of $D(\Xdes,\Ftar,K)$ can be derived, the coordinate-exchange algorithms can be applied in a similar fashion to improve the inverse transformation method.
+Here the positive coordinate weights are $\vgamma = (\gamma_1, \ldots, \gamma_d)$.
+The squared discrepancy corresponding to this kernel may then be written as
+\begin{align*}
+      D^2(\Xdes,F,K_{\vgamma}) &= \sum_{\substack{\fraku \subseteq \{1, \ldots, d\} \\ \fraku \ne \emptyset}}\gamma_\fraku D^2_{\fraku} (\Xdes,\rho,K), \qquad \gamma_{\fraku} = \prod_{j \in \fraku} \gamma_j\\
+    D^2_{\fraku} (\Xdes_\fraku,F_\fraku,K) & = c^{\abs{\fraku}} - \frac 2N \sum_{i=1}^N \prod_{j \in \fraku} h(x_{ij}) + \frac{1}{N^2} \sum_{i,k=1}^N \prod_{j \in \fraku} \tK(x_{ij},x_{kj}),
+\end{align*}
+where $c$ and $h$ are defined in \eqref{eq:chHdef}.
+Here $\Xdes_\fraku$ denotes the projection of the design into the coordinates contained in $\fraku$, and $F_\fraku = \prod_{j \in \fraku} F_j$ is the $\fraku$-marginal distribution.
+Each discrepancy piece, $D_{\fraku} (\Xdes_\fraku,F_\fraku,K)$, measures how well $\Xdes_\fraku$ matches $F_\fraku$.
 
-\FJH{I should write about coordinate weights}
+The values of the coordinate weights can be chosen to reflect the user's belief as to the importance of the design matching the target for various coordinate projections.
+A large value of $\gamma_j$ relative to the other $\gamma_{j'}$ places more importance on the $D_{\fraku} (\Xdes_\fraku,F_\fraku,K)$ with $j \in \fraku$.
+Thus, $\gamma_j$ is an indication of the importance of coordinate $j$ in the definition of $D(\Xdes,F,K_{\vgamma})$.
+
+If $\vgamma$ is one choice of coordinate weights and $\vgamma'=C\vgamma$ is another choice of coordinate weights where $C > 1$, then $\gamma'_\fraku = C^{\abs{\fraku}} \gamma_\fraku$.
+Thus, $D(\Xdes,F,K_{\vgamma'})$ emphasizes the projections corresponding to the $\fraku$ with large $\abs{\fraku}$, i.e., the higher order effects.
+Likewise, $D(\Xdes,F,K_{\vgamma'})$ places relatively more emphasis lower order effects.
+Again, the choice of coordinate weights reflects the user's belief as to the relative importance of the design matching the target distribution for lower order effects or higher order effects.
+
+\bibliography{Ref.bib,FJH23,FJHown23}
 
 \section*{Appendix}
-Derivation of \eqref{eq:DisNormald>1}. 
-\begin{proof}
-We first derive $D^2(\Xdes,\Phi_1,K)$ for $d=1$ case. 
-To compute the discrepancy, we first integrate the kernel once:
+We derive the formula in \eqref{eq:DisNormald>1} for the discrepancy with respect to the standard normal distribution, $\Phi$, using the kernel defined in \eqref{eq:OrigKernel}.
+We first consider the case $d=1$.
+We integrate the kernel once:
 \begin{align*}
-\MoveEqLeft{\int_{-\infty}^\infty K(x,t) \, \dif \Phi_1(x)}\\
-=&\int_{-\infty}^{\infty} \left(1+\frac{1}{2}|x|+\frac{1}{2}|t|-\frac{1}{2}|x-t|\right)\phi(x) \, \dif x\\
-=& 1+ \frac{1}{\sqrt{2\pi}} + \frac{1}{2}|t|-\frac{1}{2}\left[\int_{-\infty}^{t}(t-x)\phi(x) \, \dif x+\int_{t}^{\infty} (x-t)\phi(x) \, \dif x\right]\\
-=& 1+ \frac{1}{\sqrt{2\pi}} + \frac{1}{2}|t| - t [\Phi_1(t)-1/2] - \phi(t) .
+\MoveEqLeft{\int_{-\infty}^\infty K(t,x) \, \dif \Phi(t)}\\
+=&\int_{-\infty}^{\infty} \left(1+\frac{1}{2}|x|+\frac{1}{2}|t|-\frac{1}{2}|x-t|\right)\phi(t) \, \dif t\\
+=& 1+ \frac{1}{\sqrt{2\pi}} + \frac{1}{2}|x|
+-\frac{1}{2}\left[\int_{-\infty}^{x}(x - t)\phi (t) \, \dif t
++\int_{x}^{\infty} (t - x)\phi(t) \, \dif t\right]\\
+=& 1+ \frac{1}{\sqrt{2\pi}} + \frac{1}{2}|x| - x [\Phi(x)-1/2] - \phi(x) .
 \end{align*}
-Then we integrate again:
+Then we integrate once more:
 \begin{align*}
-\MoveEqLeft{\int_{-\infty}^\infty \int_{-\infty}^\infty K(x,t) \, \dif \Phi_1(x) \dif \Phi_1(t)}\\
-& =  \int_{-\infty}^{\infty} \left( 1+\frac{1}{\sqrt{2\pi}} + \frac{1}{2}|t| - t [\Phi_1(t)-1/2] + \phi(t)\right)\phi(t) \, \dif t\\
-&= 1+ \sqrt{\frac{2}{\pi}} + \int_{-\infty}^{\infty} \{ - t \Phi_1(t)\phi(t)  +  [\phi(t)]^2 \} \, \dif t\\
-&= 1+\sqrt{\frac{2}{\pi}}-\frac{1}{\sqrt{4\pi}}+\int_{-\infty}^{\infty}\frac{1}{2\pi}e^{-t^2}\dif t\\
-&= 1+\sqrt{\frac{2}{\pi}}-\frac{1}{\sqrt{4\pi}}+\frac{\frac{1}{\sqrt{2}}}{\sqrt{2\pi}}\int_{-\infty}^{\infty}\frac{1}{\sqrt{2\pi}\left(\frac{1}{\sqrt{2}}\right)}e^{-\frac{t^2}{2\left(\frac{1}{\sqrt{2}}\right)^2}}\dif t\\
-&=1+\sqrt{\frac{2}{\pi}}. 
+\MoveEqLeft{\int_{-\infty}^\infty \int_{-\infty}^\infty K(t,x) \, \dif \Phi(t) \dif \Phi(x)}\\
+& =  \int_{-\infty}^{\infty} \left(1+ \frac{1}{\sqrt{2\pi}} + \frac{1}{2}|x| - x [\Phi(x)-1/2] - \phi(x) \right)\phi(x) \, \dif x\\
+&= 1+ \sqrt{\frac{2}{\pi}} + \int_{-\infty}^{\infty} \{ - x \Phi(x)\phi(x)  +  [\phi(x)]^2 \} \, \dif x\\
+&= 1+\sqrt{\frac{2}{\pi}}-\frac{1}{\sqrt{4\pi}}+\int_{-\infty}^{\infty}\frac{1}{2\pi}\mathrm{e}^{-x^2}\dif x =1+\sqrt{\frac{2}{\pi}}. 
 \end{align*}
-Notice that $\int_{-\infty}^{\infty} t\Phi_1(t)\phi(t)\dif t = \frac{1}{\sqrt{4\pi}}$ and 
-\begin{eqnarray*}
-&&\int_{\Omega}K(x,x_n)\dif \Phi_1(x)\\
-&=& \int_{-\infty}^{\infty} \left(1+\frac{1}{2}|x|+\frac{1}{2}|x_n|-\frac{1}{2}|x-x_n|\right)\phi(x)\dif x\\
-&=& 1+\frac{1}{2}\sqrt{\frac{2}{\pi}}+\frac{1}{2}|x_n|-\frac{1}{2}\left[\int_{-\infty}^{x_n}(x_n-x)\phi(x)\dif x+\int_{x_n}^{\infty} (x-x_n)\phi(x)\dif x\right]\\
-&=& 1+\sqrt{\frac{1}{2\pi}}+\frac{1}{2}|x_n|-\frac{1}{2}\left[\int_{-\infty}^{x_n}(x_n-x)\phi(x)\dif x+\int_{x_n}^{\infty} (x-x_n)\phi(x)\dif x\right]\\
-&=& 1+\sqrt{\frac{1}{2\pi}}+\frac{1}{2}|x_n|-\frac{1}{2}\left[2x_n\Phi_1(x_n)-x_n-2\int_{-\infty}^{x_n}x\phi(x)\dif x\right]\\
-&=& 1+\sqrt{\frac{1}{2\pi}}+\max(x_n,0)-x_n\Phi_1(x_n)-\frac{ e^{-x_n^2/2}}{\sqrt{2\pi}}. 
-\end{eqnarray*}
-Thus, the discrepancy can be obtained as follows. 
-\begin{eqnarray*}
-&& D^2(\Xdes,\Phi_1,K)=1+\sqrt{\frac{2}{\pi}}-\frac{2}{N}\sum_{n=1}^N \left[1+\sqrt{\frac{1}{2\pi}}+\max(x_n,0)-x_n\Phi_1(x_n)-\frac{ e^{-x_n^2/2}}{\sqrt{2\pi}}\right]\\
-&&+\frac{1}{N^2}\sum_{n,m=1}^N \left[1+\frac{1}{2}|x_n|+\frac{1}{2}|x_m|-\frac{1}{2}|x_n-x_m|\right]\\
-&= &-\frac{2}{N}\sum_{n=1}^N \left[\max(x_n,0)-x_n\Phi_1(x_n)-\frac{ e^{-x_n^2/2}}{\sqrt{2\pi}}\right]+\frac{1}{N^2}\sum_{n,m=1}^N \left[\frac{1}{2}|x_n|+\frac{1}{2}|x_m|-\frac{1}{2}|x_n-x_m|\right]\\
-&=& -\frac{2}{N}\sum_{n=1}^N \left[\max(x_n,0)-x_n\Phi_1(x_n)-\phi(x_n)\right]+\frac{1}{N}\sum_{n=1}^N|x_n|-\frac{1}{2N^2}\sum_{n,m=1}^N|x_n-x_m|.\\
-\end{eqnarray*}
-For the distribution $N({\bf 0}, {\bf I}_d)$, the joint pdf is $$\prod\limits_{j=1}^d\phi(x_j) = \prod\limits_{j=1}^d \frac{1}{\sqrt{2\pi}}e^{-x_j^2/2}.$$
-Here the cdf function $\Phi(\vx)=\prod_{j=1}^d \Phi_1(x_j)$. Thus, 
-\begin{align*}
-\int_{\reals^d\times \reals^d} K(\vx,\vt)&\dif\Phi(\vx)\dif\Phi(\vt) = \left(1+\sqrt{\frac{2}{\pi}}\right)^d, \\
-\int_{\reals^d}K(\vx,\vx_n)\dif\Phi(\vx) = \prod\limits_{j=1}^d&\left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_j|-x_j[\Phi(x_j)-1/2]-\phi(x_j)\right].
-\end{align*}
-The discrepancy can be obtained
+
+Generalizing this to the $d$-dimensional case yields 
+\begin{gather*}
+\int_{\reals^d\times \reals^d} K(\vx,\vt) \, \dif\Phi(\vx)\dif\Phi(\vt) = \left(1+\sqrt{\frac{2}{\pi}}\right)^d, \\
+\int_{\reals^d}K(\vx,\vx_n) \, \dif\Phi(\vx) = \prod\limits_{j=1}^d \left[ 1+\frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x_j|-x_j[\Phi(x_j)-1/2]-\phi(x_j)\right].
+\end{gather*}
+Thus, the discrepancy for the normal distribution is
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-\end{proof}
-
-\FJH{Lulu, could you please make the references consistent, i.e., all initials and not first names.  Also please use AMS standard abbreviations for the journals.}
-\bibliographystyle{amsplain}
-%\bibliography{FJH23,FJHown23}
-\bibliography{Ref.bib,FJH23,FJHown23}
 

### 2019-06-14 InvPts_verB.tex
Updates from Overleaf

@@
 %%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%Needs FJH23.bib, FJHown23.bib, Ref.bib, KernelPict.eps, Kernel3DPict.eps,
+% d5n50.eps, dimVsdisc.eps, boxplotall_d2n32.eps, 
+% boxplot_d2n32.eps, boxplot_d3n64.eps, boxplot_d4n64.eps, boxplot_d5n128.eps, 
+% boxplot_d8n256.eps, boxplotall_d10n512.eps
+% errorboxplot_d2n32.eps, errorboxplot_d3n64.eps, errorboxplot_d4n64.eps, 
+% errorboxplot_d6n128.eps, errorboxplot_d8n256.eps, errorboxplot_d10n512.eps
 
@@
 \newcommand{\vgamma}{\boldsymbol{\gamma}}
+\newcommand{\figdir}{code/} %internally
+%\newcommand{\figdir}{} %internally
 
@@
 Define the kernel function $K:\Omega \times \Omega \to \reals$ in terms of inner products of Dirac measures:
-\begin{equation} \label{kerDeltaDef}
+\begin{equation} \label{eq:kerDeltaDef}
     K(\vt,\vx) := \ip[\cm]{\delta_{\vt}}{\delta_{\vx}}, \qquad \forall \vt, \vx \in \Omega.
@@
 The squared distance between two Dirac measures in $\cm$ is then
-\begin{equation} \label{distDelta}
+\begin{equation} \label{eq:distDelta}
    \norm[\cm]{\delta_{\vx} - \delta_{\vt}}^2 = K(\vt,\vt) - 2K(\vt,\vx) + K(\vx,\vx), \qquad \forall \vt, \vx \in \Omega.
@@
 K(\vx, \vt) = K(\vt, \vx) \qquad \forall \vt, \vx\in \Omega,\\
-\sum\limits_{i, k=1}^N c_i c_k  K(\vx_i,\vx_k) > 0, \qquad \forall N\in\mathbb{N}, \  \vc \in\mathbb{R}^N, \ \vc \ne \vzero,  \ \Xdes \subset \Omega.
+\sum\limits_{i, k=1}^N c_i c_k  K(\vx_i,\vx_k) > 0, \qquad \forall N\in\mathbb{N}, \  \vc \in\mathbb{R}^N \setminus \{\vzero\},  \ \Xdes \subset \Omega.
 \end{gather}
@@
 The inner product of arbitrary measures $\lambda, \nu \in \cm$ can be expressed in terms of a double integral of the kernel, $K$:
-\begin{equation} \label{ipMdef}
+\begin{equation} \label{eq:ipMdef}
     \ip[\cm]{\lambda}{\nu} = \int_{\Omega \times \Omega} K(\vt,\vx) \, \lambda(\dif \vt) \nu(\dif \vx).
 \end{equation}
-This can be established directly from \eqref{kerDeltaDef} for $\cm_0$, the vector space spanned by all Dirac measures.
-Letting $\cm$ be the closure of the pre-Hilbert space $\cm_0$ then yields \eqref{ipMdef}.
+This can be established directly from \eqref{eq:kerDeltaDef} for $\cm_0$, the vector space spanned by all Dirac measures.
+Letting $\cm$ be the closure of the pre-Hilbert space $\cm_0$ then yields \eqref{eq:ipMdef}.
 
@@
 \begin{align} 
+\nonumber
     D^2(\Xdes,\nu,K) & := \norm[\cm]{\nu - \nu_{\Xdes}}^2 \\
@@
 \end{equation}
-This kernel is plotted in Figure \ref{fig:kernelpict} for $d=1$. The distance between two Dirac measures by \eqref{distDelta} for this kernel in one dimension is 
+This kernel is plotted in Figure \ref{fig:kernelpict} for $d=1$. The distance between two Dirac measures by \eqref{eq:distDelta} for this kernel in one dimension is 
 \begin{equation*}
@@
     \centering
-    \includegraphics[height = 4cm]{code/KernelPict.eps} \qquad
-    \includegraphics[height = 4cm]{code/Kernel3DPict.eps}
+    \includegraphics[height = 4cm]{\figdir KernelPict.eps} \qquad
+    \includegraphics[height = 4cm]{\figdir Kernel3DPict.eps}
     \caption{The kernel defined in \eqref{eq:OrigKernel} for $d=1$.}
@@
      - \frac 2N \sum_{i=1}^N \prod_{j=1}^d \left[1 + u_{ij} - \frac{u_{ij}^2}{2} \right] \\
+     \nonumber
      & \qquad \qquad + \frac 1{N^2} \sum_{i,k=1}^N \prod_{j=1}^d \left[1+ \min(u_{ij},u_{ik})\right].
@@
 We can equate this formula for $\norm[\ch]{\xi}^2$ with the formula for $D^2(\Xdes,F,K)$ in  \eqref{eq:discDef}.
-Thus, the tight, worst-case cubature error  bound in \eqref{eq:wcErrA} can be written as
-\begin{equation}\label{eq:wcErrB}
+Thus, the tight, worst-case cubature error  bound in \eqref{eq:wcErrA} can be written in terms of the discrepancy as
+\begin{equation*}\label{eq:wcErrB}
 \abs{\err(f,\Xdes)} \le \norm[\ch]{f} D(\Xdes,F,K).
-\end{equation}
+\end{equation*}
 This implies our second interpretation of the discrepancy in Table \ref{tab:ThreeInterpTable}.
@@
 The inner product for the reproducing kernel $K$ defined in  \eqref{eq:OrigKernel} is defined as
-\begin{align}\label{eq:inner}
+\begin{align}
+\label{eq:inner}
 \langle f,g \rangle_{\ch} &:= \sum_{\fraku\subseteq \{1,...,d\}}\int_{(\va,\vb)}\partial^{\fraku}f(\vx_\fraku)\partial^{\fraku}g(\vx_\fraku) \, \dif \vx_\fraku \\
@@
 \begin{align*}
-&\Ex_{f\in\mathcal{A}}[(\err(f,\Xdes)]^2= \Ex_{f\in\mathcal{A}} \left\{\int_{\Omega}f(\vx) \,\dif F(\vx)-\frac{1}{N}\sum_{i=1}^N f(\vx_i) \right\}^2\\
-=&\Ex_{f\in\mathcal{A}}\left\{\int_{\Omega}(f(\vx)-m) \, \dif F(\vx)-\frac{1}{N}\sum_{i=1}^N (f(\vx_i)-m) \right\}^2\\
-=&\int_{\Omega^2}\Ex_{f\in \mathcal{A}}[ (f(\vt)-m)(f(\vx)-m)] \, \dif F(\vt)\dif F(\vx)\\
-&-\frac{2}{N}\sum_{i=1}^N \int_{\Omega} \Ex_{f\in\mathcal{A}}[(f(\vx)-m)(f(\vx_i)-m)]\,\dif F(\vx)\\
-&+\frac{1}{N^2}\sum_{i,k=1}^N\Ex_{f\in\mathcal{A}}[(f(\vx_i)-m)(f(\vx_k)-m)]\\
-=&\int_{\Omega^2}K(\vt,\vx) \, \dif F(\vt)\dif F(\vx)-\frac{2}{N}\sum_{i=1}^N \int_{\Omega} K(\vx, \vx_i)\, \dif F(\vx)+\frac{1}{N^2} \sum_{i,k=1}^N K(\vx_i,\vx_k). 
+\Ex_{f\in\mathcal{A}}[(\err(f,\Xdes)]^2 &= \Ex_{f\in\mathcal{A}} \left\{\int_{\Omega}f(\vx) \,\dif F(\vx)-\frac{1}{N}\sum_{i=1}^N f(\vx_i) \right\}^2\\
+&=\Ex_{f\in\mathcal{A}}\left\{\int_{\Omega}(f(\vx)-m) \, \dif F(\vx)-\frac{1}{N}\sum_{i=1}^N (f(\vx_i)-m) \right\}^2\\
+&=\int_{\Omega^2}\Ex_{f\in \mathcal{A}}[ (f(\vt)-m)(f(\vx)-m)] \, \dif F(\vt)\dif F(\vx)\\
+&\qquad  -\frac{2}{N}\sum_{i=1}^N \int_{\Omega} \Ex_{f\in\mathcal{A}}[(f(\vx)-m)(f(\vx_i)-m)]\,\dif F(\vx)\\
+&\qquad +\frac{1}{N^2}\sum_{i,k=1}^N\Ex_{f\in\mathcal{A}}[(f(\vx_i)-m)(f(\vx_k)-m)]\\
+&=\int_{\Omega^2}K(\vt,\vx) \, \dif F(\vt)\dif F(\vx)-\frac{2}{N}\sum_{i=1}^N \int_{\Omega} K(\vx, \vx_i)\, \dif F(\vx) \\
+& \qquad +\frac{1}{N^2} \sum_{i,k=1}^N K(\vx_i,\vx_k). 
 \end{align*}
@@
     & \qquad \qquad  + \frac{1}{N^2} \sum_{i,k=1}^N K_\unif(\vPsi^{-1}(\vx_i),\vPsi^{-1}(\vx_k)) \\
+    \nonumber
     & = D^2(\Xdes,F,K)
@@
       &= \prod_{j=1}^d\left[1+\frac{1}{2}\left(\left|\Phi(t_j)-1/2\right|+ \left|\Phi(x_j)- 1/2 \right| \right . \right . \\
+      \nonumber
       & \qquad \qquad \left.  \left . -\left|\Phi(t_j)-\Phi(x_j)\right|\right)\right].
@@
 then 
-\begin{equation} \label{eq:desEquiv}
+\begin{equation*} \label{eq:desEquiv}
      D(\Udes',F'_\unif,K) = D(\Udes, F_\unif, K_\unif),
-\end{equation}
+\end{equation*}
 where $K$ is the kernel defined in \eqref{eq:OrigKernel}.
@@
 Such a discrepancy is
-\begin{align}\label{eq:DisNormald>1}
+\begin{align}
 \nonumber
@@
   &+\frac{1}{N^2}\sum_{i,k=1}^N \prod_{j=1}^d \left[1+\frac{1}{2}\left(|x_{ij}|+|x_{kj}|-|x_{ij}-x_{kj}|\right)\right]. 
+  \label{eq:DisNormald>1}
 \end{align}
@@
 \begin{center}
-\includegraphics[width=8cm]{code/d5n50.eps}
+\includegraphics[width=8cm]{\figdir d5n50.eps}
 \caption{Normal discrepancy versus uniform discrepancy for transformed designs. \label{fig:UniVsNormDisc}}
@@
 \begin{center}
-\includegraphics[width=8cm]{code/dimVsdisc.eps}
+\includegraphics[width=8cm]{\figdir dimVsdisc.eps}
 \caption{Correlation between the uniform and normal discrepancies for different dimensions. \label{fig:DiscVsd}}
@@
 The function $f:\reals^d \to \reals$ is constructed to asymptote to a constant as $\norm[2]{\vx}$ tends to infinity to ensure that $f$ lies inside the Hilbert space corresponding to the kernel $K$ defined in \eqref{eq:OrigKernel}.
-Since the integrand in \eqref{eq:badexampleb} is a function of $\norm[2]{\vx}$, $\mu$ can be written as a one dimensional integral.
+Since the integrand in \eqref{eq:badexample} is a function of $\norm[2]{\vx}$, $\mu$ can be written as a one dimensional integral.
 For $d=10$, $\mu = 10$ to at least $15$ significant digits using quadrature.
@@
 We then choose
-\begin{equation} \label{eq:rowchoice}
+\begin{equation*} \label{eq:rowchoice}
     i^*=\argmax_{i=1,\ldots,N} \frakd_p(i).
-\end{equation}
+\end{equation*}
 The definition of $i^*$ means that removing $\vx_{i^*}$ from the design $\Xdes$ results in the smallest discrepancy among all possible deletions.
@@
 For this calculation to be feasible, the target distribution must have independent marginals.
-Also, the kernel to be of product form.
+Also, the kernel must be of product form.
 To simplify the derivation, we assume a somewhat stronger condition, namely that the marginals are identical and that each term in the product defining the kernel is the same for every coordinate:
@@
 We then choose 
-\begin{equation} \label{eq:columnchoice}
+\begin{equation*} \label{eq:columnchoice}
     j^*=\argmax_{j=1, \ldots, d} \frakd_c(j).
-\end{equation}
+\end{equation*}
 For reasons analogous to those given above, the $j^{*\text{th}}$ coordinate seems to be the best candidate for change.
@@
 We recommend multiple runs of the algorithm with different initial designs to obtain a design with the lowest discrepancy possible. 
-Alternatively, users can include stochastic scheme in choosing the coordinate that is to be exchanged, similarly as in \cite{kang2018stochastic}.
+Alternatively, users can include stochasticity in the choice of the coordinate that is to be exchanged, similarly to \cite{kang2018stochastic}.
 
@@
 &= \frac{(2N-1)(1+c)^d}{N^2} - \frac{2}{N}\biggl[ \frac{1}{N} \sum_{k=1}^N  H(\vx_{k}) + \left(1 - \frac 1N \right) H(\vx_{i})  \biggr] \\
-\label{eq:rowdeletionA}
+\nonumber
+%\label{eq:rowdeletionA}
 & \qquad \qquad + \frac{1}{N^2}\biggl[2 \sum_{k=1}^N K(\vx_{i},\vx_{j})- K(\vx_{i},\vx_{i})\biggr]. 
@@
 The coordinate deletion function defined in \eqref{eq:coorddeletion} can be be expressed as
-\begin{multline}\label{eq:coldeletionA}
+\begin{multline*}%\label{eq:coldeletionA}
 \frakd_c(j) = (c-1)c^{d-1} -\frac{2}{N}\sum_{i=1}^N \frac{h(x_{ij})H(\vx_i)}{1+h(x_{ij})}  \\
 +\frac{1}{N^2}\sum_{i,k=1}^N \frac{\tK(x_{ij},x_{kj}) K(\vx_i,\vx_j)}{1+\tK(x_{ij},x_{kj})}  .
-\end{multline}
+\end{multline*}
 The computational cost for $\frakd_c(1), \ldots, \frakd_p(d)$ is also $\Order(dN^2)$, which is the same order as the cost of the discrepancy of a single design.
@@
 & \qquad \qquad +\frac{1}{N^2}\left(2\sum_{\substack{i=1 \\ i \ne i^*}}^N  \frac{[\tK(x_{i^*j^*},x_{ij^*})-\tK(x,x_{ij^*})] K(\vx_{i^*},\vx_i)} {1 + \tK(x_{i^*j^*},x_{ij^*})} \right . \\
+\nonumber
 & \qquad \qquad \left . + \frac{[\tK(x_{i^*j^*},x_{i^*j^*})-\tK(x,x)] K(\vx_{i^*},\vx_{i^*})} {1 + \tK(x_{i^*j^*},x_{i^*j^*})} \right )
@@
 If we drop the terms that are independent of $x$, then we can maximize the function
-\begin{equation}\label{eq:deltapfunction}
+\begin{equation*} %\label{eq:deltapfunction}
 \Delta'(x) = Ah(x)  - \frac{1}{N}\sum_{\substack{i=1 \\ i \ne i^*}}^N B_i \tK(x,x_{ij^*}) - C \tK(x,x)
-\end{equation}
+\end{equation*}
 where
@@
 All codes were run on a MacBook Pro with 2.4 GHz Intel Core i5 processor.
-The maximum iteration allowed is set to be $M_{\max} = 200$, and the Algorithm \ref{alg:coorex} converges within 20 iterations in all simulation examples.
+The maximum iteration allowed is set to be $M_{\max} = 200$, and  Algorithm \ref{alg:coorex} converges within 20 iterations in all simulation examples.
 
@@
 \begin{center}
-\includegraphics[width=8cm]{code/boxplotall_d2n32.eps}
+\includegraphics[width=8cm]{\figdir boxplotall_d2n32.eps}
 \caption{Performance comparison of designs. \label{fig:SOBOLVsRAND}}
@@
 \centering
-{\subfigure[$d=2,N=32$] {\includegraphics[width=5.5cm]{code/boxplot_d2n32.eps}}}
+{\subfigure[$d=2,N=32$] {\includegraphics[width=5.5cm]{\figdir boxplot_d2n32.eps}}}
 \quad
 {\subfigure [$d=3, N=64$]
-{\includegraphics[width=5.5cm]{code/boxplot_d3n64.eps}}}
+{\includegraphics[width=5.5cm]{\figdir boxplot_d3n64.eps}}}
 \quad
-{\subfigure[$d=4, N=64$] {\includegraphics[width=5.5cm]{code/boxplot_d4n64.eps}}}
+{\subfigure[$d=4, N=64$] {\includegraphics[width=5.5cm]{\figdir boxplot_d4n64.eps}}}
 \quad
-{\subfigure[$d=6, N=128$] {\includegraphics[width=5.5cm]{code/boxplot_d5n128.eps}}}
+{\subfigure[$d=6, N=128$] {\includegraphics[width=5.5cm]{\figdir boxplot_d5n128.eps}}}
 \quad
-{\subfigure[$d=8, N=256$] {\includegraphics[width=5.5cm]{code/boxplot_d8n256.eps}}}
+{\subfigure[$d=8, N=256$] {\includegraphics[width=5.5cm]{\figdir boxplot_d8n256.eps}}}
 \quad
-{\subfigure[$d=10, N=512$] {\includegraphics[width=5.5cm]{code/boxplotall_d10n512.eps}}}
+{\subfigure[$d=10, N=512$] {\includegraphics[width=5.5cm]{\figdir boxplotall_d10n512.eps}}}
 \caption{Performance comparison of designs \label{fig:comparison}}
@@
 \centering
-{\subfigure[$d=2,N=32$] {\includegraphics[width=5.5cm]{code/errorboxplot_d2n32.eps}}}
+{\subfigure[$d=2,N=32$] {\includegraphics[width=5.5cm]{\figdir errorboxplot_d2n32.eps}}}
 \quad
 {\subfigure [$d=3, N=64$]
-{\includegraphics[width=5.5cm]{code/errorboxplot_d3n64.eps}}}
+{\includegraphics[width=5.5cm]{\figdir errorboxplot_d3n64.eps}}}
 \quad
-{\subfigure[$d=4, N=64$] {\includegraphics[width=5.5cm]{code/errorboxplot_d4n64.eps}}}
+{\subfigure[$d=4, N=64$] {\includegraphics[width=5.5cm]{\figdir errorboxplot_d4n64.eps}}}
 \quad
-{\subfigure[$d=6, N=128$] {\includegraphics[width=5.5cm]{code/errorboxplot_d6n128.eps}}}
+{\subfigure[$d=6, N=128$] {\includegraphics[width=5.5cm]{\figdir errorboxplot_d6n128.eps}}}
 \quad
-{\subfigure[$d=8, N=256$] {\includegraphics[width=5.5cm]{code/errorboxplot_d8n256.eps}}}
+{\subfigure[$d=8, N=256$] {\includegraphics[width=5.5cm]{\figdir errorboxplot_d8n256.eps}}}
 \quad
-{\subfigure[$d=10, N=512$] {\includegraphics[width=5.5cm]{code/errorboxplot_d10n512.eps}}}
+{\subfigure[$d=10, N=512$] {\includegraphics[width=5.5cm]{\figdir errorboxplot_d10n512.eps}}}
 \caption{Integral Approximate Performance Comparison of Generators}
@@
 The product form of the kernel given in \eqref{eq:prodkernel} can be generalized as
-\begin{equation} \label{eq:prodKernelWts}
+\begin{equation*} %\label{eq:prodKernelWts}
      K_{\vgamma}(\vt,\vx)  = \prod_{j=1}^d\left[1+ \gamma_j \tK(t_j,x_j) \right].
-\end{equation}
+\end{equation*}
 Here the positive coordinate weights are $\vgamma = (\gamma_1, \ldots, \gamma_d)$.

### 2019-09-28 response.tex
revision

\documentclass[12pt]{article}
\usepackage{mathrsfs}
\usepackage{amsfonts}
\usepackage{amssymb, amsmath, amsthm,graphicx}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{fancyhdr}
\usepackage{comment}
\usepackage{float}
\usepackage{enumerate}
\usepackage{tikz-cd}
\setlength{\oddsidemargin}{0.0cm} \setlength{\evensidemargin}{0.0cm}
\setlength{\topmargin}{-15mm} \advance\headheight by 2pt
\setlength{\footskip}{8mm} \setlength{\textheight}{265mm}
\advance\textheight by-2\headheight \advance\textheight by-2\headsep
\setlength{\textwidth}{165mm}
\setlength{\parskip}{1.5em}
\def\baselinestrech{1.0}
\linespread{1}
\pagenumbering{arabic} 
\usepackage{url}
\newtheorem{lem}{Lemma}
\newtheorem{cor}{Corollary}[section]
\newtheorem{thm}{Theorem}
\theoremstyle{definition}
\newtheorem{pro}{Proposition}[section]
\newtheorem{defn}{Definition}[section]
\newtheorem{rmk}{Remark}[section]
\newtheorem{ex}{Example}[section]
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\pr}{Pr}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\E}{E}
\DeclareMathOperator{\cov}{cov} \DeclareMathOperator{\var}{var}
\DeclareMathOperator{\tr}{tr} \DeclareMathOperator{\err}{err}
\DeclareMathOperator{\IMSE}{IMSE}
\DeclareMathOperator{\Diag}{diag}
\DeclareMathOperator{\diag}{diag}

\newcommand{\blind}{1}
\newcommand{\reals}{\mathbb{R}}
\newcommand{\naturals}{\mathbb{R}}
\newcommand{\va}{\boldsymbol{a}}
\newcommand{\vb}{\boldsymbol{b}}
\newcommand{\vc}{\boldsymbol{c}}
\newcommand{\vx}{\boldsymbol{x}}
\newcommand{\vX}{\boldsymbol{X}}
\newcommand{\vt}{\boldsymbol{t}}
\newcommand{\vz}{\boldsymbol{z}}
\newcommand{\vu}{\boldsymbol{u}}
\newcommand{\vv}{\boldsymbol{v}}
\newcommand{\vy}{\boldsymbol{y}}
\newcommand{\fraku}{\mathfrak{u}}
\newcommand{\frakv}{\mathfrak{v}}
\newcommand{\mX}{{\mathsf X}}
\newcommand{\vinfty}{\boldsymbol{\infty}}
\newcommand{\vzero}{\boldsymbol{0}}
\newcommand{\vPsi}{\boldsymbol{\Psi}}
\newcommand{\dif}{{\rm d}}
\DeclareMathOperator{\sign}{sign}

\newcommand{\Udes}{\mathcal{U}}
\newcommand{\Xdes}{\mathcal{X}}
\newcommand{\FXdes}{F_{\Xdes}}
\newcommand{\cm}{\mathcal{M}}
\newcommand{\ch}{\mathcal{H}}
\newcommand{\MATLAB}{\textsc{Matlab}\xspace}
\newcommand{\Ftar}{F}
\newcommand{\ftar}{\varrho}
\newcommand{\cube}{\ensuremath{(0,1)^d}}
\newcommand{\bbone}{\mathbbm{1}}
\newcommand{\Ex}{\mathbb{E}}
\newcommand{\ip}[3][{}]{\ensuremath{\left \langle #2, #3 \right \rangle_{#1}}}
\newcommand{\norm}[2][{}]{\ensuremath{\left \lVert #2 \right \rVert}_{#1}}

\newcommand{\unif}{\textup{unif}}
\newcommand{\normal}{\textup{normal}}
\newcommand{\frakd}{\mathfrak{d}}
\newcommand{\tK}{\widetilde{K}}
\newcommand{\tOmega}{\widetilde{\Omega}}
\newcommand{\tvarrho}{\widetilde{\varrho}}
\newcommand{\Order}{\mathcal{O}}
\newcommand{\TOL}{\text{TOL}}
\newcommand{\vT}{\boldsymbol{T}}
\newcommand{\vone}{\boldsymbol{1}}
\newcommand{\vgamma}{\boldsymbol{\gamma}}
\newcommand{\figdir}{} %internally
%\newcommand{\figdir}{} %internally

\def\abs#1{\ensuremath{\left \lvert #1 \right \rvert}}
\pagestyle{fancy}

\bibliographystyle{amsplain}

% define a mysection env which content is excluded
\excludecomment{answer}
%\includecomment{answer}

\begin{document}

%header
%\rhead{\footnotesize{Yiou Li\\DePaul University}}
\chead{ }
\cfoot{\thepage}

%here the body of your document is beginning
\thispagestyle{empty}
\begin{center}
\center{\Large{Response to Referee Comments}}\\
\end{center}

\bigskip

We would like to thank the referee(s) for the valuable comments on the manuscript. The following are our responses to referee(s) comments and concerns.

\begin{enumerate}
\item
\emph{However, as the proposed approach is a stochastic algorithm, I would like to suggest the authors clarify the following issues: 1. What is the benefit to use the coordinate-exchange algorithm here? Since other stochastic algorithms, including the threshold accepting (TA), had been successfully applied to search for uniform designs, it seemed necessary to conduct some comparison, or at least add some comments, about the performance among different stochastic algorithms;}

First, we need to correct a misunderstanding. 
The coordinate-exchange algorithm is a deterministic algorithm, rather than stochastic. 
We only change one coordinate in each iteration, when change one design to one of its neighboring designs. 
To decide which coordinate for exchange, we compute the point deletion function to decide the row index, and then compute the coordinate deletion function to decide which coordinate of the chosen row to be exchanged. 
The selection is deterministic, i.e., we always pick the indices corresponding to the largest deletion function values. 
The exchange for the coordinates is also deterministic, as long as the objective function is improved with the exchange. 
Please see details in Algorithm 1.

We admit that the major flaw of the greedy algorithm is that the solution is likely to be a local minima. 
To overcome this, we can either run the algorithms with multiple random starts, if the initial design can be randomly generated, rather than being given, or we can combine the combine the coordinate-exchange with stochastic optimization algorithms, such as simulated annealing (SA) or threshold accepting (TA) methods. 
For example, before making the exchange of the coordinates, we can incorporate a random scheme to accept the exchange or not, as in SA algorithm. 
To combine it with the TA, it can be done similarly.

However, we eventually decided not to revise the algorithm and keep it in this greedy fashion. 
The main reason is that to use these stochastic algorithms, many tuning parameters have to be carefully selected to make the stochastic algorithm truly effective. 
For example, for SA we need to decide how fast the temperature would decrease, and for TA we need to design the sequence of the threshold values. 
Even though combining SA or TA with the coordinate-exchange algorithm is straightforward, setting these tuning parameters is not. 
We need to do many simulation studies and probably some theoretical derivation to make reasonable choices
It would significantly increase the length of our manuscript. 
Moreover, it will distract the readers from the main focus of our work, which is to raise the concern of the potential danger of directly using the inverse transformed uniform design. 
The goal of the algorithm is not to achieve the ``optimal'', rather to elevate the issue caused by transformation. 
In this sense, we would are satisfied with the current coordinate-exchange algorithm.

We do add one paragraph to commenting on the TA and SA algorithm and how it can be incorporated with the current algorithm in end of the Section 5.

\item
\emph{What is the benefit to use the transformed design as the input? What if just using a randomly generated input design?}

One can start with either randomly generated input design or the transformed one. 
As we have shown that $D(\mathcal{U}, F_{\textrm{unif}}, K_{\textrm{unif}})$ has a certain amount of positive correlation with $D(\vPsi(\Udes),F_\normal, K)$, especially for low dimension, if the initial design is the transformed uniform design, the corresponding $D(\vPsi(\Udes),F_\normal, K)$ value might be smaller than some randomly generated design. 
Thus, the algorithm would take fewer iterations to converge.

\item \emph{In the abstract, it is said that "one remedy is to ensure that the original uniform design has optimal one-dimensional projection". Does it mean the importance of using E-SOBOL designs? It seems necessary to give more explanation.}

We revised the relevant states in the abstract and add some more details to clarify as the following.

``One remedy is to ensure that the original uniform design has optimal one-dimensional projection, but this remedy works best if the design is dense, or in other words, the ratio of sample size divided by the dimension of the random variable is relatively large. 
Another remedy is to use the transformed design as the input to a coordinate-exchange algorithm that optimizes the desired discrepancy, and this works for both dense or sparse designs. ''

This conclusion is from our observations of the simulations. 
The E-SOBOL design, which simply is the inverse transformed scrambled Sobol' design with one-dimension project property. 
The CE is the coordinate exchange that further improves the E-SOBOL design, as E-SOBOL design is used as the initial design.

Our simulation shows that CE always outperforms the others. 
For dense design, E-SOBOL is good enough, but this is not the case for sparse design, i.e., $N/d$ is small. 
Hence, we wrote the statement on remedies in the abstract.

\item We have corrected the typos pointed out by the referee.

\end{enumerate}
\end{document}

### 2019-09-28 InvPts_verB_revision.tex
revision

--- 2019-06-14 InvPts_verB.tex
@@
 \abstract{Experimental designs intended to match arbitrary target distributions are typically constructed via a variable transformation of a uniform experimental design.
-The inverse distribution function is one such transformation. The discrepancy is a measure of how well the empirical distribution of any design matches its target distribution.
+The inverse distribution function is one such transformation.
+The discrepancy is a measure of how well the empirical distribution of any design matches its target distribution.
 This chapter addresses the question of whether a variable transformation of a low discrepancy uniform design yields a low discrepancy design for the desired target distribution.
@@
 We also suggest some remedies. 
-One remedy is to ensure that the original uniform design has optimal one-dimensional projection.
-Another remedy is to use the transformed design as the input to a coordinate-exchange algorithm that optimizes the desired discrepancy.
+One remedy is to ensure that the original uniform design has optimal one-dimensional projection, but this remedy works best if the design is dense, or in other words, the ratio of sample size divided by the dimension of the random variable is relatively large.
+Another remedy is to use the transformed design as the input to a coordinate-exchange algorithm that optimizes the desired discrepancy, and this works for both dense or sparse designs. 
 The effectiveness of these two remedies is illustrated via simulation.}
@@
 The discrepancy measures the magnitude of $F_\unif-F_\Udes$. 
-The uniform design a commonly used space filling design for computer experiments \cite{FanLiSud06} and can be constructed using  JMP\textsuperscript{\textregistered} \cite{sall2012jmp}.
+The uniform design is a commonly used space filling design for computer experiments \cite{FanLiSud06} and can be constructed using  JMP\textsuperscript{\textregistered} \cite{sall2012jmp}.
 
@@
 \begin{equation}\label{eq:inverse}
-\Psi_j(u_j) = F_j^{-1}(u_j), \quad j =1, \ldots, d, \qquad \text{where } \Ftar(\vx) = F_1(u_1) \cdots F_d(u_d).
+\Psi_j(u_j) = F_j^{-1}(u_j), \quad j =1, \ldots, d, \qquad \text{where } \Ftar(\vx) = F_1(x_1) \cdots F_d(x_d).
 \end{equation}
@@
 
-We now identify the RKHS for the kernel $K$ defined in \eqref{eq:OrigKernel} Let $(\va,\vb)$ be some $d$ dimensional box containing the origin in the interior or on the boundary.
+We now identify the RKHS for the kernel $K$ defined in \eqref{eq:OrigKernel}.
+Let $(\va,\vb)$ be some $d$ dimensional box containing the origin in the interior or on the boundary.
 For any $\fraku \subseteq \{1, \ldots, d\}$, define $\partial^\fraku f(\vx_\fraku) : = \partial^{|\fraku|}f(\vx_\fraku,\vzero)/\partial \vx_\fraku$, the mixed first-order partial derivative of $f$ with respect to the $x_j$ for $j\in \fraku$, while setting $x_j=0$ for all $j \notin \fraku$.
@@
 
+Note that the coordinate-exchange algorithm we have developed is a greedy and deterministic algorithm. 
+The coordinate that we choose to make exchange is the one has the largest point and coordinate deletion function values, and we always make the exchange for new coordinate as long as the new optimal coordinate improves the objective function.
+It is true that such deterministic and greedy algorithm is likely to return the design of the local minima. 
+To overcome this, we can either run the algorithms with multiple random initial designs, or we can combine the combine the coordinate-exchange with stochastic optimization algorithms, such as simulated annealing (SA) \cite{kirkpatrick1983optimization} or threshold accepting (TA) \cite{fang2003lower} methods.
+For example, before making the exchange of the coordinates, we can incorporate a random scheme to accept the exchange or not. 
+The random scheme can follow the SA or TA method. 
+Tuning parameters must be carefully chosen to make the SA or TA method effective. 
+In this chapter, we omit the further investigation in this direction. 
+Interested readers can refer to \cite{winker1997application} to see how TA can be applied to evaluation of discrepancy.
+
+% However, we eventually decided not to revise the algorithm and keep it in this greedy fashion. 
+% The main reason is that to use these stochastic algorithms, many tuning parameters have to be carefully selected to make the stochastic algorithm truly effective. 
+% For example, for SA we need to decide how fast the temperature would decrease, and for TA we need to design the sequence of the threshold values. 
+% Even though combining SA or TA with the coordinate-exchange algorithm is straightforward, setting these tuning parameters is not. 
+% We need to do many simulation studies and probably some theoretical derivation to make reasonable choices
+% It would significantly increase the length of our manuscript. 
+% Moreover, it will distract the readers from the main focus of our work, which is to raise the concern of the potential danger of directly using the inverse transformed uniform design. 
+% The goal of the algorithm is not to achieve the ``optimal'', rather to elevate the issue caused by transformation. 
+% In this sense, we would are satisfied with the current coordinate-exchange algorithm.
+
+% Global optimization tools like simulated annealing \cite{kirkpatrick1983optimization} and threshold accepting algorithm \cite{fang2003lower} could be applied to achieve minimum discrepancy designs.
+For most of the global optimization tools, the choice of tuning parameters would influence the performance of the algorithm significantly, and additional efforts are needed to determine the tuning parameters.
+In this work, we aim at improving the discrepancy of the design, but not minimizing it.
+Thus, we would recommend using the coordinate-exchange method that is both computationally efficient and easy to implement.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 When the design is more sparse, i.e., $N/d$ is smaller, SOBOL and E-SOBOL have similar performance, but CE is superior to both of them in terms of the discrepancy.
-not only in terms of the mean but also in terms of the \emph{range} for the $500$ designs generated.
+Not only in terms of the mean but also in terms of the \emph{range} for the $500$ designs generated.
 

### 2019-09-28 InvPts_verB_revision.tex

@@
 \institute{Yiou Li \at DePaul University, 2320 N. Kenmore Avenue, Chicago, IL 60614 \email{yli139@depaul.edu}
-\and Lulu Kang \at Illinois Institute of Technology, 10 W. 32nd Street, Chicago, IL 60616 \email{lkang2@iit.edu} 
+\and Lulu Kang \at Illinois Institute of Technology, RE 208, 10 W. 32nd Street, Chicago, IL 60616 \email{lkang2@iit.edu} 
 \and 
-Fred J. Hickernell \at Illinois Institute of Technology, 10 W. 32nd Street, Chicago, IL 60616 \email{hickernell@iit.edu}}
+Fred J. Hickernell \at Illinois Institute of Technology, RE 208, 10 W. 32nd Street, Chicago, IL 60616 \email{hickernell@iit.edu}}
 %
@@
 One remedy is to ensure that the original uniform design has optimal one-dimensional projection, but this remedy works best if the design is dense, or in other words, the ratio of sample size divided by the dimension of the random variable is relatively large.
+\FJH{How do we know that $N/d$ is the right quantity to be large?}
 Another remedy is to use the transformed design as the input to a coordinate-exchange algorithm that optimizes the desired discrepancy, and this works for both dense or sparse designs. 
@@
 
-Low discrepancy designs, $\Udes = \{\vu_i\}_{i=1}^N$, are typically constructed so that their empirical distributions, $F_\Udes$, approximate $F_\unif$, the uniform distribution on the unit cube, \cube.
+Low discrepancy uniform designs, $\Udes = \{\vu_i\}_{i=1}^N$, are typically constructed so that their empirical distributions, $F_\Udes$, approximate $F_\unif$, the uniform distribution on the unit cube, \cube.
 The discrepancy measures the magnitude of $F_\unif-F_\Udes$. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{When Transformed Low Discrepancy Design Also Has Low Discrepancy}
+\section{When a Transformed Low Discrepancy Design Also Has Low Discrepancy}
 \label{sec:WhenYes}
@@
 The coordinate that we choose to make exchange is the one has the largest point and coordinate deletion function values, and we always make the exchange for new coordinate as long as the new optimal coordinate improves the objective function.
-It is true that such deterministic and greedy algorithm is likely to return the design of the local minima. 
-To overcome this, we can either run the algorithms with multiple random initial designs, or we can combine the combine the coordinate-exchange with stochastic optimization algorithms, such as simulated annealing (SA) \cite{kirkpatrick1983optimization} or threshold accepting (TA) \cite{fang2003lower} methods.
-For example, before making the exchange of the coordinates, we can incorporate a random scheme to accept the exchange or not. 
-The random scheme can follow the SA or TA method. 
+It is true that such deterministic and greedy algorithm is likely to return a design of whose discrepancy attains a \emph{local} minimum. 
+To overcome this, we can either run the algorithm with multiple random initial designs, or we can combine the combine coordinate-exchange with stochastic optimization algorithms, such as simulated annealing (SA) \cite{kirkpatrick1983optimization} or threshold accepting (TA) \cite{fang2003lower}.
+For example, before making the exchange of the coordinates, we can incorporate a random decision to accept the exchange or not. 
+The random decision can follow the SA or TA method. 
 Tuning parameters must be carefully chosen to make the SA or TA method effective. 
-In this chapter, we omit the further investigation in this direction. 
 Interested readers can refer to \cite{winker1997application} to see how TA can be applied to evaluation of discrepancy.
@@
 
-To demonstrate the performance of the $d$-dim standard normal design proposed in Section \ref{sec:CoordEx}, we compare three families of designs: (1) RAND: inverse transformed IID uniform random numbers;  (2) SOBOL: inverse transformed Sobol' set; (3) E-SOBOL: inverse transformed scrambled Sobol' set where the one dimensional projections of the Sobol' set have been adjusted to be  $\left\{1/(2N), 3/(2N), \ldots, (2N-1)/(2N) \right\}$; (4) CE: improved E-SOBOL via Algorithm \ref{alg:coorex}.
+To demonstrate the performance of the $d$-dimensional standard normal design proposed in Section \ref{sec:CoordEx}, we compare three families of designs: (1) RAND: inverse transformed IID uniform random numbers;  (2) SOBOL: inverse transformed Sobol' set; (3) E-SOBOL: inverse transformed scrambled Sobol' set where the one dimensional projections of the Sobol' set have been adjusted to be  $\left\{1/(2N), 3/(2N), \ldots, (2N-1)/(2N) \right\}$; and (4) CE: improved E-SOBOL via Algorithm \ref{alg:coorex}.
 We have tried different combinations of dimension, $d$, and sample size, $N$. 
@@
 Figure \ref{fig:SOBOLVsRAND} contains the boxplots of normal discrepancies corresponding to the four generators with $d=2$ and $N=32$.
-It shows that SOBOL, E-SOBOL, and CE all outperform RAND by a great margin.
-To better present the comparison between the better generators, in Figure \ref{fig:comparison} we mostly exclude RAND.
+It shows that SOBOL, E-SOBOL, and CE all outperform RAND by a large margin.
+To better present the comparison between the better generators, in Figure \ref{fig:comparison} we generally exclude RAND.
 
@@
 All codes were run on a MacBook Pro with 2.4 GHz Intel Core i5 processor.
-The maximum iteration allowed is set to be $M_{\max} = 200$, and  Algorithm \ref{alg:coorex} converges within 20 iterations in all simulation examples.
+The maximum number of iterations allowed is $M_{\max} = 200$.
+Algorithm \ref{alg:coorex} converges within 20 iterations in all simulation examples.
 
@@
 \end{equation*}
-Here the positive coordinate weights are $\vgamma = (\gamma_1, \ldots, \gamma_d)$.
+Here, the positive coordinate weights are $\vgamma = (\gamma_1, \ldots, \gamma_d)$.
 The squared discrepancy corresponding to this kernel may then be written as
@@
 where $c$ and $h$ are defined in \eqref{eq:chHdef}.
-Here $\Xdes_\fraku$ denotes the projection of the design into the coordinates contained in $\fraku$, and $F_\fraku = \prod_{j \in \fraku} F_j$ is the $\fraku$-marginal distribution.
-Each discrepancy piece, $D_{\fraku} (\Xdes_\fraku,F_\fraku,K)$, measures how well $\Xdes_\fraku$ matches $F_\fraku$.
+Here, $\Xdes_\fraku$ denotes the projection of the design into the coordinates contained in $\fraku$, and $F_\fraku = \prod_{j \in \fraku} F_j$ is the $\fraku$-marginal distribution.
+Each discrepancy piece, $D_{\fraku} (\Xdes_\fraku,F_\fraku,K)$, measures how well the projected design $\Xdes_\fraku$ matches $F_\fraku$.
 

### 2019-09-28 response.tex
Updates from Overleaf

@@
 Moreover, it will distract the readers from the main focus of our work, which is to raise the concern of the potential danger of directly using the inverse transformed uniform design. 
-The goal of the algorithm is not to achieve the ``optimal'', rather to elevate the issue caused by transformation. 
+The goal of the algorithm is not to achieve the ``optimal'', rather to alleviate the issue caused by transformation. 
 In this sense, we would are satisfied with the current coordinate-exchange algorithm.
@@
 
-\item \emph{In the abstract, it is said that "one remedy is to ensure that the original uniform design has optimal one-dimensional projection".
+\item \emph{In the abstract, it is said that ``one remedy is to ensure that the original uniform design has optimal one-dimensional projection".
 Does it mean the importance of using E-SOBOL designs?

### 2019-09-30 InvPts_verB_revision.tex
Updates from Overleaf

@@
 One remedy is to ensure that the original uniform design has optimal one-dimensional projection, but this remedy works best if the design is dense, or in other words, the ratio of sample size divided by the dimension of the random variable is relatively large.
-\FJH{How do we know that $N/d$ is the right quantity to be large?}
 Another remedy is to use the transformed design as the input to a coordinate-exchange algorithm that optimizes the desired discrepancy, and this works for both dense or sparse designs. 
@@
 It is true that such deterministic and greedy algorithm is likely to return a design of whose discrepancy attains a \emph{local} minimum. 
-To overcome this, we can either run the algorithm with multiple random initial designs, or we can combine the combine coordinate-exchange with stochastic optimization algorithms, such as simulated annealing (SA) \cite{kirkpatrick1983optimization} or threshold accepting (TA) \cite{fang2003lower}.
-For example, before making the exchange of the coordinates, we can incorporate a random decision to accept the exchange or not. 
+To overcome this, we can either run the algorithm with multiple random initial designs, or we can combine the coordinate-exchange with stochastic optimization algorithms, such as simulated annealing (SA) \cite{kirkpatrick1983optimization} or threshold accepting (TA) \cite{fang2003lower}.
+For example, we can add a random selection scheme when choosing a coordinate to exchange, and when making the exchange of the coordinates, we can incorporate a random decision to accept the exchange or not.
 The random decision can follow the SA or TA method. 
 Tuning parameters must be carefully chosen to make the SA or TA method effective. 
-Interested readers can refer to \cite{winker1997application} to see how TA can be applied to evaluation of discrepancy.
+Interested readers can refer to \cite{winker1997application} to see how TA can be applied to the minimization of discrepancy.
 
